---
title: "Field and UAv Data Analysis"
author: "Anna Talucci"
date: "2/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lsmeans)
library(DHARMa)
```


# Field Data
```{r}
sites = read.csv("../data/field_subset/site_info_uav.csv")
shrubs = read.csv("../data/field_subset/shrub_info_uav.csv")
trees = read.csv("../data/field_subset/tree_info_uav.csv")
```

```{r}
sites
```
 Create a plot_dis column to pull out numeric values from the plot column. There  are some sites that  had two  plots  at  -25 labeled  as -25a and -25b, which is  not useful for analysis.  Unique ID and plot  include the a or b designation
```{r}
numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 

sites_subset = sites %>% mutate(plot_dis = numextract(plot)) %>% mutate(burn_unburn = ifelse(plot_dis>=0, "burned", "unburned")) %>% dplyr::select(ID, region:plot, plot_dis, burn_unburn, slope:aspect) %>% mutate(burn_year = as.factor(burn_year))
sites_subset
```
````{r}
trees_subset = trees %>% mutate(plot_dis = numextract(plot))  %>% dplyr::select(ID:plot, plot_dis, area_sampled_m2:total_ba)
shrubs_subset = shrubs %>% mutate(plot_dis = numextract(plot)) %>% dplyr::select(ID:plot, plot_dis, area_sampled_m2:salix_ba)
```


```{r}
trees
```

## field Plot sizes

```{r}
shrubs %>% group_by(site, transect) %>% 
  summarise(min(area_sampled_m2))
```

```{r}
shrubs %>% group_by(site, transect) %>% 
  summarise(max(area_sampled_m2))
```

```{r}
trees %>% group_by(site, transect) %>% 
  summarise(min(radius))
```

```{r}
trees %>% group_by(site, transect) %>% 
  summarise(max(radius))
```

# UAV Data

```{r}
gcc_1m = read.csv("../data/extracted_data/gcc_1m.csv", strip.white = TRUE)
gcc_3m = read.csv("../data/extracted_data/gcc_3m.csv", strip.white = TRUE)
gcc_25cm = read.csv("../data/extracted_data/gcc_25cm.csv", strip.white = TRUE)
gcc = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_1m = read.csv("../data/extracted_data/ndvi_1m.csv", strip.white = TRUE)
ndvi_3m = read.csv("../data/extracted_data/ndvi_3m.csv", strip.white = TRUE)
ndvi_25cm = read.csv("../data/extracted_data/ndvi_25cm.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/ndvi_all.csv", strip.white = TRUE)
```


# Combine Field and UAV

```{r}
sites_gcc = merge(sites_subset, gcc, by="ID")
sites_gcc
```

```{r}
burn_year = sites_gcc %>% dplyr::select(ID, burn_year)
burn_year
```



```{r}
merge1 = merge(trees_subset, gcc, by="ID")
merge2 = merge(burn_year, merge1, by="ID")
tree_gcc = merge2 %>% mutate(prop_live = live/stems)
tree_gcc
```

```{r}
shrubs_gcc = merge(shrubs_subset, gcc, by="ID")
shrubs_gcc
```

# Analysis: Distance from Edge

## Model
```{r}
mod_dis = glm(mean_gcc_25cm ~ plot_dis, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod_dis.res = simulateResiduals(fittedModel = mod_dis, n = 500)
mod_dis.res$scaledResiduals
mod_dis.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod_dis.res)
```

```{r}
testDispersion(mod_dis.res)
```

### Sumamry
```{r}
summary(mod_dis)
```



## Model: burn/unburned
```{r}
mod2 = glm(mean_gcc_25cm ~ burn_unburn, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

### Sumamry
```{r}
summary(mod2)
```

### Graph

```{r}
(mod2_graph = data.frame(summary(lsmeans(mod2, pairwise ~ burn_unburn),type = "response")))
```

```{r}
levels(mod2_graph$lsmeans.burn_unburn)[levels(mod2_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod2_graph$lsmeans.burn_unburn)[levels(mod2_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod2_graph1 = dplyr::select(mod2_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod2_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod2_graph1 = data.frame(mod2_graph1)
mod2_graph1

```



```{r}
mod2_graph = ggplot(data = mod2_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("tan", "darkgreen")) + 
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))

mod2_graph  
```

## Model: burn year
```{r}
mod3 = glm(mean_gcc_25cm ~ burn_year, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

### Sumamry
```{r}
summary(mod3)
```

### Graph

```{r}
(mod3_graph = data.frame(summary(lsmeans(mod3, ~ burn_year),type = "response")))
```

```{r}


( mod3_graph1 = dplyr::select(mod3_graph, burn_year:asymp.UCL))



names(mod3_graph1)[1:6] = c("burn_year", "response", "se", "df", "lcl", "ucl")
mod3_graph1 = data.frame(mod3_graph1)
mod3_graph1

```



```{r}
mod3_graph = ggplot(data = mod3_graph1, aes(x = burn_year, y = response, color = burn_year) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#000000", "#E69F00", "#56B4E9", "#009E73")) + 
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))

mod3_graph  
```


## Model: burn/unburned + burn year
```{r}
mod4 = glm(mean_gcc_25cm ~ burn_year + burn_unburn, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

### Sumamry
```{r}
summary(mod4)
```

### Graph

```{r}
(mod4_graph = data.frame(summary(lsmeans(mod4, ~ burn_year + burn_unburn),type = "response")))
```

```{r}
levels(mod4_graph$burn_unburn)[levels(mod4_graph$burn_unburn)=="burned"] = "Burned"
levels(mod4_graph$burn_unburn)[levels(mod4_graph$burn_unburn)=="unburned"] = "Unburned"


( mod4_graph1 = dplyr::select(mod4_graph, burn_year:asymp.UCL))



names(mod4_graph1)[1:7] = c("burn_year","burn_unburn", "response", "se", "df", "lcl", "ucl")
mod4_graph1 = data.frame(mod4_graph1)
mod4_graph1

```



```{r}
mod4_graph = ggplot(data = mod4_graph1, aes(x = burn_year, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))

mod4_graph  
```




## Model: GCC as a function of proportion of Live trees + burn year
fit10 = glm.nb(seedling.ct ~ prop.canopy + prop.opencone + prop.cone.ct + offset(log(seedling.area)), data = fire2)
```{r}
mod5 = glm(mean_gcc_tree ~ prop_live + burn_year + offset(log(radius)), data = tree_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

### Sumamry
```{r}
summary(mod5)
```

### Graph

```{r}
(mod5_graph = data.frame(summary(lsmeans(mod5, ~ prop_live + burn_year + offset(log(radius))),type = "response")))
```

```{r}

names(mod5_graph)[4:8] = c("response", "se", "df", "lcl", "ucl")
mod5_graph1 = data.frame(mod5_graph)
mod5_graph1

```



```{r}
mod5_graph = ggplot(data = mod5_graph1, aes(x = burn_year, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))

mod4_graph  
```

## Model: GCC as a function of proportion of Live trees 
fit10 = glm.nb(seedling.ct ~ prop.canopy + prop.opencone + prop.cone.ct + offset(log(seedling.area)), data = fire2)
```{r}
mod6 = glm(mean_gcc_tree ~ prop_live + offset(log(radius)), data = tree_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod5.res)
```

### Sumamry
```{r}
summary(mod5)
```

### Graph

```{r}
(mod5_graph = data.frame(summary(lsmeans(mod5, ~ prop_live + burn_year + offset(log(radius))),type = "response")))
```

```{r}

names(mod5_graph)[4:8] = c("response", "se", "df", "lcl", "ucl")
mod5_graph1 = data.frame(mod5_graph)
mod5_graph1

```



```{r}
mod5_graph = ggplot(data = mod5_graph1, aes(x = burn_year, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))

mod4_graph  
```

