---
title: "Field and UAv Data Analysis"
author: "Anna Talucci"
date: "2/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_area_sampled_m2))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_area_sampled_m2))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/ndvi_all.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Data visualization


```{r}
ggplot(data = field_gcc, aes(x = plot_dis , y = mean_gcc_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean gcc (25cm)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = field_gcc, aes(x = transect_ID , y = shrub_total_ba, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("shrub basal area") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```

```{r}
ggplot(data = field_gcc, aes(x = transect_ID , y = tree_total_ba, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("Tree basal area") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```

```{r}
ggplot(data = field_gcc, aes(x = transect_ID , y = prop_live, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("Proportion live trees") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```


Boxplot with points
```{r}
ggplot(data = field_gcc, aes(x = transect_ID , y = mean_gcc_25cm, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("mean gcc (25cm)") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```
```{r}
ggplot(data = field_gcc_ndvi, aes(x = mean_ndvi_25cm , y = mean_ndvi_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean ndvi (25cm)") +
          xlab("")  +
          theme_bw() 
```

```{r}
ggplot(data = field_gcc_ndvi, aes(x = mean_gcc_25cm , y = mean_ndvi_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean ndvi (25cm)") +
          xlab("mean gcc (25cm)")  +
          theme_bw() 
```

```{r}
ggplot(data = field_gcc, aes(x = plot_dis , y = mean_gcc_1m, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc (1m)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = field_gcc, aes(x = plot_dis , y = mean_gcc_3m, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc (3m)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = field_gcc, aes(x = prop_live , y = mean_gcc_tree, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc") +
          xlab("proportion live trees")  +
          theme_bw() 
```


```{r}
ggplot(data = field_gcc, aes(x = shrub_ct , y = mean_gcc_shrub, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc") +
          xlab("shrub abundance")  +
          theme_bw() 
```

# Analysis: 

# Part 1: GCC relates to NDVI

Assess spatial scale...


## 1. Model: NDVIas  function of GCC
```{r}
mod1 = glm(mean_ndvi_25cm ~ mean_gcc_25cm, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod1.res = simulateResiduals(fittedModel = mod1, n = 500)
mod1.res$scaledResiduals
mod1.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod1.res)
```

```{r}
testDispersion(mod1.res)
```

### Sumamry
```{r}
summary(mod1)
```

```{r}
with(summary(mod1), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod1, ~ mean_gcc_25cm), type = "response"))
```

### Data for graph
```{r}
preddat_mod1 = data.frame(mean_gcc_25cm = field_gcc_ndvi$mean_gcc_25cm)

head(preddat_mod1)

pred_mod1 = predict(mod1, newdata = preddat_mod1, se.fit = TRUE)

UL_mod1 = with(pred_mod1, fit + 2*se.fit)
LL_mod1 = with(pred_mod1, fit - 2*se.fit)

field_gcc_ndvi1 = mutate(field_gcc_ndvi, pred_mod1 = pred_mod1$fit, 
               ucl_mod1 = UL_mod1, 
               lcl_mod1 = LL_mod1)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod1 = ggplot(data = field_gcc_ndvi1, aes(x = mean_gcc_25cm, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod1), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod1), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (25cm)") +
    xlab("Mean GCC (25cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(0.32, 0.37, 0.42, 0.47)) 

plot_mod1
```


## 2. Model: NDVIas  function of GCC
```{r}
mod2 = glm(mean_ndvi_50cm ~ mean_gcc_50cm, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

### Sumamry
```{r}
summary(mod2)
```

```{r}
with(summary(mod2), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod2, ~ mean_gcc_50cm), type = "response"))
```

### Data for graph
```{r}
preddat_mod2 = data.frame(mean_gcc_50cm = field_gcc_ndvi$mean_gcc_50cm)

head(preddat_mod2)

pred_mod2 = predict(mod2, newdata = preddat_mod2, se.fit = TRUE)

UL_mod2 = with(pred_mod2, fit + 2*se.fit)
LL_mod2 = with(pred_mod2, fit - 2*se.fit)

field_gcc_ndvi2 = mutate(field_gcc_ndvi, pred_mod2 = pred_mod2$fit, 
               ucl_mod2 = UL_mod2, 
               lcl_mod2 = LL_mod2)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod2 = ggplot(data = field_gcc_ndvi2, aes(x = mean_gcc_50cm, y = mean_ndvi_50cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod2), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod2, ymax = ucl_mod2, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod2), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod2), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (50cm)") +
    xlab("Mean GCC (50cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod2
```

## 3. Model: NDVIas  function of GCC
```{r}
mod3 = glm(mean_ndvi_1m ~ mean_gcc_1m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

### Sumamry
```{r}
summary(mod3)
```

```{r}
with(summary(mod3), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod3, ~ mean_gcc_1m), type = "response"))
```

### Data for graph
```{r}
preddat_mod3 = data.frame(mean_gcc_1m = field_gcc_ndvi$mean_gcc_1m)

head(preddat_mod3)

pred_mod3 = predict(mod3, newdata = preddat_mod3, se.fit = TRUE)

UL_mod3 = with(pred_mod3, fit + 2*se.fit)
LL_mod3 = with(pred_mod3, fit - 2*se.fit)

field_gcc_ndvi3 = mutate(field_gcc_ndvi, pred_mod3 = pred_mod3$fit, 
               ucl_mod3 = UL_mod3, 
               lcl_mod3 = LL_mod3)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod3 = ggplot(data = field_gcc_ndvi3, aes(x = mean_gcc_1m, y = mean_ndvi_1m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod3), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod3, ymax = ucl_mod3, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod3), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod3), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (1m)") +
    xlab("Mean GCC  (1m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod3
```

## 4. Model: NDVIas  function of GCC
```{r}
mod4 = glm(mean_ndvi_3m ~ mean_gcc_3m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

### Sumamry
```{r}
summary(mod4)
```

```{r}
with(summary(mod4), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod4, ~ mean_gcc_3m), type = "response"))
```

### Data for graph
```{r}
preddat_mod4 = data.frame(mean_gcc_3m = field_gcc_ndvi$mean_gcc_3m)

head(preddat_mod4)

pred_mod4 = predict(mod4, newdata = preddat_mod4, se.fit = TRUE)

UL_mod4 = with(pred_mod4, fit + 2*se.fit)
LL_mod4 = with(pred_mod4, fit - 2*se.fit)

field_gcc_ndvi4 = mutate(field_gcc_ndvi, pred_mod4 = pred_mod4$fit, 
               ucl_mod4 = UL_mod4, 
               lcl_mod4 = LL_mod4)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod4 = ggplot(data = field_gcc_ndvi4, aes(x = mean_gcc_3m, y = mean_ndvi_3m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod4), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod4, ymax = ucl_mod4, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod4), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod4), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (3m)") +
    xlab("Mean GCC (3m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks=c(0.0, 0.1, 0.2))

plot_mod4
```

## 5. Model: NDVIas  function of GCC
```{r}
mod5 = glm(mean_ndvi_5m ~ mean_gcc_5m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

### Sumamry
```{r}
summary(mod5)
```

```{r}
with(summary(mod5), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod5, ~ mean_gcc_5m), type = "response"))
```

### Data for graph
```{r}
preddat_mod5 = data.frame(mean_gcc_5m = field_gcc_ndvi$mean_gcc_5m)

head(preddat_mod5)

pred_mod5 = predict(mod5, newdata = preddat_mod5, se.fit = TRUE)

UL_mod5 = with(pred_mod5, fit + 2*se.fit)
LL_mod5 = with(pred_mod5, fit - 2*se.fit)

field_gcc_ndvi5 = mutate(field_gcc_ndvi, pred_mod5 = pred_mod5$fit, 
               ucl_mod5 = UL_mod5, 
               lcl_mod5 = LL_mod5)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod5 = ggplot(data = field_gcc_ndvi5, aes(x = mean_gcc_5m, y = mean_ndvi_5m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod5), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod5, ymax = ucl_mod5, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod5), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod5), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (5m)") +
    xlab("Mean GCC (5m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks=c(0.0, 0.1))

plot_mod5
```

## 6. Model: NDVIas  function of GCC
```{r}
mod6 = glm(mean_ndvi_10m ~ mean_gcc_10m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod6.res)
```

### Sumamry
```{r}
summary(mod6)
```

```{r}
with(summary(mod6), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod6, ~ mean_gcc_10m), type = "response"))
```

### Data for graph
```{r}
preddat_mod6 = data.frame(mean_gcc_10m = field_gcc_ndvi$mean_gcc_10m)

head(preddat_mod6)

pred_mod6 = predict(mod6, newdata = preddat_mod6, se.fit = TRUE)

UL_mod6 = with(pred_mod6, fit + 2*se.fit)
LL_mod6 = with(pred_mod6, fit - 2*se.fit)

field_gcc_ndvi6 = mutate(field_gcc_ndvi, pred_mod6 = pred_mod6$fit, 
               ucl_mod6 = UL_mod6, 
               lcl_mod6 = LL_mod6)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod6 = ggplot(data = field_gcc_ndvi6, aes(x = mean_gcc_10m, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod6), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod6, ymax = ucl_mod6, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod6), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod6), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI  (10m)") +
    xlab("Mean GCC (10m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks=c(0.0, 0.1))

plot_mod6
```

# Part 2:  Post-fire

## 7. Model: GCC burn/unburned
```{r}
mod7 = glm(mean_gcc_10m ~ burn_unburn, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod7.res = simulateResiduals(fittedModel = mod7, n = 500)
mod7.res$scaledResiduals
mod7.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod7.res)
```

```{r}
testDispersion(mod7.res)
```

### Sumamry
```{r}
summary(mod7)
```

### Data for graph

```{r}
(mod7_graph = data.frame(summary(lsmeans(mod7, pairwise ~ burn_unburn),type = "response")))
```

```{r}
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod7_graph1 = dplyr::select(mod7_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod7_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod7_graph1 = data.frame(mod7_graph1)
mod7_graph1

```

### Graph

```{r}
plot_mod7 = ggplot(data = mod7_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod7 
```


## 8. Model: NDVI burn/unburned
```{r}
mod8 = glm(mean_ndvi_10m ~ burn_unburn, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod8.res = simulateResiduals(fittedModel = mod8, n = 500)
mod8.res$scaledResiduals
mod8.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod8.res)
```

```{r}
testDispersion(mod8.res)
```

### Sumamry
```{r}
summary(mod8)
```

### Data for graph

```{r}
(mod8_graph = data.frame(summary(lsmeans(mod8, pairwise ~ burn_unburn),type = "response")))
```

```{r}
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod8_graph1 = dplyr::select(mod8_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod8_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod8_graph1 = data.frame(mod8_graph1)
mod8_graph1

```

### Graph

```{r}
plot_mod8 = ggplot(data = mod8_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod8 
```



## 9. Model: GCC by burn-year 
```{r}
mod9 = glm(mean_gcc_10m ~ burn_year:burn_unburn, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod9.res = simulateResiduals(fittedModel = mod9, n = 500)
mod9.res$scaledResiduals
mod9.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod9.res)
```

```{r}
testDispersion(mod9.res)
```

### Sumamry
```{r}
summary(mod9)
```


```{r}
with(summary(mod9), 1 - deviance/null.deviance)
```

### Data for Graph

```{r}
(mod9_graph = data.frame(summary(lsmeans(mod9, ~ burn_year:burn_unburn),type = "response")))
```



### Graph 

```{r}
plot_mod9 = ggplot(data = mod9_graph, aes(x = burn_year, y = lsmean, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme 

plot_mod9  
```

## 10. Model: NDVI as a function of burn year
```{r}
mod10 = glm(mean_ndvi_10m ~ burn_year:burn_unburn, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod10.res = simulateResiduals(fittedModel = mod10, n = 500)
mod10.res$scaledResiduals
mod10.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod10.res)
```

```{r}
testDispersion(mod10.res)
```

### Sumamry
```{r}
summary(mod10)
```

### Data for Graph

```{r}
(mod10_graph = data.frame(summary(lsmeans(mod10, ~ burn_year:burn_unburn),type = "response")))
```




### Graph 

```{r}
plot_mod10 = ggplot(data = mod10_graph, aes(x = burn_year, y = lsmean, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean NDVI") +
   scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme 

plot_mod10  
```




## 11. Model: GCC distance from unburned edge 
```{r}
mod11 = glm(mean_gcc_10m ~ plot_dis, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod11.res = simulateResiduals(fittedModel = mod1, n = 500)
mod11.res$scaledResiduals
mod11.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod11.res)
```

```{r}
testDispersion(mod11.res)
```

### Sumamry
```{r}
summary(mod11)
```

```{r}
(mod11_sum = data.frame(summary(lsmeans(mod11, ~ plot_dis),type = "response")))
```

### Predicted data for for graph
```{r}
preddat_mod11 = data.frame(plot_dis = field_gcc$plot_dis)

head(preddat_mod11)

pred_mod11 = predict(mod11, newdata = preddat_mod11, se.fit = TRUE)

UL_mod11 = with(pred_mod11, fit + 2*se.fit)
LL_mod11 = with(pred_mod11, fit - 2*se.fit)

field_gcc11 = mutate(field_gcc, pred_mod11 = (pred_mod11$fit), 
               ucl_mod11 = (UL_mod11), 
               lcl_mod11 = (LL_mod11))
```


### Graph  

```{r}
plot_mod11 = ggplot(data = field_gcc11, aes(x = plot_dis, y = mean_gcc_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod11), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod11, ymax = ucl_mod11, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod11), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod11), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean GCC") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_y_continuous(breaks = c(0.34, 0.36, 0.38, 0.40, 0.42)) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod11
```


## 12.  Model: NDVI distance from edge
```{r}
mod12 = glm(mean_ndvi_10m ~ plot_dis, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod12.res = simulateResiduals(fittedModel = mod12, n = 500)
mod12.res$scaledResiduals
mod12.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod12.res)
```

```{r}
testDispersion(mod12.res)
```

### Sumamry
```{r}
summary(mod12)
```

```{r}
(mod12_sum = data.frame(summary(lsmeans(mod12, ~ plot_dis),type = "response")))
```

```{r}
preddat_mod12 = data.frame(plot_dis = field_gcc_ndvi$plot_dis)

head(preddat_mod12)

pred_mod12 = predict(mod12, newdata = preddat_mod12, se.fit = TRUE)

UL_mod12 = with(pred_mod12, fit + 2*se.fit)
LL_mod12 = with(pred_mod12, fit - 2*se.fit)

field_gcc_ndvi12 = mutate(field_gcc_ndvi, pred_mod12 = (pred_mod12$fit), 
               ucl_mod12 = (UL_mod12), 
               lcl_mod12 = (LL_mod12))
```

### Graph  

```{r}
plot_mod12 = ggplot(data = field_gcc_ndvi12, aes(x = plot_dis, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod12), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod12, ymax = ucl_mod12, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod12), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod12), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean NDVI") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme + guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod12
```



# Part 3: Vegetation cover

## 13. Model: GCC proportion of Live trees

```{r}
mod13 = glm(mean_gcc_tree ~ prop_live, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod13.res = simulateResiduals(fittedModel = mod13, n = 500)
mod13.res$scaledResiduals
mod13.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod13.res)
```

```{r}
testDispersion(mod13.res)
```

### Sumamry
```{r}
summary(mod13)
```

### Data for graph
```{r}
lsmeans(mod13, ~ prop_live)

```

```{r}
(mod13_graph = data.frame(summary(lsmeans(mod13, ~ prop_live), type = "response")))
```



```{r}
preddat13 = data.frame(prop_live = field_gcc$prop_live)

head(preddat13)

pred13 = predict(mod13, newdata = preddat13, se.fit = TRUE)

UL13 = with(pred13, fit + 2*se.fit)
LL13 = with(pred13, fit - 2*se.fit)

field_gcc13 = mutate(field_gcc, pred13 = pred13$fit, 
               ucl_mod13 = UL13, 
               lcl_mod13 = LL13)
```

```{r}
min(field_gcc$mean_gcc_tree)
mean(field_gcc$tree_area_sampled_m2)
min(field_gcc$tree_area_sampled_m2)
median(field_gcc$tree_area_sampled_m2)
max(field_gcc$tree_area_sampled_m2)
```
### Graph

```{r}
plot_mod13 = ggplot(data = field_gcc13, aes(x = prop_live, y = mean_gcc_tree)) + 
  geom_point(size = 2) +
    geom_line(aes(y = pred13), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod13, ymax = ucl_mod13, color = NULL), alpha = .15) +
    geom_line(aes(y= lcl_mod13), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod13), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Proportion of live trees")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod13
```


## 14. Model: GCC tree  BA
```{r}
mod14 = glm(mean_gcc_tree ~ tree_total_ba, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod14.res = simulateResiduals(fittedModel = mod14, n = 500)
mod14.res$scaledResiduals
mod14.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod14.res)
```

```{r}
testDispersion(mod14.res)
```

### Sumamry
```{r}
summary(mod14)
```

### Data for graph

```{r}
(mod14_graph = data.frame(summary(lsmeans(mod14, ~ tree_total_ba),type = "response")))
```



```{r}
preddat_mod14 = data.frame(tree_total_ba = field_gcc$tree_total_ba)

head(preddat_mod14)

pred_mod14 = predict(mod14, newdata = preddat_mod14, se.fit = TRUE)

UL_mod14 = with(pred_mod14, fit + 2*se.fit)
LL_mod14 = with(pred_mod14, fit - 2*se.fit)

field_gcc14 = mutate(field_gcc, pred_mod14 = pred_mod14$fit, 
               ucl_mod14 = UL_mod14, 
               lcl_mod14 = LL_mod14)
```

### Graph

```{r}
plot_mod14 = ggplot(data = field_gcc14, aes(x = tree_total_ba, y = mean_gcc_tree)) + 
  geom_point(size = 2) +
    geom_line(aes(y = pred_mod14), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod14, ymax = ucl_mod14, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod14), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod14), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Tree total basal area" ~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod14
```

## 15. Model: GCC shrub  BA

```{r}
mod15 = glm(mean_gcc_shrub ~ shrub_total_ba, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod15.res = simulateResiduals(fittedModel = mod15, n = 500)
mod15.res$scaledResiduals
mod15.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot tofall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod15.res)
```

```{r}
testDispersion(mod15.res)
```

### Sumamry
```{r}
summary(mod15)
```

### Data for graph

```{r}
(mod15_graph = data.frame(summary(lsmeans(mod15, ~ shrub_total_ba),type = "response")))
```


```{r}
preddat_mod15 = data.frame(shrub_total_ba = field_gcc$shrub_total_ba)

head(preddat_mod15)

pred_mod15 = predict(mod15, newdata = preddat_mod15, se.fit = TRUE)

UL_mod15 = with(pred_mod15, fit + 2*se.fit)
LL_mod15 = with(pred_mod15, fit - 2*se.fit)

field_gcc15 = mutate(field_gcc, pred_mod15 = pred_mod15$fit, 
               ucl_mod15 = UL_mod15, 
               lcl_mod15 = LL_mod15)
```

### Graph

```{r}
plot_mod15 = ggplot(data = field_gcc15, aes(x = shrub_total_ba, y = mean_gcc_tree)) +
  geom_point(size = 2) +
    geom_line(aes(y = pred_mod15), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod15, ymax = ucl_mod15, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod15), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod15), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Shrub total basal area" ~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod15
```



## 16. Model: NDVI tree BA

```{r}
mod16 = glm(mean_ndvi_tree ~ tree_total_ba, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod16.res = simulateResiduals(fittedModel = mod16, n = 500)
mod16.res$scaledResiduals
mod16.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod16.res)
```

```{r}
testDispersion(mod16.res)
```

### Sumamry
```{r}
summary(mod16)
```

### Data for graph

```{r}
(mod16_graph = data.frame(summary(lsmeans(mod16, ~ tree_total_ba),type = "response")))
```


```{r}
preddat_mod16 = data.frame(tree_total_ba = field_gcc_ndvi$tree_total_ba)

head(preddat_mod16)

pred_mod16 = predict(mod16, newdata = preddat_mod16, se.fit = TRUE)

UL_mod16 = with(pred_mod16, fit + 2*se.fit)
LL_mod16 = with(pred_mod16, fit - 2*se.fit)

field_gcc_ndvi16 = mutate(field_gcc_ndvi, pred_mod16 = pred_mod16$fit, 
               ucl_mod16 = UL_mod16, 
               lcl_mod16 = LL_mod16)
```

### Graph

```{r}
plot_mod16 = ggplot(data = field_gcc_ndvi16, aes(x = tree_total_ba, y = mean_ndvi_tree)) +
  geom_point(size = 2) +
    geom_line(aes(y = pred_mod16), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod16, ymax = ucl_mod16, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod16), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod16), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Tree total basal area"~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod16
```

## 17. Model: NDVI shrub BA

```{r}
mod17 = glm(mean_ndvi_shrub ~ shrub_total_ba, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod17.res = simulateResiduals(fittedModel = mod17, n = 500)
mod17.res$scaledResiduals
mod17.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod17.res)
```

```{r}
testDispersion(mod17.res)
```

### Sumamry
```{r}
summary(mod17)
```

### Data for graph

```{r}
(mod17_graph = data.frame(summary(lsmeans(mod17, ~ shrub_total_ba),type = "response")))
```

```{r}
preddat_mod17 = data.frame(shrub_total_ba = field_gcc_ndvi$shrub_total_ba)

head(preddat_mod17)

pred_mod17 = predict(mod17, newdata = preddat_mod17, se.fit = TRUE)

UL_mod17 = with(pred_mod17, fit + 2*se.fit)
LL_mod17 = with(pred_mod17, fit - 2*se.fit)

field_gcc_ndvi17 = mutate(field_gcc_ndvi, pred_mod17 = pred_mod17$fit, 
               ucl_mod17 = UL_mod17, 
               lcl_mod17 = LL_mod17)
```

### Graph

```{r}
plot_mod17 = ggplot(data = field_gcc_ndvi17, aes(x = shrub_total_ba, y = mean_ndvi_shrub)) + geom_point(size = 2) +
    geom_line(aes(y = pred_mod17), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod17, ymax = ucl_mod17, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod17), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod17), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Shrub total basal area" ~(m^2))  +
    scale_y_continuous(breaks=c(0.05,0.1, 0.15)) +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod17
```


## 18. Model: NDVI proportion of Live trees

```{r}
mod18 = glm(mean_ndvi_tree ~ prop_live, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod18.res = simulateResiduals(fittedModel = mod18, n = 500)
mod18.res$scaledResiduals
mod18.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod18.res)
```

```{r}
testDispersion(mod18.res)
```

### Sumamry
```{r}
summary(mod18)
```

### Data for graph

```{r}
(mod18_graph = data.frame(summary(lsmeans(mod18, ~ prop_live), type = "response")))
```

```{r}

names(mod18_graph)[5:6] = c("lcl", "ucl")
mod18_graph1 = data.frame(mod18_graph)
mod18_graph1

```

```{r}
preddat18 = data.frame(prop_live = field_gcc_ndvi$prop_live)

head(preddat18)

pred18 = predict(mod18, newdata = preddat18, se.fit = TRUE)

UL18 = with(pred18, fit + 2*se.fit)
LL18 = with(pred18, fit - 2*se.fit)

field_gcc_ndvi18 = mutate(field_gcc_ndvi, pred18 = pred18$fit, 
               ucl_mod18 = UL18, 
               lcl_mod18 = LL18)
```


### Graph

```{r}
plot_mod18 = ggplot(data = field_gcc_ndvi18, aes(x = prop_live, y = mean_ndvi_tree)) + 
  geom_point(size = 2) +
    geom_line(aes(y = pred18), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod18, ymax = ucl_mod18, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod18), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod18), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Proportion of live trees")  +
    scale_y_continuous(breaks=c(0.05,0.1, 0.15)) +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod18
```









# Manuscript Figures 

## Part 1: Vegetation Indices

```{r fig.height=7, fig.width=6}

grid_plot_vi = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_vi

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-31_VI-gcc-ndvi.jpeg", plot = grid_plot_vi, width = 6, height = 7, units = c("in"), dpi=600 )
```

## Part 2: Post-fire

### Burned vs. Unburned + Burn Year
```{r fig.height=6, fig.width=6}

grid_plot_burn = cowplot::plot_grid(plot_mod7, plot_mod8, plot_mod9, plot_mod10, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_plot_burn

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-31_burn-unburn-year.jpeg", plot = grid_plot_burn, width = 6, height = 6, units = c("in"), dpi=600 )
```

### Distance from unburned edge

```{r fig.height=3, fig.width=6}

grid_plot_edge = cowplot::plot_grid(plot_mod11, plot_mod12, labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot_edge

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-31_distance_edge_pts.jpeg", plot = grid_plot_edge, width = 6, height = 3, units = c("in"), dpi=600 )
```


## Part 3: Vegetation  cover


```{r fig.height=7, fig.width=6}

grid_plot_veg = cowplot::plot_grid(plot_mod13, plot_mod18, plot_mod14, plot_mod16, plot_mod15, plot_mod17,    labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_veg

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-27_vegcover-gcc-ndvi.jpeg", plot = grid_plot_veg, width = 6, height = 7, units = c("in"), dpi=600 )
```

