---
title: "Field and UAv Data Analysis"
author: "Anna Talucci"
date: "2/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
```


# Field Data
```{r}
sites = read.csv("../data/field_subset/site_info_uav.csv")
shrubs = read.csv("../data/field_subset/shrub_info_uav.csv")
trees = read.csv("../data/field_subset/tree_info_uav.csv")
```

```{r}
sites
```
 Create a plot_dis column to pull out numeric values from the plot column. There  are some sites that  had two  plots  at  -25 labeled  as -25a and -25b, which is  not useful for analysis.  Unique ID and plot  include the a or b designation
```{r}
numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 

sites_subset = sites %>% mutate(plot_dis = numextract(plot)) %>% mutate(burn_unburn = ifelse(plot_dis>=0, "burned", "unburned")) %>% dplyr::select(ID, region:plot, plot_dis, burn_unburn, slope:aspect) %>% mutate(burn_year = as.factor(burn_year))
sites_subset
```
````{r}
trees_subset = trees %>% mutate(plot_dis = numextract(plot))  %>% dplyr::select(ID:plot, plot_dis, area_sampled_m2:total_ba)
shrubs_subset = shrubs %>% mutate(plot_dis = numextract(plot)) %>% dplyr::select(ID:plot, plot_dis, area_sampled_m2:salix_ba)
```


```{r}
trees
```

## field Plot sizes

```{r}
shrubs %>% group_by(site, transect) %>% 
  summarise(min(area_sampled_m2))
```

```{r}
shrubs %>% group_by(site, transect) %>% 
  summarise(max(area_sampled_m2))
```

```{r}
trees %>% group_by(site, transect) %>% 
  summarise(min(radius))
```

```{r}
trees %>% group_by(site, transect) %>% 
  summarise(max(radius))
```

# UAV Data

```{r}
gcc_1m = read.csv("../data/extracted_data/gcc_1m.csv", strip.white = TRUE)
gcc_3m = read.csv("../data/extracted_data/gcc_3m.csv", strip.white = TRUE)
gcc_25cm = read.csv("../data/extracted_data/gcc_25cm.csv", strip.white = TRUE)
gcc = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_1m = read.csv("../data/extracted_data/ndvi_1m.csv", strip.white = TRUE)
ndvi_3m = read.csv("../data/extracted_data/ndvi_3m.csv", strip.white = TRUE)
ndvi_25cm = read.csv("../data/extracted_data/ndvi_25cm.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/ndvi_all.csv", strip.white = TRUE)
```


# Combine Field and UAV

```{r}
sites_gcc = merge(sites_subset, gcc, by="ID") 
sites_gcc = sites_gcc %>% mutate(plot_dis = as.numeric(sites_gcc$plot_dis)) %>% mutate(transect_ID =  paste(site, burn_year, transect, sep = '_'))
sites_gcc
str(sites_gcc)
```

```{r}
burn_year = sites_gcc %>% dplyr::select(ID, burn_year)
burn_year
```



```{r}
merge1 = merge(trees_subset, gcc, by="ID")
merge2 = merge(burn_year, merge1, by="ID")
tree_gcc = merge2 %>% mutate(prop_live = live/stems)
tree_gcc = tree_gcc %>% mutate(plot_dis = as.numeric(sites_gcc$plot_dis))%>% mutate(transect_ID =  paste(site, burn_year, transect, sep = '_'))
tree_gcc
```

```{r}
merge12 = merge(shrubs_subset, gcc, by="ID")
shrubs_gcc = merge(burn_year, merge12, by="ID")
shrub_gcc = shrubs_gcc %>% mutate(plot_dis = as.numeric(sites_gcc$plot_dis)) %>% mutate(transect_ID =  paste(site, burn_year, transect, sep = '_'))
shrub_gcc
```
### Add NDVI

```{r}
sites_gcc_ndvi = merge(sites_gcc, ndvi_all, by = "ID")
sites_gcc_ndvi
tree_gcc_ndvi = merge(tree_gcc, ndvi_all, by = "ID")
tree_gcc_ndvi
shrub_gcc_ndvi = merge(shrubs_gcc, ndvi_all, by = "ID")
shrub_gcc_ndvi
```
# Define grpah Theme and color Palette 



```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.2, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Data visualization


```{r}
ggplot(data = sites_gcc, aes(x = plot_dis , y = mean_gcc_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean gcc (25cm)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = shrub_gcc, aes(x = transect_ID , y = total_ba, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("shrub basal area") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```

```{r}
ggplot(data = tree_gcc, aes(x = transect_ID , y = total_ba, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("Tree basal area") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```

```{r}
ggplot(data = tree_gcc, aes(x = transect_ID , y = prop_live, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("Proportion live trees") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```


## Boxplot with points
```{r}
ggplot(data = sites_gcc, aes(x = transect_ID , y = mean_gcc_25cm, color = factor(transect_ID))) +
  geom_boxplot() +       
  geom_point() +
         scale_color_manual(values=cbbPalette) +
          ylab("mean gcc (25cm)") +
          xlab("Transect ID")  +
           theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Transect ID"))
```
```{r}
ggplot(data = sites_gcc_ndvi, aes(x = mean_ndvi_25cm , y = mean_ndvi_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean ndvi (25cm)") +
          xlab("")  +
          theme_bw() 
```

```{r}
ggplot(data = sites_gcc_ndvi, aes(x = mean_gcc_25cm , y = mean_ndvi_25cm, color = factor(transect_ID))) +
         geom_point(size = 3) +
         scale_color_manual(values=cbbPalette) +
          ylab("mean ndvi (25cm)") +
          xlab("mean gcc (25cm)")  +
          theme_bw() 
```

```{r}
ggplot(data = sites_gcc, aes(x = plot_dis , y = mean_gcc_1m, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc (1m)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = sites_gcc, aes(x = plot_dis , y = mean_gcc_3m, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc (3m)") +
          xlab("distance from edge")  +
          theme_bw() 
```

```{r}
ggplot(data = tree_gcc, aes(x = prop_live , y = mean_gcc_tree, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc") +
          xlab("proportion live trees")  +
          theme_bw() 
```


```{r}
ggplot(data = shrubs_gcc, aes(x = shrub_ct , y = mean_gcc_shrub, color = factor(burn_year))) +
         geom_point(size = 3) +
         scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) +
          ylab("mean gcc") +
          xlab("shrub abundance")  +
          theme_bw() 
```

# Analysis: 

# Burned vs Unburned
# Analysis: Time Since Fire

## 15. Model: GCC as a function of transects
```{r}
mod15 = glm(mean_gcc_25cm ~ burn_year, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod15.res = simulateResiduals(fittedModel = mod15, n = 500)
mod15.res$scaledResiduals
mod15.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod15.res)
```

```{r}
testDispersion(mod15.res)
```

### Sumamry
```{r}
summary(mod15)
```

### Data for Graph

```{r}
(mod15_graph = data.frame(summary(lsmeans(mod15, ~ burn_year),type = "response")))
```

```{r}
( mod15_graph1 = dplyr::select(mod15_graph, burn_year:asymp.UCL))

names(mod15_graph1)[2:6] = c("response", "se", "df", "lcl", "ucl")
mod15_graph1 = data.frame(mod15_graph1)
mod15_graph1
```


### Graph 

```{r}
plot_mod15 = ggplot(data = mod15_graph1, aes(x = burn_year, y = response, color = burn_year) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean GCC") +
  scale_color_manual(values = cbbPalette) + 
  comp_theme 

plot_mod15  
```

## 16. Model: NDVI as a function of burn year
```{r}
mod16 = glm(mean_ndvi_25cm ~ burn_year, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod16.res = simulateResiduals(fittedModel = mod16, n = 500)
mod16.res$scaledResiduals
mod16.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod16.res)
```

```{r}
testDispersion(mod16.res)
```

### Sumamry
```{r}
summary(mod16)
```

### Data for Graph

```{r}
(mod16_graph = data.frame(summary(lsmeans(mod16, ~ burn_year),type = "response")))
```

```{r}
( mod16_graph1 = dplyr::select(mod16_graph, burn_year:asymp.UCL))

names(mod16_graph1)[2:6] = c("response", "se", "df", "lcl", "ucl")
mod16_graph1 = data.frame(mod16_graph1)
mod16_graph1
```


### Graph 

```{r}
plot_mod16 = ggplot(data = mod16_graph1, aes(x = burn_year, y = response, color = burn_year) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean NDVI") +
   scale_color_manual(values=c("#000000", "#56B4E9")) + 
  comp_theme 

plot_mod16  
```



# Analysis: Distance from Unburned

## 1. Model: GCC distance from eadge
```{r}
mod1 = glm(mean_gcc_25cm ~ plot_dis:burn_year, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod1.res = simulateResiduals(fittedModel = mod1, n = 500)
mod1.res$scaledResiduals
mod1.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod1.res)
```

```{r}
testDispersion(mod1.res)
```

### Sumamry
```{r}
summary(mod1)
```

```{r}
(mod1_sum = data.frame(summary(lsmeans(mod1, ~ plot_dis:burn_year),type = "response")))
```

### Predicted data for for graph
```{r}
preddat_mod1 = data.frame(plot_dis = sites_gcc$plot_dis, burn_year = sites_gcc$burn_year)

head(preddat_mod1)

pred_mod1 = predict(mod1, newdata = preddat_mod1, se.fit = TRUE)

UL_mod1 = with(pred_mod1, fit + 2*se.fit)
LL_mod1 = with(pred_mod1, fit - 2*se.fit)

sites_gcc1 = mutate(sites_gcc, pred_mod1 = (pred_mod1$fit), 
               ucl_mod1 = (UL_mod1), 
               lcl_mod1 = (LL_mod1))
```


### Graph  

```{r}
plot_mod1 = ggplot(data = sites_gcc1, aes(x = plot_dis, y = mean_gcc_25cm, color = factor(burn_year) )) + 
    geom_line(aes(y = pred_mod1, color = factor(burn_year)), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, fill = burn_year, color = NULL, show.legend = FALSE), alpha = .15) +
    scale_fill_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73"), guide = FALSE) + 
    geom_line(aes(y= lcl_mod1, color = factor(burn_year)), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1, color = factor(burn_year)), linetype='longdash', size = 1) +
    scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) + 
    ylab("Mean GCC (25cm)") +
    xlab("Distance from edge (m)")  +
    reg_theme + guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod1
```

### Legend
```{r}
legend1 = ggplot(data = sites_gcc1, aes(x = plot_dis, y = mean_gcc_25cm, color = factor(burn_year) )) + 
    geom_line(aes(y = pred_mod1, color = factor(burn_year)), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, fill = burn_year, color = NULL, show.legend = FALSE), alpha = .15) +
    scale_fill_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73"), guide = FALSE) + 
    geom_line(aes(y= lcl_mod1, color = factor(burn_year)), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1, color = factor(burn_year)), linetype='longdash', size = 1) +
    scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9", "#009E73")) + 
    ylab("Mean GCC (25cm)") +
    xlab("Distance from edge (m)")  +
     theme_bw() + theme(legend.position = "bottom") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.1, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black")) + guides(color=guide_legend(override.aes=list(fill=NA), title = "Year of burn")) 
legend1
```



## 6.  Model: NDVI distance from edge
canopymod1 = glmer(canopy2 ~ mortality + burncon + (1 | id), data = biomass, family = binomial(link = "logit"))
```{r}
mod6 = glm(mean_ndvi_25cm ~ plot_dis:burn_year, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod6.res)
```

### Sumamry
```{r}
summary(mod6)
```



```{r}
preddat_mod6 = data.frame(plot_dis = sites_gcc_ndvi$plot_dis, burn_year = sites_gcc_ndvi$burn_year)

head(preddat_mod6)

pred_mod6 = predict(mod6, newdata = preddat_mod6, se.fit = TRUE)

UL_mod6 = with(pred_mod6, fit + 2*se.fit)
LL_mod6 = with(pred_mod6, fit - 2*se.fit)

sites_gcc_ndvi1 = mutate(sites_gcc_ndvi, pred_mod6 = (pred_mod6$fit), 
               ucl_mod6 = (UL_mod6), 
               lcl_mod6 = (LL_mod6))
```


### Graph
```{r}
plot_mod6 = ggplot(data = sites_gcc_ndvi1, aes(x = plot_dis, y = mean_gcc_25cm, color = factor(burn_year) )) + 
    geom_line(aes(y = pred_mod6, color = factor(burn_year)), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod6, ymax = ucl_mod6, fill = burn_year, color = NULL, show.legend = FALSE), alpha = .15) +
    scale_fill_manual(values=c("#E69F00", "#56B4E9"), guide = FALSE) + 
    geom_line(aes(y= lcl_mod6, color = factor(burn_year)), linetype = 'longdash', size = 1) + 
    geom_line(aes(y= ucl_mod6, color = factor(burn_year)), linetype='longdash', size = 1) +
    scale_color_manual(values=c("#E69F00", "#56B4E9")) + 
    ylab("Mean NDVI (25cm)") +
    xlab("Distance from edge (m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod6
```


## 17. Model: GCC distance from eadge only
```{r}
mod17 = glm(mean_gcc_25cm ~ plot_dis, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod17.res = simulateResiduals(fittedModel = mod1, n = 500)
mod17.res$scaledResiduals
mod17.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod17.res)
```

```{r}
testDispersion(mod17.res)
```

### Sumamry
```{r}
summary(mod17)
```

```{r}
(mod17_sum = data.frame(summary(lsmeans(mod17, ~ plot_dis),type = "response")))
```

### Predicted data for for graph
```{r}
preddat_mod17 = data.frame(plot_dis = sites_gcc$plot_dis)

head(preddat_mod17)

pred_mod17 = predict(mod17, newdata = preddat_mod17, se.fit = TRUE)

UL_mod17 = with(pred_mod17, fit + 2*se.fit)
LL_mod17 = with(pred_mod17, fit - 2*se.fit)

sites_gcc17 = mutate(sites_gcc, pred_mod17 = (pred_mod17$fit), 
               ucl_mod17 = (UL_mod17), 
               lcl_mod17 = (LL_mod17))
```


### Graph  

```{r}
plot_mod17 = ggplot(data = sites_gcc17, aes(x = plot_dis, y = mean_gcc_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod17), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod17, ymax = ucl_mod17, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod17), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod17), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean GCC") +
    xlab("Distance from edge")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod17
```


## 18.  Model: NDVI distance from edge
canopymod1 = glmer(canopy2 ~ mortality + burncon + (1 | id), data = biomass, family = binomial(link = "logit"))
```{r}
mod18 = glm(mean_ndvi_25cm ~ plot_dis, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod18.res = simulateResiduals(fittedModel = mod18, n = 500)
mod18.res$scaledResiduals
mod18.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod18.res)
```

```{r}
testDispersion(mod18.res)
```

### Sumamry
```{r}
summary(mod18)
```



```{r}
preddat_mod18 = data.frame(plot_dis = sites_gcc_ndvi$plot_dis)

head(preddat_mod18)

pred_mod18 = predict(mod18, newdata = preddat_mod18, se.fit = TRUE)

UL_mod18 = with(pred_mod18, fit + 2*se.fit)
LL_mod18 = with(pred_mod18, fit - 2*se.fit)

sites_gcc_ndvi18 = mutate(sites_gcc_ndvi, pred_mod18 = (pred_mod18$fit), 
               ucl_mod18 = (UL_mod18), 
               lcl_mod18 = (LL_mod18))
```

### Graph  

```{r}
plot_mod18 = ggplot(data = sites_gcc_ndvi18, aes(x = plot_dis, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod18), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod18, ymax = ucl_mod18, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod18), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod18), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean NDVI") +
    xlab("Distance from edge")  +
    reg_theme + guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod18
```

# Analysis: Burned and Unburned: Difference in reflectance 

## 2. Model: GCC burn/unburned
```{r}
mod2 = glm(mean_gcc_25cm ~ burn_unburn, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

### Sumamry
```{r}
summary(mod2)
```

### Data for graph

```{r}
(mod2_graph = data.frame(summary(lsmeans(mod2, pairwise ~ burn_unburn),type = "response")))
```

```{r}
levels(mod2_graph$lsmeans.burn_unburn)[levels(mod2_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod2_graph$lsmeans.burn_unburn)[levels(mod2_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod2_graph1 = dplyr::select(mod2_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod2_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod2_graph1 = data.frame(mod2_graph1)
mod2_graph1

```

### Graph

```{r}
plot_mod2 = ggplot(data = mod2_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod2 
```


## 7. Model: NDVI burn/unburned
```{r}
mod7 = glm(mean_ndvi_25cm ~ burn_unburn, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod7.res = simulateResiduals(fittedModel = mod7, n = 500)
mod7.res$scaledResiduals
mod7.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod7.res)
```

```{r}
testDispersion(mod7.res)
```

### Sumamry
```{r}
summary(mod7)
```

### Data for graph

```{r}
(mod7_graph = data.frame(summary(lsmeans(mod7, pairwise ~ burn_unburn),type = "response")))
```

```{r}
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod7_graph1 = dplyr::select(mod7_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod7_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod7_graph1 = data.frame(mod7_graph1)
mod7_graph1

```

### Graph

```{r}
plot_mod7 = ggplot(data = mod7_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod7 
```



# Analysis Vegetation cover

## 5. Model: GCC proportion of Live trees

```{r}
head(tree_gcc)
```


```{r}
mod5 = glm(mean_gcc_tree ~ prop_live, data = tree_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

### Sumamry
```{r}
summary(mod5)
```

### Data for graph

```{r}
(mod5_graph = data.frame(summary(lsmeans(mod5, ~ prop_live), type = "response")))
```



```{r}
preddat5 = data.frame(prop_live = tree_gcc$prop_live)

head(preddat5)

pred5 = predict(mod5, newdata = preddat5, se.fit = TRUE)

UL5 = with(pred5, fit + 2*se.fit)
LL5 = with(pred5, fit - 2*se.fit)

tree_gcc5 = mutate(tree_gcc, pred5 = pred5$fit, 
               ucl_mod5 = UL5, 
               lcl_mod5 = LL5)
```

```{r}
min(tree_gcc$mean_gcc_tree)
mean(tree_gcc$area_sampled_m2)
min(tree_gcc$area_sampled_m2)
median(tree_gcc$area_sampled_m2)
max(tree_gcc$area_sampled_m2)
```
### Graph

```{r}
plot_mod5 = ggplot(data = tree_gcc5, aes(x = prop_live, y = mean_gcc_tree)) + 
    geom_line(aes(y = pred5), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod5, ymax = ucl_mod5, color = NULL), alpha = .15) +
    geom_line(aes(y= lcl_mod5), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod5), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Proportion of live trees")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod5
```


## 9. Model: GCC tree  BA

```{r}
head(tree_gcc)
```


```{r}
mod9 = glm(mean_gcc_tree ~ total_ba, data = tree_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod9.res = simulateResiduals(fittedModel = mod9, n = 500)
mod9.res$scaledResiduals
mod9.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod9.res)
```

```{r}
testDispersion(mod9.res)
```

### Sumamry
```{r}
summary(mod9)
```

### Data for graph

```{r}
(mod9_graph = data.frame(summary(lsmeans(mod9, ~ total_ba),type = "response")))
```

```{r}

names(mod9_graph)[5:6] = c("lcl", "ucl")
mod9_graph1 = data.frame(mod9_graph)
mod9_graph1

```

```{r}
preddat_mod9 = data.frame(total_ba = tree_gcc$total_ba)

head(preddat_mod9)

pred_mod9 = predict(mod9, newdata = preddat_mod9, se.fit = TRUE)

UL_mod9 = with(pred_mod9, fit + 2*se.fit)
LL_mod9 = with(pred_mod9, fit - 2*se.fit)

tree_gcc1 = mutate(tree_gcc, pred_mod9 = pred_mod9$fit, 
               ucl_mod9 = UL_mod9, 
               lcl_mod9 = LL_mod9)
```

### Graph

```{r}
plot_mod9 = ggplot(data = tree_gcc1, aes(x = total_ba, y = mean_gcc_tree)) + 
    geom_line(aes(y = pred_mod9), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod9, ymax = ucl_mod9, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod9), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod9), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Tree total basal area" ~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod9
```

## 12. Model: GCC shrub  BA

```{r}
head(shrub_gcc)
```


```{r}
mod12 = glm(mean_gcc_shrub ~ total_ba, data = shrub_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod12.res = simulateResiduals(fittedModel = mod12, n = 500)
mod12.res$scaledResiduals
mod12.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot tofall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod12.res)
```

```{r}
testDispersion(mod12.res)
```

### Sumamry
```{r}
summary(mod12)
```

### Data for graph

```{r}
(mod12_graph = data.frame(summary(lsmeans(mod12, ~ total_ba),type = "response")))
```

```{r}

names(mod12_graph)[5:6] = c("lcl", "ucl")
mod12_graph1 = data.frame(mod12_graph)
mod12_graph1

```

```{r}
preddat_mod12 = data.frame(total_ba = shrub_gcc$total_ba)

head(preddat_mod12)

pred_mod12 = predict(mod12, newdata = preddat_mod12, se.fit = TRUE)

UL_mod12 = with(pred_mod12, fit + 2*se.fit)
LL_mod12 = with(pred_mod12, fit - 2*se.fit)

shrub_gcc1 = mutate(shrub_gcc, pred_mod12 = pred_mod12$fit, 
               ucl_mod12 = UL_mod12, 
               lcl_mod12 = LL_mod12)
```

### Graph

```{r}
plot_mod12 = ggplot(data = shrub_gcc1, aes(x = total_ba, y = mean_gcc_tree)) + 
    geom_line(aes(y = pred_mod12), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod12, ymax = ucl_mod12, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod12), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod12), linetype='longdash', size = 1) +
    ylab("Mean GCC") +
    xlab("Shrub total basal area" ~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod12
```



## 10. Model: NDVI tree BA

```{r}
head(tree_gcc_ndvi)
```


```{r}
mod10 = glm(mean_ndvi_tree ~ total_ba, data = tree_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod10.res = simulateResiduals(fittedModel = mod10, n = 500)
mod10.res$scaledResiduals
mod10.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod10.res)
```

```{r}
testDispersion(mod10.res)
```

### Sumamry
```{r}
summary(mod10)
```

### Data for graph

```{r}
(mod10_graph = data.frame(summary(lsmeans(mod10, ~ total_ba),type = "response")))
```

```{r}

names(mod10_graph)[5:6] = c("lcl", "ucl")
mod10_graph1 = data.frame(mod10_graph)
mod10_graph1

```

```{r}
preddat_mod10 = data.frame(total_ba = tree_gcc_ndvi$total_ba)

head(preddat_mod10)

pred_mod10 = predict(mod10, newdata = preddat_mod10, se.fit = TRUE)

UL_mod10 = with(pred_mod10, fit + 2*se.fit)
LL_mod10 = with(pred_mod10, fit - 2*se.fit)

tree_gcc_ndvi10 = mutate(tree_gcc_ndvi, pred_mod10 = pred_mod10$fit, 
               ucl_mod10 = UL_mod10, 
               lcl_mod10 = LL_mod10)
```

### Graph

```{r}
plot_mod10 = ggplot(data = tree_gcc_ndvi10, aes(x = total_ba, y = mean_gcc_tree)) + 
    geom_line(aes(y = pred_mod10), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod10, ymax = ucl_mod10, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod10), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod10), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Tree total basal area"~(m^2))  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod10
```

## 13. Model: NDVI shrub BA

```{r}
head(shrub_gcc_ndvi)
```

```{r}
max(shrub_gcc_ndvi$mean_ndvi_shrub)
min(shrub_gcc_ndvi$mean_ndvi_shrub)
```

```{r}
mod13 = glm(mean_ndvi_shrub ~ total_ba, data = shrub_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod13.res = simulateResiduals(fittedModel = mod13, n = 500)
mod13.res$scaledResiduals
mod13.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod13.res)
```

```{r}
testDispersion(mod13.res)
```

### Sumamry
```{r}
summary(mod13)
```

### Data for graph

```{r}
(mod13_graph = data.frame(summary(lsmeans(mod13, ~ total_ba),type = "response")))
```

```{r}

names(mod13_graph)[5:6] = c("lcl", "ucl")
mod13_graph1 = data.frame(mod13_graph)
mod13_graph1

```

```{r}
preddat_mod13 = data.frame(total_ba = shrub_gcc_ndvi$total_ba)

head(preddat_mod13)

pred_mod13 = predict(mod13, newdata = preddat_mod13, se.fit = TRUE)

UL_mod13 = with(pred_mod13, fit + 2*se.fit)
LL_mod13 = with(pred_mod13, fit - 2*se.fit)

shrub_gcc_ndvi1 = mutate(shrub_gcc_ndvi, pred_mod13 = pred_mod13$fit, 
               ucl_mod13 = UL_mod13, 
               lcl_mod13 = LL_mod13)
```

### Graph

```{r}
plot_mod13 = ggplot(data = shrub_gcc_ndvi1, aes(x = total_ba, y = mean_ndvi_shrub)) + 
    geom_line(aes(y = pred_mod13), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod13, ymax = ucl_mod13, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod13), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod13), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Shrub total basal area" ~(m^2))  +
    scale_y_continuous(breaks=c(0.05,0.1, 0.15)) +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod13
```


## 11. Model: NDVI proportion of Live trees

```{r}
head(tree_gcc_ndvi)
```


```{r}
mod11 = glm(mean_ndvi_tree ~ prop_live, data = tree_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod11.res = simulateResiduals(fittedModel = mod11, n = 500)
mod11.res$scaledResiduals
mod11.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod11.res)
```

```{r}
testDispersion(mod11.res)
```

### Sumamry
```{r}
summary(mod11)
```

### Data for graph

```{r}
(mod11_graph = data.frame(summary(lsmeans(mod11, ~ prop_live), type = "response")))
```

```{r}

names(mod11_graph)[5:6] = c("lcl", "ucl")
mod11_graph1 = data.frame(mod11_graph)
mod11_graph1

```

```{r}
preddat11 = data.frame(prop_live = tree_gcc_ndvi$prop_live)

head(preddat11)

pred11 = predict(mod11, newdata = preddat11, se.fit = TRUE)

UL11 = with(pred11, fit + 2*se.fit)
LL11 = with(pred11, fit - 2*se.fit)

tree_gcc_ndvi1 = mutate(tree_gcc_ndvi, pred11 = pred11$fit, 
               ucl_mod11 = UL11, 
               lcl_mod11 = LL11)
```


### Graph

```{r}
plot_mod11 = ggplot(data = tree_gcc_ndvi1, aes(x = prop_live, y = mean_ndvi_tree)) + 
    geom_line(aes(y = pred11), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod11, ymax = ucl_mod11, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod11), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod11), linetype='longdash', size = 1) +
    ylab("Mean NDVI") +
    xlab("Proportion of live trees")  +
    scale_y_continuous(breaks=c(0.05,0.1, 0.15)) +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod11
```



# Analysis: GCC relates to NDVI

```{r}
names(sites_gcc_ndvi)
```


## 8. Model: NDVIas  function of GCC
canopymod1 = glmer(canopy2 ~ mortality + burncon + (1 | id), data = biomass, family = binomial(link = "logit"))
```{r}
mod8 = glm(mean_ndvi_25cm ~ mean_gcc_25cm:transect_ID, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod8.res = simulateResiduals(fittedModel = mod8, n = 500)
mod8.res$scaledResiduals
mod8.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod8.res)
```

```{r}
testDispersion(mod8.res)
```

### Sumamry
```{r}
summary(mod8)
```



```{r}
preddat_mod8 = data.frame(mean_gcc_25cm = sites_gcc_ndvi$mean_gcc_25cm, transect_ID = sites_gcc_ndvi$transect_ID)

head(preddat_mod8)

pred_mod8 = predict(mod8, newdata = preddat_mod8, se.fit = TRUE)

UL_mod8 = with(pred_mod8, fit + 2*se.fit)
LL_mod8 = with(pred_mod8, fit - 2*se.fit)

sites_gcc_ndvi1 = mutate(sites_gcc_ndvi, pred_mod8 = pred_mod8$fit, 
               ucl_mod8 = UL_mod8, 
               lcl_mod8 = LL_mod8)
```
### Graph
```{r}
plot_mod8 = ggplot(data = sites_gcc_ndvi1, aes(x = mean_gcc_25cm, y = mean_ndvi_25cm, color = factor(transect_ID) )) + 
    geom_line(aes(y = pred_mod8, color = factor(transect_ID)), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod8, ymax = ucl_mod8, fill = transect_ID, color = NULL, show.legend = FALSE), alpha = .15) +
    scale_fill_manual(values=c("#000000", "#E69F00", "#56B4E9"), guide = FALSE) + 
    geom_line(aes(y= lcl_mod8, color = factor(transect_ID)), linetype = 'longdash', size = 1) + 
    geom_line(aes(y= ucl_mod8, color = factor(transect_ID)), linetype='longdash', size = 1) +
    scale_color_manual(values=c("#000000", "#E69F00", "#56B4E9")) + 
    ylab("Mean NDVI (25cm)") +
    xlab("Mean GCC (25 cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod8
```






# Extra Models

## 3. Model: GCC as a function of transects
```{r}
mod3 = glm(mean_gcc_25cm ~ transect_ID, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

### Sumamry
```{r}
summary(mod3)
```

### Data for Graph

```{r}
(mod3_graph = data.frame(summary(lsmeans(mod3, ~ transect_ID),type = "response")))
```

```{r}
( mod3_graph1 = dplyr::select(mod3_graph, transect_ID:asymp.UCL))

names(mod3_graph1)[2:6] = c("response", "se", "df", "lcl", "ucl")
mod3_graph1 = data.frame(mod3_graph1)
mod3_graph1
```


### Graph 

```{r}
plot_mod3 = ggplot(data = mod3_graph1, aes(x = transect_ID, y = response, color = transect_ID) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Transect ID"), y= "Mean GCC") +
  scale_color_manual(values = cbbPalette) + 
  comp_theme 

plot_mod3  
```


## 4. Model: GCC burn/unburned + burn year

```{r}
mod4 = glm(mean_gcc_25cm ~ burn_year + burn_unburn, data = sites_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

### Sumamry
```{r}
summary(mod4)
```

### data for Graph

```{r}
(mod4_graph = data.frame(summary(lsmeans(mod4, ~ burn_year + burn_unburn),type = "response")))
```

```{r}
levels(mod4_graph$burn_unburn)[levels(mod4_graph$burn_unburn)=="burned"] = "Burned"
levels(mod4_graph$burn_unburn)[levels(mod4_graph$burn_unburn)=="unburned"] = "Unburned"


( mod4_graph1 = dplyr::select(mod4_graph, burn_year:asymp.UCL))



names(mod4_graph1)[1:7] = c("burn_year","burn_unburn", "response", "se", "df", "lcl", "ucl")
mod4_graph1 = data.frame(mod4_graph1)
mod4_graph1

```

### Graph

```{r}
mod4_graph = ggplot(data = mod4_graph1, aes(x = burn_year, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
comp_theme

mod4_graph  
```



## 14. Model: NDVI as a function of transects
```{r}
mod14 = glm(mean_ndvi_25cm ~ transect_ID, data = sites_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod14.res = simulateResiduals(fittedModel = mod14, n = 500)
mod14.res$scaledResiduals
mod14.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod14.res)
```

```{r}
testDispersion(mod14.res)
```

### Sumamry
```{r}
summary(mod14)
```

### Data for Graph

```{r}
(mod14_graph = data.frame(summary(lsmeans(mod14, ~ transect_ID),type = "response")))
```

```{r}
( mod14_graph1 = dplyr::select(mod14_graph, transect_ID:asymp.UCL))

names(mod14_graph1)[2:6] = c("response", "se", "df", "lcl", "ucl")
mod14_graph1 = data.frame(mod14_graph1)
mod14_graph1
```


### Graph 

```{r}
plot_mod14 = ggplot(data = mod14_graph1, aes(x = transect_ID, y = response, color = transect_ID) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Transect ID"), y= "Mean NDVI") +
  scale_color_manual(values = cbbPalette) + 
  comp_theme 

plot_mod14  
```






# Panel Figures 


legend = cowplot::get_legend(legend3)
(cfgrid12 = plot_grid(cfgrid11, legend, ncol=1, rel_widths = c(1, .1), rel_heights = c(1, .05)) ) 
## Figure: distance from edge + Burn year
```{r fig.height=4, fig.width=6}
legend = cowplot::get_legend(legend1)
grid_plot16 = cowplot::plot_grid(plot_mod1, plot_mod6, labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot16
grid2_plot16 = plot_grid(grid_plot16, legend, ncol=1, rel_widths = c(1, .1), rel_heights = c(1, .1)) 
grid2_plot16
```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-02_distance-burnyr.jpeg", plot = grid2_plot16, width = 6, height = 4, units = c("in"), dpi=600 )
```

## Figure: Distance from edge

```{r fig.height=3, fig.width=6}

grid_plot1718 = cowplot::plot_grid(plot_mod17, plot_mod18, labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot1718

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-11_distance_edge_pts.jpeg", plot = grid_plot1718, width = 6, height = 3, units = c("in"), dpi=600 )
```


## Figure: Burned vs. Unburned
```{r fig.height=3, fig.width=6}

grid_plot27 = cowplot::plot_grid(plot_mod2, plot_mod7, labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot27

```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-02_burn-unburn.jpeg", plot = grid_plot27, width = 6, height = 3, units = c("in"), dpi=600 )
```

##  Figure: Tree biomass
```{r fig.height=6, fig.width=6}
grid_plot591011 = cowplot::plot_grid(plot_mod5, plot_mod11, plot_mod9, plot_mod10,  labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_plot591011
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-02_tree-gcc-ndvi.jpeg", plot = grid_plot591011, width = 6, height = 6, units = c("in"), dpi=600 )
```

##  Figure: shrub biomass
```{r fig.height=3, fig.width=6}

grid_plot1213 = cowplot::plot_grid(plot_mod12, plot_mod13,  labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot1213

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-02_shrub-gcc-ndvi.jpeg", plot = grid_plot1213, width = 6, height = 3, units = c("in"), dpi=600 )
```


## Figure: vegetation cover

```{r fig.height=7, fig.width=6}

grid_plot_veg = cowplot::plot_grid(plot_mod12, plot_mod13, plot_mod9, plot_mod10, plot_mod5, plot_mod11,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_veg

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-11_vegcover-gcc-ndvi.jpeg", plot = grid_plot_veg, width = 6, height = 7, units = c("in"), dpi=600 )
```

##  Figure: GCC and NDVI by transect
```{r fig.height=5, fig.width=6}

grid_plot314 = cowplot::plot_grid(plot_mod3, plot_mod14,  labels = c("A", "B"), align = "hv", nrow= 2) 
grid_plot314

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-03-02_transect-gcc-ndvi.jpeg", plot = grid_plot314, width = 6, height = 3, units = c("in"), dpi=600 )
```