---
title: "FLARE-UAV-veg"
author: "Anna Talucci"
date: "1/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Define projections for equal area for data extraction.

Equal Area projection for russia
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 

```{r}
newproj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Packages

```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(landsat) # processes landsat images
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(SDMTools) #Species distribution model tools for patch metrics
library(dplyr)
library(latticeExtra)
```

```{r}
gps = readOGR("../data/shapefiles/siberia_gps.shp", "siberia_gps") 
```
```{r}
plot_locations <-
  read.csv("../data/gcp_coordinates.csv")
```

```{r}
plot_locations
```
```{r}
plot_locations1 = na.omit(plot_locations)
```

```{r}
plot.coords <- SpatialPointsDataFrame(plot_locations1[,5:6],plot_locations1,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```


```{r}
plots_wgs84 <- spTransform(plot.coords, CRS("+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "))


```

# Points for individual flights

Subset gps data points by individual flight numbers
## CYN

```{r}
cyn = plot_locations1 %>% group_by(site) %>% filter(site == "CYN") 

```

```{r}
cyn_pt = SpatialPointsDataFrame(cyn[,5:6], cyn,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cyn_pt_ee = spTransform(cyn_pt, CRS(newproj))
```

## Flight 3

```{r}
f3 = plot_locations1 %>% group_by(flight) %>% filter(flight == 3) 

```

```{r}
aln_f3_pt = SpatialPointsDataFrame(f3[,5:6], f3,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
aln_f3_pt_ee = spTransform(aln_f3_pt, CRS(newproj))
```

## Flight 6

```{r}
f6 = plot_locations1 %>% group_by(flight) %>% filter(flight == 6) 

```

```{r}
aln_f6_pt = SpatialPointsDataFrame(f6[,5:6], f6,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
aln_f6_pt_ee = spTransform(aln_f6_pt, CRS(newproj))
```


## Flight 14

```{r}
f14 = plot_locations1 %>% group_by(flight) %>% filter(flight == 14) 

```

```{r}
hrb_f14_pt = SpatialPointsDataFrame(f14[,5:6], f14,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
hrb_f14_pt_ee = spTransform(hrb_f14_pt, CRS(newproj))
```

## Flight 15

```{r}
f15 = plot_locations1 %>% group_by(flight) %>% filter(flight == 15) 

```

```{r}
cyn_f15_pt = SpatialPointsDataFrame(f15[,5:6], f15,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cyn_f15_pt_ee = spTransform(cyn_f15_pt, CRS(newproj))
```

Transform from sp to sf
```{r}
cyn_f15_pt_ee_sf = st_as_sf(cyn_f15_pt_ee)
```

Write shapefile to outputs
```{r}
st_write(cyn_f15_pt_ee_sf, "../outputs/shapefiles/cyn_f15_ee.shp", driver="ESRI Shapefile") 
```


## Flight 16

```{r}
f16 = plot_locations1 %>% group_by(flight) %>% filter(flight == 16) 

```

```{r}
cyn_f16_pt = SpatialPointsDataFrame(f16[,5:6], f16,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cyn_f16_pt_ee = spTransform(cyn_f16_pt, CRS(newproj))
```

## Flight 17

```{r}
f17 = plot_locations1 %>% group_by(flight) %>% filter(flight == 17) 

```

```{r}
cyn_f17_pt = SpatialPointsDataFrame(f17[,5:6], f17,
                                      proj4string = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
```

```{r}
cyn_f17_pt_ee = spTransform(cyn_f17_pt, CRS(newproj))
```

# Raster data

## Flight 3

```{r}
aln_f3 = raster("../data/ortho_stereo/ALN_TR1_FL003.tif")
```

```{r}
aln_f3
```

```{r}
extent(aln_f3)
```


```{r}
projection(aln_f3)

```

```{r}
aln_f3_ee <- projectRaster(aln_f3, crs=newproj)
```

## Flight 6

```{r}
aln_f6 = raster("../data/ortho_stereo/ALN_TR3_FL006.tif")
```


```{r}
aln_f6
```

```{r}
extent(aln_f6)
```


```{r}
projection(aln_f6)

```

```{r}
aln_f6_ee <- projectRaster(aln_f6, crs=newproj)
```


## Flight 14

```{r}
hrb_f14 = raster("../data/ortho_stereo/HRB_ALL_Fl014.tif")
```


```{r}
hrb_f14
```

```{r}
extent(hrb_f14)
```

```{r}
hrb_f14_ee <- projectRaster(hrb_f14, crs=newproj)
```

```{r}
hrb_f14_ee
```

## Flight 15

```{r}
cyn_f15 = raster("../data/ortho_stereo/CYN_TR1_FL015.tif")
```


```{r}
cyn_f15
```

```{r}
extent(cyn_f15)
```

```{r}
cyn_f15_ee <- projectRaster(cyn_f15, crs=newproj)
```

```{r}
cyn_f15_ee
```

## Flight 16

```{r}
cyn_f16 = raster("../data/ortho_stereo/CYN_TR1_FL016.tif")
```


```{r}
cyn_f16
```

```{r}
extent(cyn_f16)
```

```{r}
cyn_f16_ee <- projectRaster(cyn_f16, crs=newproj)
```

```{r}
cyn_f16_ee
```

## Flight 17

```{r}
cyn_f17 = raster("../data/ortho_stereo/CYN_TR2_FL017.tif")
```


```{r}
cyn_f17
```

```{r}
extent(cyn_f17)
```

```{r}
cyn_f17_ee <- projectRaster(cyn_f17, crs=newproj)
```

```{r}
cyn_f17_ee
```


# Plot UAV and GPS data

## Flight 3

```{r}
plot(aln_f3_ee) # the plot function lets you view the maps
plot(aln_f3_pt_ee, add=TRUE)
```

## Flight 6

```{r}
plot(aln_f6_ee) # the plot function lets you view the maps
plot(aln_f6_pt_ee, add=TRUE)
```


## Flight 14

```{r}
plot(hrb_f14_ee) # the plot function lets you view the maps
plot(hrb_f14_pt_ee, add=TRUE)
```

## Flight 15

```{r}
plot(cyn_f15_ee) # the plot function lets you view the maps
plot(cyn_f15_pt_ee, add=TRUE)
```

## Flight 16

```{r}
plot(cyn_f16_ee) # the plot function lets you view the maps
plot(cyn_f16_pt_ee, add=TRUE)
```

## Flight 17

```{r}
plot(cyn_f17_ee) # the plot function lets you view the maps
plot(cyn_f17_pt_ee, add=TRUE)
```

