---
title: "Flights and field data"
author: "Anna Talucci"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(landsat) # processes landsat images
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(SDMTools) #Species distribution model tools for patch metrics
library(dplyr)
library(latticeExtra)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```


# Field data

```{r}
field_data = read.csv("../data/field/site_info_2018-2019.csv")
```


```{r}
head(field_data)
```

```{r}
field_data
```

```{r}
field_data_ch = field_data %>% group_by(year) %>% filter(region == "Cherskiy")

```


```{r}
field_data_ch
```

```{r}
site_CN_2001 = field_data_ch %>% group_by(site) %>% filter(site == "CN")

site_CN_2001
```

```{r}
site_ANS_2003 = field_data_ch %>% group_by(site) %>% filter(site == "ANS")

site_ANS_2003
```

```{r}
site_alnus_1984 = field_data_ch %>% group_by(site) %>% filter(site == "Alnus")

site_alnus_1984
```


```{r}
site_bp_1983 = field_data_ch %>% group_by(site) %>% filter(site == "BP")

site_bp_1983
```


```{r}
ans_2003_pt <- SpatialPointsDataFrame(site_ANS_2003[,15:16],site_ANS_2003, proj4string = CRS(wgs_proj))
```

```{r}
cn_2001_pt <- SpatialPointsDataFrame(site_CN_2001[,15:16],site_CN_2001, proj4string = CRS(wgs_proj))
```

```{r}
alnus_1984_pt <- SpatialPointsDataFrame(site_alnus_1984[,15:16],site_alnus_1984, proj4string = CRS(wgs_proj))
```

```{r}
bp_1983_pt <- SpatialPointsDataFrame(site_bp_1983[,15:16],site_bp_1983, proj4string = CRS(wgs_proj))
```

```{r}
plot(cn_2001_pt)
```
```{r}
plot(ans_2003_pt)
```

```{r}
plot(alnus_1984_pt)
```

```{r}
ans_2003_ee <- spTransform(ans_2003_pt, CRS(ee_russia))
```

```{r}
cn_2001_ee <- spTransform(cn_2001_pt, CRS(ee_russia))
```

```{r}
alnus_1984_ee <- spTransform(alnus_1984_pt, CRS(ee_russia))
```

# RGB rasters

```{r}
alnus_tr1_f07 = raster("../data/rgb/ALN_TR1_FL007.tif")
brp_tr2_f12 = raster("../data/rgb/BRP_TR2_FL012.tif")
cn_tr1_f16 = raster("../data/rgb/CYN_TR1_FL016.tif")
cn_tr2_f17 = raster("../data/rgb/CYN_TR2_FL017.tif")

```


```{r}
alnus_tr1_f07
brp_tr2_f12
cn_tr1_f16
cn_tr2_f17
```

# Multispectral Raster Data
```{r}
alnus_f08_multi = raster("../data/multispectral/RU_ALN_TR1_FL008M/RU_ALN_TR1_FL008M_transparent_mosaic_green.tif")
```

```{r}
alnus_f08_multi
```

```{r}
cn_f16_multi = raster("../data/multispectral/RU_CYN_TR1_FL016B/RU_CYN_TR1_FL016B_transparent_mosaic_green.tif")
```

```{r}
cn_f16_multi
```

```{r}
cn_f17_multi = raster("../data/multispectral/RU_CYN_TR2_FL017B/RU_CYN_TR2_FL017B_transparent_mosaic_green.tif")
```

```{r}
cn_f17_multi
```

```{r}
cn_f20_multi = raster("../data/multispectral/RU_CYN_TR1_FL020M/RU_CYN_TR1_FL020M_transparent_mosaic_green.tif")
```

```{r}
cn_f20_multi
```

# Plots

## Aluns 1984 
Flight 8 - Multispectral
Flight 7 - RGB
FIeld Points from Transect 1

All seem to alighn!

```{r}
plot(alnus_f08_multi) # the plot function lets you view the maps
plot(alnus_1984_ee, add=TRUE)
```

```{r}

plot(alnus_tr1_f07)
plot(alnus_1984_ee, add=TRUE)
```

```{r}
plot(alnus_f08_multi) # the plot function lets you view the maps
plot(alnus_tr1_f07, add=TRUE)
plot(alnus_1984_ee, add=TRUE)
```


# CN 2001

* Flight 16 multispectral (Transect 1)
* Flight 17 multispectral (transect 2)
* Flight 20 multispectral (transect 1)
* Flight 16 RGB (Transect 1)
* Flight 17 RGB (Transect 2)

## Flight 16 and 20 (Transect 1)

### RGB
```{r}
plot(cn_tr1_f16)
plot(cn_2001_ee, add=TRUE)
```

### Multi
```{r}
plot(cn_f16_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

```{r}
plot(cn_f20_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

## Flight 17 (transect 2)

### RGB and Field
```{r}
plot(cn_tr2_f17) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

### Multi and Field
```{r}
plot(cn_f17_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

```{r}
plot(cn_f17_multi)
plot(cn_tr2_f17, add=TRUE)
plot(cn_2001_ee, add=TRUE)
```







