---
title: "Flights and field data"
author: "Anna Talucci"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE}
library(sp) # spatial data
library(rgdal) # geospatial data
library(raster) # deals with rasters
library(landsat) # processes landsat images
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(SDMTools) #Species distribution model tools for patch metrics
library(dplyr)
library(latticeExtra)
```

# Projections

WGS 84 need for gee
```{r}
wgs_proj =  "+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs "

```

Equal Area projection for russia need for buffering hotspot data
https://gis.stackexchange.com/questions/264093/projection-for-russia-map

+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs 
+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 

```{r}
ee_russia = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0 "
```


# Field data

```{r}
field_data = read.csv("../data/field/site_info_2018-2019.csv")
```


```{r}
head(field_data)
```

```{r}
field_data
```

```{r}
field_data_ch = field_data %>% group_by(year) %>% filter(region == "Cherskiy")

```


```{r}
field_data_ch
```

```{r}
site_CN_2001 = field_data_ch %>% group_by(site) %>% filter(site == "CN")

site_CN_2001
```

```{r}
site_ANS_2003 = field_data_ch %>% group_by(site) %>% filter(site == "ANS")

site_ANS_2003
```

```{r}
site_alnus_1984 = field_data_ch %>% group_by(site) %>% filter(site == "Alnus")

site_alnus_1984
```


```{r}
site_bp_1983 = field_data_ch %>% group_by(site) %>% filter(site == "BP")

site_bp_1983
```


```{r}
ans_2003_pt <- SpatialPointsDataFrame(site_ANS_2003[,15:16],site_ANS_2003, proj4string = CRS(wgs_proj))
```

```{r}
cn_2001_pt <- SpatialPointsDataFrame(site_CN_2001[,15:16],site_CN_2001, proj4string = CRS(wgs_proj))
```

```{r}
alnus_1984_pt <- SpatialPointsDataFrame(site_alnus_1984[,15:16],site_alnus_1984, proj4string = CRS(wgs_proj))
```

```{r}
bp_1983_pt <- SpatialPointsDataFrame(site_bp_1983[,15:16],site_bp_1983, proj4string = CRS(wgs_proj))
```

```{r}
plot(cn_2001_pt)
```
```{r}
plot(ans_2003_pt)
```

```{r}
plot(alnus_1984_pt)
```

```{r}
ans_2003_ee <- spTransform(ans_2003_pt, CRS(ee_russia))
```

```{r}
cn_2001_ee <- spTransform(cn_2001_pt, CRS(ee_russia))
```

```{r}
alnus_1984_ee <- spTransform(alnus_1984_pt, CRS(ee_russia))
```


```{r}
bp_1983_ee <- spTransform(bp_1983_pt, CRS(ee_russia))
```

# RGB rasters

```{r}
alnus_tr1_f07 = raster("../data/rgb/ALN_TR1_FL007.tif")
brp_tr2_f12 = raster("../data/rgb/BRP_TR2_FL012.tif")
cn_tr1_f16 = raster("../data/rgb/CYN_TR1_FL016.tif")
cn_tr2_f17 = raster("../data/rgb/CYN_TR2_FL017.tif")
cn_tr1_f15 = raster("../data/rgb/CYN_TR1_FL015.tif")
```

```{r}
alnus_tr1_f07
brp_tr2_f12
cn_tr1_f16
cn_tr2_f17
cn_tr1_f15 
```

```{r}
ans_tr2_f04 = raster("../data/rgb/ALN_TR2_FL004.tif")
ans_tr2_f05 = raster("../data/rgb/ALN_TR2_FL005.tif")
ans_tr3_f06 = raster("../data/rgb/ALN_TR3_FL006.tif")
brp_tr1_f09 = raster("../data/rgb/BRP_TR1_FL009.tif")

```

```{r}
ans_tr2_f04
ans_tr3_f06
brp_tr1_f09
```



# Multispectral Raster Data
```{r}
alnus_f08_multi = raster("../data/multispectral/RU_ALN_TR1_FL008M/RU_ALN_TR1_FL008M_transparent_mosaic_green.tif")
```

```{r}
alnus_f08_multi
```

```{r}
cn_f16_multi = raster("../data/multispectral/RU_CYN_TR1_FL016B/RU_CYN_TR1_FL016B_transparent_mosaic_green.tif")
```

```{r}
cn_f16_multi
```

```{r}
cn_f17_multi = raster("../data/multispectral/RU_CYN_TR2_FL017B/RU_CYN_TR2_FL017B_transparent_mosaic_green.tif")
```

```{r}
cn_f17_multi
```

```{r}
cn_f20_multi = raster("../data/multispectral/RU_CYN_TR1_FL020M/RU_CYN_TR1_FL020M_transparent_mosaic_green.tif")
```

```{r}
cn_f20_multi
```



# Plots

## Aluns 1984 
Flight 8 - Multispectral
Flight 7 - RGB
FIeld Points from Transect 1

All seem to alighn!

```{r}
plot(alnus_f08_multi) # the plot function lets you view the maps
plot(alnus_1984_ee, add=TRUE)
```

```{r}

plot(alnus_tr1_f07)
plot(alnus_1984_ee, add=TRUE)
```

```{r}
plot(alnus_f08_multi) # the plot function lets you view the maps
plot(alnus_tr1_f07, add=TRUE)
plot(alnus_1984_ee, add=TRUE)
```




## CN 2001

* Flight 16 multispectral (Transect 1)
* Flight 17 multispectral (transect 2)
* Flight 20 multispectral (transect 1)
* Flight 16 RGB (Transect 1)
* Flight 17 RGB (Transect 2)
* Flight 15 RGB (transect 1)

### Flight 16 and 20 (Transect 1)

#### RGB


```{r}
plot(cn_tr1_f15)
plot(cn_2001_ee, add=TRUE)
```

```{r}
plot(cn_tr1_f15)
plot(cn_f20_multi, add=TRUE)
plot(cn_2001_ee, add=TRUE)
```

Match up between Flight 20 multispectral, Flight 15 RGB, and field sites!

```{r}
plot(cn_tr1_f16)
plot(cn_2001_ee, add=TRUE)
```

One field site missed by flight for RGB

#### Multi
```{r}
plot(cn_f16_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

One field site missed by flight for multispectral for flight 16

```{r}
plot(cn_f20_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```


Flight 20 multispectral covers all field plots, 
### Flight 17 (transect 2)

#### RGB and Field
```{r}
plot(cn_tr2_f17) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

#### Multi and Field
```{r}
plot(cn_f17_multi) # the plot function lets you view the maps
plot(cn_2001_ee, add=TRUE)
```

```{r}
plot(cn_f17_multi)
plot(cn_tr2_f17, add=TRUE)
plot(cn_2001_ee, add=TRUE)
```

## BP 1983 (field; (1985 elena))
### Flight 12

### RGB
```{r}
plot(brp_tr2_f12)
plot(bp_1983_ee, add=TRUE)
```


```{r}
plot(brp_tr1_f09 )
plot(bp_1983_ee, add=TRUE)
```

# ANS 2003
## RGB only 

```{r}

plot(ans_tr2_f04)
plot(ans_2003_ee, add=TRUE)
```

```{r}
plot(ans_tr2_f05)
plot(ans_2003_ee, add=TRUE)
```

```{r}
plot(ans_tr3_f06)
plot(ans_2003_ee, add=TRUE)
```

# Notes to self for process

* Resample to equal pixel size
* Calculate GCC
* Calculate NDVI
* Buffer field sites to clip image
* Buffer field sites to extract data


# Elena's code for gcc
```{r}
########## Green Chromatic Index ###########

getwd()
setwd("Z:/geography-storage01.colgate.edu/data/data_repo/field_data/siberia_uas_2019/orthomosaics/ortho_exports")

install.packages("raster")
## use stack to get all 4 bands
f1 <- stack("ortho_exports/CHY_RLD_FL001.tif")

## projection
projection(f1)
# the original projection has k=0, which appears ot be wrong
# +proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +k=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs

## defining correct projection
projection(f1) <- CRS("+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")

plot(f1)

## masking to elimate unwanted values 
f1b <- mask(f1[[1:3]],f1[[4]],maskvalue=0)
plot(f1b)

## calculating gcc
gcc <- f1b[[2]]/(f1b[[1]]+f1b[[2]]+f1b[[3]])
plot(gcc)

## list files
l <- list.files(path="ortho_exports", pattern = glob2rx("*.tif"))
l
install.packages("svMisc")
## for loop (for all images in list)
for(i in 1:(length(l)))
{
  progress(i, progress.bar=TRUE)
  f1c <- stack("ortho_exports/CHY_RLD_FL001.tif")
  projection(f1c) <- CRS("+proj=stere +lat_0=90 +lat_ts=71 +lon_0=0 +k=1 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs")
  f1c <- mask(f1c[[1:3]], f1c[[4]], maskvalue=0)
  gcc <- f1c[[2]]/(f1c[[1]]+f1c[[2]]+f1c[[3]])
  o <- gsub(".tif", "_gcc.tif","list")
  # read raster stack
  # fix projection
  # mask stack
  # calculate gcc
  # write result to file
}

```

