---
title: "Map-script"
author: "Anna Talucci"
date: "4/2/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(sf)
library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
library(RStoolbox)
library(mapproj)
library(magick)
```

# Projections 

Russia Equal area projection

```{r}
ee_proj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

```{r}
laea <- "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 
```
# Raster Data

## Raster Stack for 3-band RGB Image Satellite Image

```{r}
kr_stack <- stack("../data/satellite/UAV-veg-image-sentinel.tif")
```

```{r}
extent(kr_stack)
```

# Vector Data

## World 
```{r}
data("wrld_simpl", package = "maptools")                                                                            
wm <- crop(wrld_simpl, extent(-180, 180, 60, 90))                                                                   
plot(wm) 

wm_ee <- spTransform(wm, CRSobj = CRS(laea))
plot(wm_ee)
wm_ee
wm
```

```{r}

wrld_simpl_sf = st_as_sf(wrld_simpl)
```


```{r}
wm_ru <- crop(wrld_simpl, extent(-180, -180, 40, 90))                                                                   
plot(wrld_simpl)
```


We are using relative file path names here. Note the file name is preceded by the sub-folder shapefiles in the data folder.

```{r}
shapefile <- st_read("../data/shapefiles/RUS_adm0.shp") 
```

```{r}
ru_shp <- st_transform(shapefile, CRS(newproj))


```
## Points
### transects


```{r}
plot100_pt = readOGR("../data/field-spatial/point/plot100_pt_sf.shp", "plot100_pt_sf") 
```

```{r}
plot100_pt_sf = st_as_sf(plot100_pt)
plot100_pt_sf
```

### Cherskiy
2141125, 2141260, 2497340, 2497546  (xmin, xmax, ymin, ymax)

x = 161.399713, y = 68.739907,
```{r}
coords_ch <- matrix(c(161.399713, 68.739907), 
             ncol = 2, byrow = TRUE)

ch = Poin(coords_tr)
spatpoly_tr = SpatialPolygons(list(Polygons(list(poly_tr), ID = "a")), proj4string=CRS(ee_proj))
plot(spatpoly_tr, axes = TRUE)

```

```{r}
cherskiy = st_point(c(161.399713, 68.739907))
cherskiy
```
```{r}
cherskiy = st_sf(geometry = st_sfc(st_point(c(161.399713, 68.739907))), crs = ("+proj=longlat +datum=WGS84 +no_defs"))

cherskiy
```


## Create a bounding box 

Use metadata from all_fires shapefile to identify `xmin`, `xmax`, `ymin`, and `ymax` to define the bounding box

From raster data below:
Show in New WindowClear OutputExpand/Collapse Output
class      : Extent 
xmin       : 159.9998 
xmax       : 163.0002 
ymin       : 67.24968 
ymax       : 69.25023 

```{r}
(insetrect <- data.frame(xmin = 159.9998, xmax = 163.0002, ymin = 67.24968, ymax = 69.25023)) #Replace numeric values
```


# World Map

## Worldmap  Arctic view
label = paste0(seq(60, 90, by = 10), "°N")
```{r fig.height=3.5, fig.width=3}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)

map1 = ggplot() +
  geom_polygon(data = wm, aes(x = long, y = lat, group = group), fill = "wheat", colour = "black", alpha = 0.8) +
  coord_map("ortho", orientation = c(90, 0, 0)) +
  scale_y_continuous(breaks = seq(60, 90, by = 10), labels = c("60", "", "","90")) +
  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +
  # Adds labels
  geom_text(aes(x = 0, y = seq(60, 90, by = 10), hjust = 0.4, vjust = -0.6, label = c("60°N", "", "", "90°N"))) +
  geom_text(aes(x = x_lines, y = 54, label = c("120°W", "60°W", "0°", "60°E", "120°E", "180°W"))) +
  # Adds axes
  geom_hline(aes(yintercept = 60), size = 1)  +
  geom_segment(aes(y = 60, yend = 90, x = x_lines, xend = x_lines), linetype = "dashed") +
# Change theme to remove axes and ticks
  theme_void() + 
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0), "cm")) +
theme(panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "black"),
      axis.ticks=element_blank()) +
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) 


map1
  
```


coord_map( , orientation = c(latitude,longitude,rotation)
```{r fig.height=3.5, fig.width=3}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)

map2 = ggplot() +
  geom_polygon(data = wm, aes(x = long, y = lat, group = group), fill = "wheat", colour = "black", alpha = 0.8) +
  coord_map("ortho", orientation = c(40, 90, 0)) +
  scale_y_continuous(breaks = seq(60, 90, by = 10), labels = c("60", "", "","90")) +
  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +
  # Adds labels
  geom_text(aes(x = 0, y = seq(60, 90, by = 10), hjust = 0.4, vjust = -0.6, label = c("60°N", "", "", "90°N"))) +
  geom_text(aes(x = x_lines, y = 54, label = c("120°W", "60°W", "0°", "60°E", "120°E", "180°W"))) +
  # Adds axes
  geom_hline(aes(yintercept = 60), size = 1)  +
  geom_segment(aes(y = 60, yend = 90, x = x_lines, xend = x_lines), linetype = "dashed") +
# Change theme to remove axes and ticks
  theme_void() + 
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0), "cm")) +
theme(panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "black"),
      axis.ticks=element_blank()) +
  
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) 


map2
  
```

## Russia Map

```{r}
russia_map1 <- ggplot() +
     geom_sf(data = wrld_simpl_sf, fill = "antiquewhite1") +

     coord_sf(xlim = c(30, 170), ylim = c(40, 80)) +
     xlab("Longitude") + 
   ylab("Latitude") +
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))


russia_map1
```


```{r}
russia_map2 <- ggplot() +
     geom_sf(data = wrld_simpl_sf, fill = "antiquewhite1") +

     coord_sf(xlim = c(35, 170), ylim = c(45, 75)) +
     xlab("Longitude") + 
   ylab("Latitude") +
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  theme(panel.grid.major = element_line(color = gray(0.5), linetype = "dashed", 
        size = 0.5), panel.background = element_rect(fill = "aliceblue"))


russia_map2
```




# Tansect locations

## Option 1
, labels = c("67.5°N", "", "", "90°N")
```{r fig.height=7, fig.width=3.5}
plot_raster = ggplot() + 
  ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  geom_sf(data = cherskiy, size = 3, shape = 21, fill = "cornsilk1") +
     geom_sf(data = plot100_pt_sf, size = 3, shape = 23, fill = "tomato1") +
  scale_y_continuous(breaks = seq(67.5, 69, by = .5)) +
  scale_x_continuous(breaks = seq(160.5, 162.5, by = 1)) +
  
  annotation_north_arrow(location = "tl", which_north = "true", pad_x = unit(0.4, "in"), pad_y = unit(0.5, "in"), style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 10, text_face = NULL, text_family = "serif", text_col = "black")) +
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(160.4, 162.6), ylim = c(67.5, 68.9), expand = TRUE) +
  
  theme_bw()+
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0.1), "cm")) +
  theme(panel.grid.major = element_line(colour = gray(0.5), linetype = "dashed", 
         size = 0.5), panel.background = element_blank(), 
         panel.border = element_rect(fill = NA))

plot_raster

```

## Option 2

```{r}
linecolors = c("#000000", "#000000", "#000000", "#000000")
fillcolors = c("#E69F00", "#CC79A7", "#D55E00", "#F0E442")
```

```{r}
plot_transects = ggplot() + 
  ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  geom_sf(data = cherskiy, size = 4, shape = 24, fill = "grey70") +
     annotate(geom = "text", x = 161.75, y = 68.7, label = "Cherskiy", 
    fontface = "bold", color = "grey70", size = 4) +
  geom_sf(data = plot100_pt_sf, aes(fill = site, color = site),size = 4, shape = 21, alpha= .9) +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) +
  scale_y_continuous(breaks = seq(67.5, 69, by = .5)) +
  scale_x_continuous(breaks = seq(160.5, 162.5, by = 1)) +
  
   annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.0, "cm"), pad_y = unit(0.7, "cm"), style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 0, text_face = NULL, text_family = "sans", text_col = "white")) +
  
  
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(160.4, 162.4), ylim = c(67.8, 68.8), expand = TRUE) +
  
  theme_void() +
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0.1), "cm")) +
  theme(legend.position = "bottom")

plot_transects

```
## Option 3
```{r}
plot_transects3 = ggplot() + 
  ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  geom_sf(data = cherskiy, size = 4, shape = 24, fill = "grey70") +
     annotate(geom = "text", x = 161.75, y = 68.7, label = "Cherskiy", 
    fontface = "bold", color = "grey70", size = 4) +
  geom_sf(data = plot100_pt_sf, aes(fill = site, color = site),size = 4, shape = 21, alpha= .9) +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) +
  scale_y_continuous(breaks = seq(67.5, 69, by = .5), name = "") +
  scale_x_continuous(breaks = seq(161), name = "") +
  
   annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.0, "cm"), pad_y = unit(0.7, "cm"), style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 0, text_face = NULL, text_family = "sans", text_col = "white")) +
  
  
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(160.4, 162.4), ylim = c(67.8, 68.8), expand = TRUE) +
  
  theme_bw()+
  
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0.1), "cm")) +
  theme(legend.position = "bottom")

plot_transects3

```

## Option 4
```{r}
plot_transects4 = ggplot() + 
  ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  geom_sf(data = cherskiy, size = 4, shape = 24, fill = "grey70") +
     annotate(geom = "text", x = 161.75, y = 68.7, label = "Cherskiy", 
    fontface = "bold", color = "grey70", size = 4) +
  geom_sf(data = plot100_pt_sf, aes(fill = site, color = site),size = 4, shape = 21, alpha= .9) +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) +
  scale_y_continuous(breaks = seq(67.5, 69, by = .5), name = "") +
  scale_x_continuous(breaks = seq(161, 162), name = "") +
  
   annotation_north_arrow(location = "bl", which_north = "true", pad_x = unit(0.0, "cm"), pad_y = unit(0.7, "cm"), style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 0, text_face = NULL, text_family = "sans", text_col = "white")) +
  
  
  annotation_scale(location = "bl", width_hint = 0.25, text_size = 12, text_face = "bold", text_family = "sans", text_col = "white") +
  
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(160.4, 162.4), ylim = c(67.8, 68.8), expand = TRUE) +
  
  theme_bw()+
  
  theme(plot.margin = unit(c(t = 0, r = 0, b = 0.1, l = 0.1), "cm")) +
  theme(legend.position = "none")

plot_transects4

```


# Combining Maps

We combine our study area map with the inset map for a final map figure

```{r}

photo1 = ggdraw() + draw_image("../img/photo_highseverity.PNG", scale = 0.9)
```

## Option 1
```{r fig.height=7, fig.width=6}
ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(plot_raster, x = 0, y = 0, width = 3, height = 7) +
    draw_plot(map1, x = 3, y = 3.5, width = 3, height = 3.5) +      
  draw_image("../images/UAV-Veg-1Transect.PNG", scale = 0.9, x = 3, y = 0, width = 3, height = 3.5)

```

## Option 2
```{r fig.height=7, fig.width=6}
ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(plot_raster, x = 0, y = 0, width = 3, height = 3.5) +
    draw_plot(russia_map, x = 0, y = 3.5, width = 6, height = 3.5) +      
  draw_image("../images/UAV-Veg-1Transect.PNG", scale = 0.9, x = 3, y = 0, width = 3, height = 3.5)

```


## Option 3
```{r fig.height=7, fig.width=6}
fig_man = ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(plot_transects, x = 0, y = 0, width = 3, height = 4) +
    draw_plot(russia_map1, x = 0, y = 4, width = 6, height = 3) +      
  draw_image("../images/2020-05-19_UAV-Veg-Transect-CN-bottom.PNG", scale = 0.9, x = 3, y = 0, width = 3, height = 4)

fig_man
```



```{r}
ggsave("../figures/MAP-FILE-NAME.png", plot = fig_man, width = 6, height = 7, dpi = 600)
```


## Option 4
```{r fig.height=7, fig.width=6}
fig_man = ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(plot_transects3, x = 0, y = 0, width = 3, height = 4) +
    draw_plot(russia_map2, x = 0, y = 4, width = 6, height = 3) +      
  draw_image("../images/2020-05-19_UAV-Veg-Transect-CN-bottom.PNG", scale = 0.9, x = 3, y = 0, width = 3, height = 4) +
  draw_label("Russia", 5, 6)

fig_man
```

## Option 5

, angle = 45
```{r fig.height=7, fig.width=6}
fig_maps5 = ggdraw(xlim = c(0, 6), ylim = c(0, 7)) +
    draw_plot(plot_transects4, x = 0, y = 0, width = 3, height = 4) +
    draw_plot(russia_map2, x = 0, y = 4, width = 6, height = 3) +      
  draw_image("../images/2020-05-19_UAV-Veg-Transect-CN-bottom.PNG", scale = 0.85, x = 3, y = 0.1, width = 3, height = 4) +
  draw_label("Russia", x = 3.25, y = 6, fontfamily = "sans", fontface = "bold", color = "black", size = 12) +
  draw_label("Alnus", x = 2.55, y = 1, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("ANS", x = 1.95, y = 1.85, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("BP", x = 1.25, y = 2.45, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("CN", x = 2.1, y = 3.7, fontfamily = "sans", fontface = "bold", color = "white", size = 10) +
  draw_label("N", x = 5.7, y = 0.6, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
  draw_label("Plots", x = 3.75, y = 0.6, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
  draw_label("100 m", x = 4.7, y = 0.725, fontfamily = "sans", fontface = "bold", color = "black", size = 10) +
  draw_label("A", x = 0.16, y = 6.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
   draw_label("B", x = 0.16, y = 3.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) +
   draw_label("C", x = 3.14, y = 3.8, fontfamily = "sans", fontface = "bold", color = "black", size = 14) 

fig_maps5
```

```{r}
ggsave("../figures/2020-05-19_Figure-Map.png", plot = fig_maps5, width = 6, height = 7, dpi = 600)
```

# Save map as file

Use `ggsave()` to export the map to a file. Note the relative path name. Multiple extensions are available. Width and height are defined for this figure, but should be adjusted for future figures.

**CHANGE FILE NAME!!**

```{r}
ggsave("../figures/MAP-FILE-NAMEt.png", plot = fig_manuscript, width = 6, height = 4, dpi = 600)
```

