---
title: "Map-script"
author: "Anna Talucci"
date: "4/2/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Skeleton for developing a map figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(sf)
library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
library(RStoolbox)
library(mapproj)
```
# Projections 

Russia Equal area projection

```{r}
newproj = "+proj=aea +lat_1=50 +lat_2=70 +lat_0=56 +lon_0=100 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs "
```

# Read in shapefile boundaries

We are using relative file path names here. Note the file name is preceded by the sub-folder shapefiles in the data folder.

```{r}
shapefile <- st_read("../data/shapefiles/RUS_adm0.shp") 
```

```{r}
ru_shp <- st_transform(shapefile, CRS(newproj))


```

# Create a bounding box 

Use metadata from all_fires shapefile to identify `xmin`, `xmax`, `ymin`, and `ymax` to define the bounding box

From raster data below:
Show in New WindowClear OutputExpand/Collapse Output
class      : Extent 
xmin       : 159.9998 
xmax       : 163.0002 
ymin       : 67.24968 
ymax       : 69.25023 

```{r}
(insetrect <- data.frame(xmin = 159.9998, xmax = 163.0002, ymin = 67.24968, ymax = 69.25023)) #Replace numeric values
```

# Map Making


## British Columbia with study area bounding box

This map will serve as an inset in the final map. 

**Edit data!!**
```{r}
laea <- "+proj=laea +lat_0=90 +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs" 



data("wrld_simpl", package = "maptools")                                                                            
wm <- crop(wrld_simpl, extent(-180, 180, 60, 90))                                                                   
plot(wm) 

wm_ee <- spTransform(wm, CRSobj = CRS(laea))
plot(wm_ee)
wm_ee
wm
```
```{r}

```


```{r}
# Defines the x axes required
x_lines <- seq(-120,180, by = 60)

ggplot() +
  geom_polygon(data = wm, aes(x = long, y = lat, group = group), fill = "grey", colour = "black", alpha = 0.8) +
  
  coord_map("ortho", orientation = c(90, 0, 0)) +
  scale_y_continuous(breaks = seq(60, 90, by = 5), labels = NULL) +

  # Removes Axes and labels
  scale_x_continuous(breaks = NULL) +
  xlab("") + 
  ylab("") +

  # Adds labels
  geom_text(aes(x = 0, y = seq(65, 85, by = 10), hjust = 0.4, label = paste0(seq(65, 85, by = 10), "°N"))) +
  geom_text(aes(x = x_lines, y = 54, label = c("120°W", "60°W", "0°", "60°E", "120°E", "180°W"))) +

  # Adds axes
  geom_hline(aes(yintercept = 60), size = 1)  +
  geom_segment(aes(y = 60, yend = 90, x = x_lines, xend = x_lines), linetype = "dashed") +

# Change theme to remove axes and ticks
theme(panel.background = element_blank(),
      panel.grid.major = element_line(size = 0.25, linetype = 'dashed', colour = "black"),
      axis.ticks=element_blank()) +
  
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) 



  
```




```{r}
map_inset = ggplot() + 
  geom_sf(data = ru_shp, fill = "#E8E8E8", color = "black") +
  #Use bounding box from above
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  xlab("")+ylab("")+
  coord_sf() +
   theme_void() +
  #add a bounding box so that will border the inset
  theme(panel.background = element_rect(colour = "black", fill = "white", size = 0.5))

map_inset
```

## Map with legend bottom

Here e create a map with a legend box that is placed outside of the map along the bottom. 

**Edit data!!**

```{r}
map_main = ggplot() +
  #add shapefile
  geom_sf(data = bc, aes(fill = "BC", color = "BC")) + 
  #add shapefile
  geom_sf(data = parks, aes(fill = "Parks", color = "Parks"), show.legend = TRUE) + 
  #add shapefile
  geom_sf(data = lakes, aes(fill = "Lakes", color = "Lakes"), show.legend = TRUE, key_glyph = draw_key_rect) + 
  #add shapefile
  geom_sf(data = fire1, fill = NA, aes(color = "Fire1"), size = 1, show.legend = TRUE, key_glyph = draw_key_rect) + 
  #add shapefile
  geom_sf(data = fire2, fill = NA, aes(color = "Fire2"), size = 1, show.legend = TRUE)  +
  #add shapefile
  geom_sf(data = fire3, fill = NA, aes(color = "Fire3"), size = 1, show.legend = TRUE) + 
  #manually define colors with hexcodes 
  scale_color_manual(values = c("BC" = "#E8E8E8", "Parks" = "#C3ECB2", "Lakes" = "#AADAFF", "Fire1" = "#b82b2b", "Fire2" = "#b06f0c", "Fire3" =  "#dd7116"), 
                       labels = c("British Columbia", "Chelaslie fire", "Entiako fire", "Tweedsmuir fire", "Lakes", "Provincial parks"),
                       name = "") + 
  #manual define fill; for no fill NA
  scale_fill_manual(values = c("BC" = "#E8E8E8", "Parks" = "#C3ECB2", "Lakes" = "#AADAFF", "Fire1" = NA, "Fire2" = NA, "Fire3" =  NA), guide=FALSE) + 
  #define coordinates based on shapefile metadata
  coord_sf(crs = "+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", xlim = c(983000, 1071000), ylim = c(892000, 941000), expand = FALSE)  + 
  #add a scale bar
  annotation_scale(location = "br", width_hint = 0.25, text_size = 12, text_face = NULL, text_family = "serif", text_col = "black") + 
  #add North Arrow
    annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.4, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_nautical(line_width = 1, line_col = "black", fill = c("black", "white"), text_size = 10, text_face = NULL, text_family = "serif", text_col = "black", text_angle = 0)) + 
  #define theme
  theme(axis.text.x = element_text(face = "plain", color = "black", size = 10),
        axis.text.y = element_text(face = "plain", color = "black", size = 10),
        legend.position= "bottom",
        legend.key = element_rect(fill = "white")) 

map_main
```

# Raster

## Raster Stack for 3-band RGB Image

```{r}
kr_stack <- stack("../data/satellite/UAV-veg-image-sentinel.tif")
```

```{r}
extent(kr_stack)
```

## Map with north arrow and scale bar
```{r}
plot_raster = ggplot() + ggRGB(kr_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE) +
  xlim(159.9998, 163.0002) + ylim(67.24968, 69.25023) +
  
  
  annotation_scale(location = "br", width_hint = 0.25, text_size = 12, text_face = NULL, text_family = "serif", text_col = "black") +
    annotation_north_arrow(location = "tl", which_north = "true", 
        pad_x = unit(0.4, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_minimal(line_width = 1, line_col = "white", fill = "white", text_size = 10, text_face = NULL, text_family = "serif", text_col = "black")) +
  coord_sf(crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0", xlim = c(159.9998, 163.0002), ylim = c(67.24968, 69.25023), expand = TRUE)

plot_raster

```


# UAV Transect
```{r}
f15_pt <- st_read("../data/shapefiles/cyn_f15_ee.shp") 
```

```{r}
f15_pt
```


```{r}
cyn_f15_stack = stack("../data/ortho_stereo/CYN_TR1_FL015.tif")
```

```{r}
cyn_f15_stack
```

```{r}
cyn_f15_ee <- projectRaster(cyn_f15_stack, crs=newproj)
```

```{r}
cyn_f15_ee
```
```{r}
plot(cyn_f15_stack) # the plot function lets you view the maps
plot(cyn_f15_ee, add=TRUE)
```


```{r}
 ggplot() + ggRGB(cyn_f15_stack, r=1, g=2, b=3, ggLayer = TRUE, coord_equal = TRUE)

```



# Combining Maps

We combine our study area map with the inset map for a final map figure


```{r fig.height=4, fig.width=6}
fig_manuscript = ggdraw() +
  #add base map
  draw_plot(map_main) +
  #add inset and define size and location 
  draw_plot(map_inset, x = 0.12, y = 0.32, width = .25, height = .25) 
 
fig_manuscript
```






# Save map as file

Use `ggsave()` to export the map to a file. Note the relative path name. Multiple extensions are available. Width and height are defined for this figure, but should be adjusted for future figures.

**CHANGE FILE NAME!!**

```{r}
ggsave("../figures/MAP-FILE-NAMEt.png", plot = fig_manuscript, width = 6, height = 4, dpi = 600)
```


