---
title: "Map-script"
author: "Anna Talucci"
date: "4/2/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

Skeleton for developing a amp figure for FLARE UAS vegetation paper

This script is reliant on
* `Rproj` and therefore the `wd()`does not have to be set
* Relative path names "../folder-name/file-name.ext"
* This script is reliant on the following folders 
    +"../scripts/" --this houses all scripts written in RMarkdown
    +"../data/shapfiles/" --this houses shape files
    +"../figures/
* Please reference the Git Hub repository called **FLARE-UAV-veg** to see the file structure used here

# Packages

```{r message=FALSE, warning=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)
library(sf)
library(ggmap) # devtools::install_github("dkahle/ggmap")
library(ggrepel)
library(raster)
library(rgdal)
library(rasterVis)
library(RColorBrewer)
library(cowplot)
library(ggspatial)
library(maps)
```

# Read in shapefile boundaries

We are using relative file path names here. Note the file name is preceded by the sub-folder shapefiles in the data folder.

```{r}
shapefile <- st_read("../data/shapefiles/FILE-NAME.shp") # Replace FILENAME
```


# Create a bounding box 

Use metadata from all_fires shapefile to identify `xmin`, `xmax`, `ymin`, and `ymax` to define the bounding box

```{r}
(insetrect <- data.frame(xmin = 985362, xmax = 1069051, ymin = 894097.7, ymax = 939814.2)) #Replace numeric values
```

# Map Making


## British Columbia with study area bounding box

This map will serve as an inset in the final map. 

**Edit data!!**

```{r}
map_inset = ggplot() + 
  geom_sf(data = shapefile, fill = "#E8E8E8", color = "black") +
  #Use bounding box from above
  geom_rect(data = insetrect, aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax), alpha = 0, colour = "#000080", size = 1.5, linetype = 1) +
  xlab("")+ylab("")+
  coord_sf() +
   theme_void() +
  #add a bounding box so that will border the inset
  theme(panel.background = element_rect(colour = "black", fill = "white", size = 0.5))

map_inset
```

## Map with legend bottom

Here e create a map with a legend box that is placed outside of the map along the bottom. 

**Edit data!!**

```{r}
map_main = ggplot() +
  #add shapefile
  geom_sf(data = bc, aes(fill = "BC", color = "BC")) + 
  #add shapefile
  geom_sf(data = parks, aes(fill = "Parks", color = "Parks"), show.legend = TRUE) + 
  #add shapefile
  geom_sf(data = lakes, aes(fill = "Lakes", color = "Lakes"), show.legend = TRUE, key_glyph = draw_key_rect) + 
  #add shapefile
  geom_sf(data = fire1, fill = NA, aes(color = "Fire1"), size = 1, show.legend = TRUE, key_glyph = draw_key_rect) + 
  #add shapefile
  geom_sf(data = fire2, fill = NA, aes(color = "Fire2"), size = 1, show.legend = TRUE)  +
  #add shapefile
  geom_sf(data = fire3, fill = NA, aes(color = "Fire3"), size = 1, show.legend = TRUE) + 
  #manually define colors with hexcodes 
  scale_color_manual(values = c("BC" = "#E8E8E8", "Parks" = "#C3ECB2", "Lakes" = "#AADAFF", "Fire1" = "#b82b2b", "Fire2" = "#b06f0c", "Fire3" =  "#dd7116"), 
                       labels = c("British Columbia", "Chelaslie fire", "Entiako fire", "Tweedsmuir fire", "Lakes", "Provincial parks"),
                       name = "") + 
  #manual define fill; for no fill NA
  scale_fill_manual(values = c("BC" = "#E8E8E8", "Parks" = "#C3ECB2", "Lakes" = "#AADAFF", "Fire1" = NA, "Fire2" = NA, "Fire3" =  NA), guide=FALSE) + 
  #define coordinates based on shapefile metadata
  coord_sf(crs = "+proj=aea +lat_1=50 +lat_2=58.5 +lat_0=45 +lon_0=-126 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs", xlim = c(983000, 1071000), ylim = c(892000, 941000), expand = FALSE)  + 
  #add a scale bar
  annotation_scale(location = "br", width_hint = 0.25, text_size = 12, text_face = NULL, text_family = "serif", text_col = "black") + 
  #add North Arrow
    annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.4, "in"), pad_y = unit(0.5, "in"),
        style = north_arrow_nautical(line_width = 1, line_col = "black", fill = c("black", "white"), text_size = 10, text_face = NULL, text_family = "serif", text_col = "black", text_angle = 0)) + 
  #define theme
  theme(axis.text.x = element_text(face = "plain", color = "black", size = 10),
        axis.text.y = element_text(face = "plain", color = "black", size = 10),
        legend.position= "bottom",
        legend.key = element_rect(fill = "white")) 

map_main
```

# Combining Maps

We combine our study area map with the inset map for a final map figure


```{r fig.height=4, fig.width=6}
fig_manuscript = ggdraw() +
  #add base map
  draw_plot(map_main) +
  #add inset and define size and location 
  draw_plot(map_inset, x = 0.12, y = 0.32, width = .25, height = .25) 
 
fig_manuscript
```

# Save map as file

Use `ggsave()` to export the map to a file. Note the relative path name. Multiple extensions are available. Width and height are defined for this figure, but should be adjusted for future figures.

**CHANGE FILE NAME!!**

```{r}
ggsave("../figures/MAP-FILE-NAMEt.png", plot = fig_manuscript, width = 6, height = 4, dpi = 600)
```


