---
title: "NDVI-field-extract"
author: "Anna Talucci"
date: "2/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

- Extract NDVI values



- Plot size for field data collection was variable from 4-10m radius plots
- apply 4m buffer

# Packages
```{r, include=FALSE}
library(sp) 
library(rgdal) 
library(raster) 
library(rgeos) # GIS Geometry
library(foreign) # deals with dbf files
library(dplyr)
library(ggplot2)
```


# NVDI DATA



alnus_tr1_f08
cn_tr2_f17
cn_tr1_f20 


# NDVI rasters

```{r}
alnus_tr1_f08 = raster("../data/ndvi/alnus_f08_NDVI.tif")
cn_tr2_f17 = raster("../data/ndvi/cn_f17_NDVI.tif")
cn_tr1_f20 = raster("../data/ndvi/cn_f20_NDVI.tif")
```


# Field point data

```{r}
alnus_tr1_pt = readOGR("../data/field-spatial/point/alnus_tr1_ee_pt.shp", "alnus_tr1_ee_pt")
cn_tr1_pt = readOGR("../data/field-spatial/point/cn_tr1_ee_pt.shp", "cn_tr1_ee_pt") 
cn_tr2_pt = readOGR("../data/field-spatial/point/cn_tr2_ee_pt.shp", "cn_tr2_ee_pt") 
```


## 1m - extract mean pixel values
Use 1m buffer for GCC as  function of distance from edge
extract(rasterA,points, buffer=150, fun=mean)

- Choose buffer based on pixel size and maintaining fine scale resolution but aggregating so that values are at the same spatial scale

```{r}
extract_alnus_tr1 = raster::extract(alnus_tr1_f08, alnus_tr1_pt, buffer=1, fun=mean, df=TRUE )
extract_cn_tr1 = raster::extract(cn_tr1_f20, cn_tr1_pt, buffer=1, fun=mean,  df=TRUE )
extract_cn_tr2 = raster::extract(cn_tr2_f17, cn_tr2_pt, buffer=1, fun=mean,  df=TRUE )
```


```{r}
extract_alnus_tr1$plot_id = alnus_tr1_pt$ID
names(extract_alnus_tr1) = c('ID', 'mean_gcc', 'plot_id')
extract_alnus_tr1
```

```{r}
extract_cn_tr1$plot_id = cn_tr1_pt$ID
names(extract_cn_tr1) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr1
```

```{r}
extract_cn_tr2$plot_id = cn_tr2_pt$ID
names(extract_cn_tr2) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr2
```

extract_alnus_tr1, extract_ans_tr2, extract_ans_tr3, extract_brp_tr1, extract_brp_tr2, extract_cn_tr1, extract_cn_tr2
```{r}
cn_bind = rbind(extract_cn_tr1, extract_cn_tr2)
ndvi_1m = rbind(extract_alnus_tr1, cn_bind)

ndvi_1m
```

```{r}
write.csv(ndvi_1m,"../outputs/extracted_data/ndvi_1m.csv", row.names = FALSE)
```

## 3m - extract mean pixel values
Use 1m buffer for GCC as  function of distance from edge
extract(rasterA,points, buffer=150, fun=mean)

- Choose buffer based on pixel size and maintaining fine scale resolution but aggregating so that values are at the same spatial scale

```{r}

extract_alnus_tr1_3m = raster::extract(alnus_tr1_f08, alnus_tr1_pt, buffer=3, fun=mean, df=TRUE )
extract_cn_tr1_3m = raster::extract(cn_tr1_f20, cn_tr1_pt, buffer=3, fun=mean,  df=TRUE )
extract_cn_tr2_3m = raster::extract(cn_tr2_f17, cn_tr2_pt, buffer=3, fun=mean,  df=TRUE )
```


```{r}
extract_alnus_tr1_3m$plot_id = alnus_tr1_pt$ID
names(extract_alnus_tr1_3m) = c('ID', 'mean_gcc', 'plot_id')
extract_alnus_tr1_3m
```

```{r}
extract_cn_tr1_3m$plot_id = cn_tr1_pt$ID
names(extract_cn_tr1_3m) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr1_3m
```

```{r}
extract_cn_tr2_3m$plot_id = cn_tr2_pt$ID
names(extract_cn_tr2_3m) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr2_3m
```


```{r}
cn_bind_3m = rbind(extract_cn_tr1_3m, extract_cn_tr2_3m)
ndvi_3m = rbind(extract_alnus_tr1_3m, cn_bind_3m)
ndvi_3m
```

```{r}
write.csv(ndvi_3m,"../outputs/extracted_data/ndvi_3m.csv", row.names = FALSE)
```

## .25m - extract mean pixel values
Use 1m buffer for GCC as  function of distance from edge
extract(rasterA,points, buffer=150, fun=mean)

- Choose buffer based on pixel size and maintaining fine scale resolution but aggregating so that values are at the same spatial scale

```{r}

extract_alnus_tr1_qm = raster::extract(alnus_tr1_f08, alnus_tr1_pt, buffer=.25, fun=mean, df=TRUE )
extract_cn_tr1_qm = raster::extract(cn_tr1_f20, cn_tr1_pt, buffer=.25, fun=mean,  df=TRUE )
extract_cn_tr2_qm = raster::extract(cn_tr2_f17, cn_tr2_pt, buffer=.25, fun=mean,  df=TRUE )
```


```{r}
extract_alnus_tr1_qm$plot_id = alnus_tr1_pt$ID
names(extract_alnus_tr1_qm) = c('ID', 'mean_gcc', 'plot_id')
extract_alnus_tr1_qm
```

```{r}
extract_cn_tr1_qm$plot_id = cn_tr1_pt$ID
names(extract_cn_tr1_qm) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr1_qm
```

```{r}
extract_cn_tr2_qm$plot_id = cn_tr2_pt$ID
names(extract_cn_tr2_qm) = c('ID', 'mean_gcc', 'plot_id')
extract_cn_tr2_qm
```


```{r}
cn_bind_qm = rbind(extract_cn_tr1_qm, extract_cn_tr2_qm)
ndvi_qm = rbind(extract_alnus_tr1_qm, cn_bind_qm)
ndvi_qm
```

```{r}
write.csv(ndvi_qm,"../outputs/extracted_data/ndvi_25cm.csv", row.names = FALSE)
```

