---
title: "UAV-EdgeEffect-Analysis"
author: "Anna Talucci"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)

```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-05-20_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```


# Part 2:  Post-fire

## 7. Model: GCC burn/unburned
```{r}
mod7 = glm(mean_gcc_10m ~ burn_unburn, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod7.res = simulateResiduals(fittedModel = mod7, n = 500)
mod7.res$scaledResiduals
mod7.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod7.res)
```

```{r}
testDispersion(mod7.res)
```

### Sumamry
```{r}
summary(mod7)
```
```{r}
mod7_df = data.frame(summary(lsmeans(mod7, revpairwise ~ burn_unburn, type = "response", infer = TRUE, adjust = "tukey")))
mod7_df = mod7_df %>% mutate(model="mod7") %>% mutate(response = "GCC") %>% rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% select(model:response, explanatory:se, lcl:contrasts.SE)
```

### Data for graph

```{r}
(mod7_graph = data.frame(summary(lsmeans(mod7, pairwise ~ burn_unburn),type = "response")))
```



```{r}
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod7_graph1 = dplyr::select(mod7_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod7_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod7_graph1 = data.frame(mod7_graph1)
mod7_graph1

```

### Graph

```{r}
plot_mod7 = ggplot(data = mod7_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod7 
```

#### Box plot

```{r}
boxplot_mod7 = ggplot(field_gcc, aes(x=burn_unburn, y=mean_gcc_10m, color = burn_unburn, fill=burn_unburn) ) + # define plot axes
geom_boxplot(fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = .5) + 
stat_summary(fun.y = mean, geom= "point", shape = 18, size = 5) + 
labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod7

```



## 8. Model: NDVI burn/unburned
```{r}
mod8 = glm(mean_ndvi_10m ~ burn_unburn, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod8.res = simulateResiduals(fittedModel = mod8, n = 500)
mod8.res$scaledResiduals
mod8.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod8.res)
```

```{r}
testDispersion(mod8.res)
```

### Summary
```{r}
summary(mod8)
```

#### Summary Dataframe
```{r}
mod8_df = data.frame(summary(lsmeans(mod8, revpairwise ~ burn_unburn, type = "response", infer = TRUE, adjust = "tukey")))
mod8_df = mod8_df %>% mutate(model="mod8") %>% mutate(response = "NDVI") %>% rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% select(model:response, explanatory:se, lcl:contrasts.SE)
mod8_df
```

### Data for graph

```{r}
(mod8_graph = data.frame(summary(lsmeans(mod8, pairwise ~ burn_unburn),type = "response")))
```
```{r}
mod8_df = data.frame(summary(lsmeans(mod8, revpairwise ~ burn_unburn, type = "response", infer = TRUE, adjust = "tukey")))
mod8_df = mod8_df %>% mutate(model="mod8") %>% mutate(response = "NDVI") %>% rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% select(model:response, explanatory:se, lcl:contrasts.SE)
mod8_df
```

```{r}
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod8_graph1 = dplyr::select(mod8_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod8_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod8_graph1 = data.frame(mod8_graph1)
mod8_graph1

```

### Graph

```{r}
plot_mod8 = ggplot(data = mod8_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod8 
```

```{r}
boxplot_mod8 = ggplot(field_gcc_ndvi, aes(x=burn_unburn, y=mean_ndvi_10m, color = burn_unburn, fill = burn_unburn) ) + # define plot axes
geom_boxplot(fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center",
dotsize = .5) + # Dotplot by group
stat_summary(fun.y = mean, geom= "point", shape = 18, size = 5) + # Add means to the plot
labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod8

```

## 9. Model: GCC by burn-year 
```{r}
mod9 = glm(mean_gcc_10m ~ burn_year:burn_unburn, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod9.res = simulateResiduals(fittedModel = mod9, n = 500)
mod9.res$scaledResiduals
mod9.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod9.res)
```

```{r}
testDispersion(mod9.res)
```

### Sumamry
```{r}
summary(mod9)
```

### Data for Graph

```{r}
(mod9_graph = data.frame(summary(lsmeans(mod9, ~ burn_year:burn_unburn),type = "response")))
```



### Graph 

```{r}
plot_mod9 = ggplot(data = mod9_graph, aes(x = burn_year, y = lsmean, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme 

plot_mod9  
```

```{r}
boxplot_mod9 = ggplot(field_gcc, aes(x=burn_year, y=mean_gcc_10m, color = burn_unburn,  fill = burn_unburn)) + 
  geom_boxplot(position=position_dodge(0.8), fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = .5, position=position_dodge(0.8)) +
  stat_summary(fun.y = mean, geom= "point", shape = 18, size = 4, position = position_dodge(0.8)) + # Add means to the plot
  labs(x=("Burn year"), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod9

```

## 10. Model: NDVI as a function of burn year
```{r}
mod10 = glm(mean_ndvi_10m ~ burn_year:burn_unburn, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod10.res = simulateResiduals(fittedModel = mod10, n = 500)
mod10.res$scaledResiduals
mod10.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod10.res)
```

```{r}
testDispersion(mod10.res)
```

### Sumamry
```{r}
summary(mod10)
```

### Data for Graph

```{r}
(mod10_graph = data.frame(summary(lsmeans(mod10, ~ burn_year:burn_unburn),type = "response")))
```




### Graph 

```{r}
plot_mod10 = ggplot(data = mod10_graph, aes(x = burn_year, y = lsmean, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = asymp.LCL, ymax = asymp.UCL), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=("Burn year"), y= "Mean NDVI") +
   scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme 

plot_mod10  
```

```{r}
boxplot_mod10 = ggplot(field_gcc_ndvi, aes(x=burn_year, y=mean_ndvi_10m, color = burn_unburn,  fill = burn_unburn)) + 
  geom_boxplot(position=position_dodge(0.8), fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = .5, position=position_dodge(0.8)) +
  stat_summary(fun.y = mean, geom= "point", shape = 18, size = 4, position = position_dodge(0.8)) + # Add means to the plot
  labs(x=("Burn year"), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod10

```


## 11. Model: GCC distance from unburned edge 
```{r}
mod11 = glm(mean_gcc_10m ~ plot_dis, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod11.res = simulateResiduals(fittedModel = mod11, n = 500)
mod11.res$scaledResiduals
mod11.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod11.res)
```

```{r}
testDispersion(mod11.res)
```

### Summary
```{r}
summary(mod11)
```
```{r}
coef(mod11)
coefficients(mod11)
```
```{r}
df <- tibble::rownames_to_column(df, "VALUE")
```

#### Summary Dataframe

```{r}
data.frame(summary(mod11)$coefficients[,], confint(mod11))
```
```{r}
mod11_df = data.frame(summary(mod11)$coefficients[,], confint(mod11))
mod11_df2 = tibble::rownames_to_column(mod11_df, "coefficent")
mod11_df2
```


```{r}
mod11_df = data.frame(summary(mod11)$coefficients[,], confint(mod11))
mod11_df2 = tibble::rownames_to_column(mod11_df, "coefficent")
mod11_df3 = mod11_df2 %>% 
  mutate(model = "mod11") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5..) %>%
  select(model:response, coefficent:ucl)
mod11_df3
```


### Predicted data for for graph
```{r}
preddat_mod11 = data.frame(plot_dis = field_gcc$plot_dis)

head(preddat_mod11)

pred_mod11 = predict(mod11, newdata = preddat_mod11, se.fit = TRUE)

UL_mod11 = with(pred_mod11, fit + 2*se.fit)
LL_mod11 = with(pred_mod11, fit - 2*se.fit)

field_gcc11 = mutate(field_gcc, pred_mod11 = (pred_mod11$fit), 
               ucl_mod11 = (UL_mod11), 
               lcl_mod11 = (LL_mod11))
```


### Graph  

```{r}
plot_mod11 = ggplot(data = field_gcc11, aes(x = plot_dis, y = mean_gcc_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod11), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod11, ymax = ucl_mod11, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod11), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod11), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean GCC") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_y_continuous(breaks = c(0.34, 0.36, 0.38, 0.40, 0.42)) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod11
```


## 12.  Model: NDVI distance from edge
```{r}
mod12 = glm(mean_ndvi_10m ~ plot_dis, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod12.res = simulateResiduals(fittedModel = mod12, n = 500)
mod12.res$scaledResiduals
mod12.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod12.res)
```

```{r}
testDispersion(mod12.res)
```

### Summary
```{r}
summary(mod12)
```

#### Summary Dataframe

```{r}
mod12_df = data.frame(summary(mod12)$coefficients[,], confint(mod12))
mod12_df2 = tibble::rownames_to_column(mod12_df, "coefficent")
mod12_df3 = mod12_df2 %>% 
  mutate(model = "mod12") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5..) %>%
  select(model:response, coefficent:ucl)
mod12_df3
```



```{r}
preddat_mod12 = data.frame(plot_dis = field_gcc_ndvi$plot_dis)

head(preddat_mod12)

pred_mod12 = predict(mod12, newdata = preddat_mod12, se.fit = TRUE)

UL_mod12 = with(pred_mod12, fit + 2*se.fit)
LL_mod12 = with(pred_mod12, fit - 2*se.fit)

field_gcc_ndvi12 = mutate(field_gcc_ndvi, pred_mod12 = (pred_mod12$fit), 
               ucl_mod12 = (UL_mod12), 
               lcl_mod12 = (LL_mod12))
```

### Graph  

```{r}
plot_mod12 = ggplot(data = field_gcc_ndvi12, aes(x = plot_dis, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod12), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod12, ymax = ucl_mod12, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod12), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod12), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean NDVI") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme + guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod12
```

# Summary output Combine
## Burned-Unburned

```{r}
burn_unburn_sum = rbind(mod7_df, mod8_df)
write.csv(burn_unburn_sum, '../outputs/model_summary/2020-05-27_burn-unburn-summary.csv', row.names = F)

```

```{r}
edge_sum = rbind(mod11_df3, mod12_df3)
write.csv(edge_sum, '../outputs/model_summary/2020-05-27_distance-edge-summary.csv', row.names = F)

```


# Manuscript figures

## Part 2: Post-fire

### Burned vs. Unburned + Burn Year
```{r fig.height=6, fig.width=6}

grid_plot_burn = cowplot::plot_grid(plot_mod7, plot_mod8, plot_mod9, plot_mod10, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_plot_burn

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_burn-unburn-year.jpeg", plot = grid_plot_burn, width = 6, height = 6, units = c("in"), dpi=600 )
```

## Burn and unburned only
```{r fig.height=3, fig.width=6}

grid_plot_burn_un = cowplot::plot_grid(plot_mod7, plot_mod8, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_plot_burn_un

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-27_burn-unburn-only.jpeg", plot = grid_plot_burn_un, width = 6, height = 3, units = c("in"), dpi=600 )
```


### Boxplots burn/unburn
```{r fig.height=6, fig.width=6}

grid_boxplot_burn = cowplot::plot_grid(boxplot_mod7, boxplot_mod8, boxplot_mod9, boxplot_mod10, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_boxplot_burn

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_BOX-burn-unburn-year.jpeg", plot = grid_boxplot_burn, width = 6, height = 6, units = c("in"), dpi=600 )
```

### Boxplots burn/unburn
```{r fig.height=3, fig.width=6}

grid_boxplot_burn_un = cowplot::plot_grid(boxplot_mod7, boxplot_mod8, labels = c("A", "B", "C", "D"), align = "hv", ncol= 2) 
grid_boxplot_burn_un

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-27_BOX-burn-unburn-only.jpeg", plot = grid_boxplot_burn_un, width = 6, height = 3, units = c("in"), dpi=600 )
```

### Distance from unburned edge

```{r fig.height=3, fig.width=6}

grid_plot_edge = cowplot::plot_grid(plot_mod11, plot_mod12, labels = c("A", "B"), align = "hv", ncol= 2) 
grid_plot_edge

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_distance_edge_pts.jpeg", plot = grid_plot_edge, width = 6, height = 3, units = c("in"), dpi=600 )
```

