---
title: "UAV-Biomass-Tree-Analysis"
author: "Anna Talucci"
date: "5/13/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
library(rcompanion)
```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-05-20_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 10, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 10, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 9, color = "black"),
        axis.text.y = element_text(size = 9, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Analysis: 
```{r}
head(field_gcc)
```

# Part 4: Biomass as it relates to GCC and NDVI
## GCC
### 1. Model: Woody Biomass function of GCC
```{r}
mod1 = glm(mean_gcc_25cm ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod1.res = simulateResiduals(fittedModel = mod1, n = 500)
mod1.res$scaledResiduals
mod1.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod1.res)
```

```{r}
testDispersion(mod1.res)
```

#### Summary
```{r}
summary(mod1)
```
##### Summary Dataframe

```{r}
mod1_df = data.frame(summary(mod1)$coefficients[,], confint(mod1), deviance(mod1), summary(mod1)$null.deviance, extractAIC(mod1))
mod1_df
mod1_df2 = tibble::rownames_to_column(mod1_df, "coefficent")
mod1_df3 = mod1_df2 %>% 
  mutate(model = "mod1") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod1., null_deviance= summary.mod1..null.deviance, AIC = extractAIC.mod1.) %>% select(model:response, coefficent:AIC)
mod1_df3
```

#### Data for graph

```{r}
preddat_mod1 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod1)

pred_mod1 = predict(mod1, newdata = preddat_mod1, se.fit = TRUE)

UL_mod1 = with(pred_mod1, fit + 2*se.fit)
LL_mod1 = with(pred_mod1, fit - 2*se.fit)

field_gcc1 = mutate(field_gcc, pred_mod1 = pred_mod1$fit, 
               ucl_mod1 = UL_mod1, 
               lcl_mod1 = LL_mod1)
```

#### Graph 

```{r}
plot_mod1 = ggplot(data = field_gcc1, aes(x = tree_biomass_C_g_m, y = mean_gcc_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod1), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod1), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1), linetype='longdash', size = 1) +
    
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (25cm)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 
plot_mod1
```


### 2. Model: GCC
```{r}
mod2 = glm(mean_gcc_50cm ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

#### Summary
```{r}
summary(mod2)
```
##### Summary Dataframe

```{r}
mod2_df = data.frame(summary(mod2)$coefficients[,], confint(mod2), deviance(mod2), summary(mod2)$null.deviance, extractAIC(mod2))
mod2_df
mod2_df2 = tibble::rownames_to_column(mod2_df, "coefficent")
mod2_df3 = mod2_df2 %>% 
  mutate(model = "mod2") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod2., null_deviance= summary.mod2..null.deviance, AIC = extractAIC.mod2.) %>% select(model:response, coefficent:AIC)
mod2_df3
```

#### Data for graph
```{r}
preddat_mod2 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod2)

pred_mod2 = predict(mod2, newdata = preddat_mod2, se.fit = TRUE)

UL_mod2 = with(pred_mod2, fit + 2*se.fit)
LL_mod2 = with(pred_mod2, fit - 2*se.fit)

field_gcc2 = mutate(field_gcc, pred_mod2 = pred_mod2$fit, 
               ucl_mod2 = UL_mod2, 
               lcl_mod2 = LL_mod2)
```

#### Graph 

```{r}
plot_mod2 = ggplot(data = field_gcc2, aes(x = tree_biomass_C_g_m, y = mean_gcc_50cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod2), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod2, ymax = ucl_mod2, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod2), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod2), linetype='longdash', size = 1) +
    
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (50cm)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod2
```

### 3. Model:  GCC
```{r}
mod3 = glm(mean_gcc_1m ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

#### Summary
```{r}
summary(mod3)
```
##### Summary Dataframe

```{r}
mod3_df = data.frame(summary(mod3)$coefficients[,], confint(mod3), deviance(mod3), summary(mod3)$null.deviance, extractAIC(mod3))
mod3_df
mod3_df2 = tibble::rownames_to_column(mod3_df, "coefficent")
mod3_df3 = mod3_df2 %>% 
  mutate(model = "mod3") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod3., null_deviance= summary.mod3..null.deviance, AIC = extractAIC.mod3.) %>% select(model:response, coefficent:AIC)
mod3_df3
```

#### Data for graph
```{r}
preddat_mod3 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod3)

pred_mod3 = predict(mod3, newdata = preddat_mod3, se.fit = TRUE)

UL_mod3 = with(pred_mod3, fit + 2*se.fit)
LL_mod3 = with(pred_mod3, fit - 2*se.fit)

field_gcc3 = mutate(field_gcc, pred_mod3 = pred_mod3$fit, 
               ucl_mod3 = UL_mod3, 
               lcl_mod3 = LL_mod3)
```

#### Graph 

```{r}
plot_mod3 = ggplot(data = field_gcc3, aes(x = tree_biomass_C_g_m, y = mean_gcc_1m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod3), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod3, ymax = ucl_mod3, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod3), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod3), linetype='longdash', size = 1) +
    
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (1m)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 
plot_mod3
```

### 4. Model:  GCC
```{r}
mod4 = glm(mean_gcc_3m ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

#### Summary
```{r}
summary(mod4)
```
##### Summary Dataframe

```{r}
mod4_df = data.frame(summary(mod4)$coefficients[,], confint(mod4), deviance(mod4), summary(mod4)$null.deviance, extractAIC(mod4))
mod4_df
mod4_df2 = tibble::rownames_to_column(mod4_df, "coefficent")
mod4_df3 = mod4_df2 %>% 
  mutate(model = "mod4") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod4., null_deviance= summary.mod4..null.deviance, AIC = extractAIC.mod4.) %>% select(model:response, coefficent:AIC)
mod4_df3
```

#### Data for graph
```{r}
preddat_mod4 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod4)

pred_mod4 = predict(mod4, newdata = preddat_mod4, se.fit = TRUE)

UL_mod4 = with(pred_mod4, fit + 2*se.fit)
LL_mod4 = with(pred_mod4, fit - 2*se.fit)

field_gcc4 = mutate(field_gcc, pred_mod4 = pred_mod4$fit, 
               ucl_mod4 = UL_mod4, 
               lcl_mod4 = LL_mod4)
```

#### Graph 

```{r}
plot_mod4 = ggplot(data = field_gcc4, aes(x = tree_biomass_C_g_m, y = mean_gcc_3m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod4), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod4, ymax = ucl_mod4, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod4), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod4), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (3m)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod4
```

### 5. Model:  GCC
```{r}
mod5 = glm(mean_gcc_5m ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

#### Summary
```{r}
summary(mod5)
```
##### Summary Dataframe

```{r}
mod5_df = data.frame(summary(mod5)$coefficients[,], confint(mod5), deviance(mod5), summary(mod5)$null.deviance, extractAIC(mod5))
mod5_df
mod5_df2 = tibble::rownames_to_column(mod5_df, "coefficent")
mod5_df3 = mod5_df2 %>% 
  mutate(model = "mod5") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod5., null_deviance= summary.mod5..null.deviance, AIC = extractAIC.mod5.) %>% select(model:response, coefficent:AIC)
mod5_df3
```

#### Data for graph
```{r}
preddat_mod5 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod5)

pred_mod5 = predict(mod5, newdata = preddat_mod5, se.fit = TRUE)

UL_mod5 = with(pred_mod5, fit + 2*se.fit)
LL_mod5 = with(pred_mod5, fit - 2*se.fit)

field_gcc5 = mutate(field_gcc, pred_mod5 = pred_mod5$fit, 
               ucl_mod5 = UL_mod5, 
               lcl_mod5 = LL_mod5)
```

#### Graph 

```{r}
plot_mod5 = ggplot(data = field_gcc5, aes(x =tree_biomass_C_g_m, y = mean_gcc_5m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod5), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod5, ymax = ucl_mod5, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod5), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod5), linetype='longdash', size = 1) +
    
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (5m)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod5
```

### 6. Model:  GCC
```{r}
mod6 = glm(mean_gcc_10m ~ tree_biomass_C_g_m, data = field_gcc, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod6.res)
```

#### Summary
```{r}
summary(mod6)
```
##### Summary Dataframe

```{r}
mod6_df = data.frame(summary(mod6)$coefficients[,], confint(mod6), deviance(mod6), summary(mod6)$null.deviance, extractAIC(mod6))
mod6_df
mod6_df2 = tibble::rownames_to_column(mod6_df, "coefficent")
mod6_df3 = mod6_df2 %>% 
  mutate(model = "mod6") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod6., null_deviance= summary.mod6..null.deviance, AIC = extractAIC.mod6.) %>% select(model:response, coefficent:AIC)
mod6_df3
```

#### Data for graph

```{r}
preddat_mod6 = data.frame(tree_biomass_C_g_m = field_gcc$tree_biomass_C_g_m)

head(preddat_mod6)

pred_mod6 = predict(mod6, newdata = preddat_mod6, se.fit = TRUE)

UL_mod6 = with(pred_mod6, fit + 2*se.fit)
LL_mod6 = with(pred_mod6, fit - 2*se.fit)

field_gcc6 = mutate(field_gcc, pred_mod6 = pred_mod6$fit, 
               ucl_mod6 = UL_mod6, 
               lcl_mod6 = LL_mod6)
```

#### Graph 

```{r}
plot_mod6 = ggplot(data = field_gcc6, aes(x = tree_biomass_C_g_m, y = mean_gcc_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod6), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod6, ymax = ucl_mod6, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod6), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod6), linetype='longdash', size = 1) +
    
    scale_y_continuous(breaks = seq(0.3, 0.45, by = .05), name = "GCC (10m)")+
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod6
```

```{r}
compareGLM(mod1, mod2, mod3, mod4, mod5, mod6)
```
## NDVI

### 7. Model: NDVI
```{r}
mod7 = glm(mean_ndvi_25cm ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod7.res = simulateResiduals(fittedModel = mod7, n = 500)
mod7.res$scaledResiduals
mod7.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod7.res)
```

```{r}
testDispersion(mod7.res)
```

#### Summary
```{r}
summary(mod7)
```
##### Summary Dataframe

```{r}
mod7_df = data.frame(summary(mod7)$coefficients[,], confint(mod7), deviance(mod7), summary(mod7)$null.deviance, extractAIC(mod7))
mod7_df
mod7_df2 = tibble::rownames_to_column(mod7_df, "coefficent")
mod7_df3 = mod7_df2 %>% 
  mutate(model = "mod7") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod7., null_deviance= summary.mod7..null.deviance, AIC = extractAIC.mod7.) %>% select(model:response, coefficent:AIC)
mod7_df3
```

#### Data for graph
```{r}
preddat_mod7 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod7)

pred_mod7 = predict(mod7, newdata = preddat_mod7, se.fit = TRUE)

UL_mod7 = with(pred_mod7, fit + 2*se.fit)
LL_mod7 = with(pred_mod7, fit - 2*se.fit)

field_gcc_ndvi7 = mutate(field_gcc_ndvi, pred_mod7 = pred_mod7$fit, 
               ucl_mod7 = UL_mod7, 
               lcl_mod7 = LL_mod7)
```

#### Graph 

```{r}
plot_mod7 = ggplot(data = field_gcc_ndvi7, aes(x = tree_biomass_C_g_m, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod7), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod7, ymax = ucl_mod7, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod7), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod7), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI (25cm)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod7
```


### 8. Model: NDVI
```{r}
mod8 = glm(mean_ndvi_50cm ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod8.res = simulateResiduals(fittedModel = mod8, n = 500)
mod8.res$scaledResiduals
mod8.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod8.res)
```

```{r}
testDispersion(mod8.res)
```

#### Summary
```{r}
summary(mod8)
```
##### Summary Dataframe

```{r}
mod8_df = data.frame(summary(mod8)$coefficients[,], confint(mod8), deviance(mod8), summary(mod8)$null.deviance, extractAIC(mod8))
mod8_df
mod8_df2 = tibble::rownames_to_column(mod8_df, "coefficent")
mod8_df3 = mod8_df2 %>% 
  mutate(model = "mod8") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod8., null_deviance= summary.mod8..null.deviance, AIC = extractAIC.mod8.) %>% select(model:response, coefficent:AIC)
mod8_df3
```

#### Data for graph
```{r}
preddat_mod8 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod8)

pred_mod8 = predict(mod8, newdata = preddat_mod8, se.fit = TRUE)

UL_mod8 = with(pred_mod8, fit + 2*se.fit)
LL_mod8 = with(pred_mod8, fit - 2*se.fit)

field_gcc_ndvi8 = mutate(field_gcc_ndvi, pred_mod8 = pred_mod8$fit, 
               ucl_mod8 = UL_mod8, 
               lcl_mod8 = LL_mod8)
```

#### Graph 

```{r}
plot_mod8 = ggplot(data = field_gcc_ndvi8, aes(x = tree_biomass_C_g_m, y = mean_ndvi_50cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod8), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod8, ymax = ucl_mod8, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod8), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod8), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI 50cm)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod8
```

### 9. Model: NDVI
```{r}
mod9 = glm(mean_ndvi_1m ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod9.res = simulateResiduals(fittedModel = mod9, n = 500)
mod9.res$scaledResiduals
mod9.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod9.res)
```

```{r}
testDispersion(mod9.res)
```

#### Summary
```{r}
summary(mod9)
```
##### Summary Dataframe

```{r}
mod9_df = data.frame(summary(mod9)$coefficients[,], confint(mod9), deviance(mod9), summary(mod9)$null.deviance, extractAIC(mod9))
mod9_df
mod9_df2 = tibble::rownames_to_column(mod9_df, "coefficent")
mod9_df3 = mod9_df2 %>% 
  mutate(model = "mod9") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod9., null_deviance= summary.mod9..null.deviance, AIC = extractAIC.mod9.) %>% select(model:response, coefficent:AIC)
mod9_df3
```

#### Data for graph
```{r}
preddat_mod9 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod9)

pred_mod9 = predict(mod9, newdata = preddat_mod9, se.fit = TRUE)

UL_mod9 = with(pred_mod9, fit + 2*se.fit)
LL_mod9 = with(pred_mod9, fit - 2*se.fit)

field_gcc_ndvi9 = mutate(field_gcc_ndvi, pred_mod9 = pred_mod9$fit, 
               ucl_mod9 = UL_mod9, 
               lcl_mod9 = LL_mod9)
```

#### Graph 

```{r}
plot_mod9 = ggplot(data = field_gcc_ndvi9, aes(x = tree_biomass_C_g_m, y = mean_ndvi_1m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod9), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod9, ymax = ucl_mod9, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod9), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod9), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI (1m)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod9
```

### 10. Model: NDVI
```{r}
mod10 = glm(mean_ndvi_3m ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod10.res = simulateResiduals(fittedModel = mod10, n = 500)
mod10.res$scaledResiduals
mod10.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod10.res)
```

```{r}
testDispersion(mod10.res)
```

#### Summary
```{r}
summary(mod10)
```
##### Summary Dataframe

```{r}
mod10_df = data.frame(summary(mod10)$coefficients[,], confint(mod10), deviance(mod10), summary(mod10)$null.deviance, extractAIC(mod10))
mod10_df
mod10_df2 = tibble::rownames_to_column(mod10_df, "coefficent")
mod10_df3 = mod10_df2 %>% 
  mutate(model = "mod10") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod10., null_deviance= summary.mod10..null.deviance, AIC = extractAIC.mod10.) %>% select(model:response, coefficent:AIC)
mod10_df3
```

#### Data for graph
```{r}
preddat_mod10 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod10)

pred_mod10 = predict(mod10, newdata = preddat_mod10, se.fit = TRUE)

UL_mod10 = with(pred_mod10, fit + 2*se.fit)
LL_mod10 = with(pred_mod10, fit - 2*se.fit)

field_gcc_ndvi10 = mutate(field_gcc_ndvi, pred_mod10 = pred_mod10$fit, 
               ucl_mod10 = UL_mod10, 
               lcl_mod10 = LL_mod10)
```

#### Graph 

```{r}
plot_mod10 = ggplot(data = field_gcc_ndvi10, aes(x = tree_biomass_C_g_m, y = mean_ndvi_3m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod10), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod10, ymax = ucl_mod10, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod10), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod10), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI (3m)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod10
```

### 11. Model: NDVI
```{r}
mod11 = glm(mean_ndvi_5m ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod11.res = simulateResiduals(fittedModel = mod11, n = 500)
mod11.res$scaledResiduals
mod11.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod11.res)
```

```{r}
testDispersion(mod11.res)
```

#### Summary
```{r}
summary(mod11)
```
##### Summary Dataframe

```{r}
mod11_df = data.frame(summary(mod11)$coefficients[,], confint(mod11), deviance(mod11), summary(mod11)$null.deviance, extractAIC(mod11))
mod11_df
mod11_df2 = tibble::rownames_to_column(mod11_df, "coefficent")
mod11_df3 = mod11_df2 %>% 
  mutate(model = "mod11") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod11., null_deviance= summary.mod11..null.deviance, AIC = extractAIC.mod11.) %>% select(model:response, coefficent:AIC)
mod11_df3
```

#### Data for graph
```{r}
preddat_mod11 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod11)

pred_mod11 = predict(mod11, newdata = preddat_mod11, se.fit = TRUE)

UL_mod11 = with(pred_mod11, fit + 2*se.fit)
LL_mod11 = with(pred_mod11, fit - 2*se.fit)

field_gcc_ndvi11 = mutate(field_gcc_ndvi, pred_mod11 = pred_mod11$fit, 
               ucl_mod11 = UL_mod11, 
               lcl_mod11 = LL_mod11)
```

#### Graph 

```{r}
plot_mod11 = ggplot(data = field_gcc_ndvi11, aes(x = tree_biomass_C_g_m, y = mean_ndvi_5m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod11), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod11, ymax = ucl_mod11, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod11), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod11), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI (5m)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod11
```

### 12. Model: NDVI
```{r}
mod12 = glm(mean_ndvi_10m ~ tree_biomass_C_g_m, data = field_gcc_ndvi, family = gaussian)
```

#### Residuals with DHARMa
```{r, include=FALSE}
mod12.res = simulateResiduals(fittedModel = mod12, n = 500)
mod12.res$scaledResiduals
mod12.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod12.res)
```

```{r}
testDispersion(mod12.res)
```

#### Summary

```{r}
summary(mod12)
```

##### Summary Dataframe

```{r}
mod12_df = data.frame(summary(mod12)$coefficients[,], confint(mod12), deviance(mod12), summary(mod12)$null.deviance, extractAIC(mod12))
mod12_df
mod12_df2 = tibble::rownames_to_column(mod12_df, "coefficent")
mod12_df3 = mod12_df2 %>% 
  mutate(model = "mod12") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod12., null_deviance= summary.mod12..null.deviance, AIC = extractAIC.mod12.) %>% select(model:response, coefficent:AIC)
mod12_df3
```

#### Data for graph
```{r}
preddat_mod12 = data.frame(tree_biomass_C_g_m = field_gcc_ndvi$tree_biomass_C_g_m)

head(preddat_mod12)

pred_mod12 = predict(mod12, newdata = preddat_mod12, se.fit = TRUE)

UL_mod12 = with(pred_mod12, fit + 2*se.fit)
LL_mod12 = with(pred_mod12, fit - 2*se.fit)

field_gcc_ndvi12 = mutate(field_gcc_ndvi, pred_mod12 = pred_mod12$fit, 
               ucl_mod12 = UL_mod12, 
               lcl_mod12 = LL_mod12)
```

#### Graph 

```{r}
plot_mod12 = ggplot(data = field_gcc_ndvi12, aes(x = tree_biomass_C_g_m, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod12), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod12, ymax = ucl_mod12, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod12), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod12), linetype='longdash', size = 1) +
    scale_y_continuous(breaks = seq(0.4, 0.8, by = .1), name = "NDVI (10m)") +
    labs(x=expression(Tree~biomass~(g~C~m^-2)))   +
    reg_theme 

plot_mod12
```



```{r}
compareGLM(mod7, mod8, mod9, mod10, mod11, mod12)
```

# Combine Summary output 

```{r}
model_sum1 = rbind(mod1_df3, mod2_df3)
model_sum2 = rbind(mod3_df3, mod4_df3)
model_sum3 = rbind(mod5_df3, mod6_df3)
model_sum4 = rbind(mod7_df3, mod8_df3)
model_sum5 = rbind(mod9_df3, mod10_df3)
model_sum6 = rbind(mod11_df3, mod12_df3)
model_sum7 = rbind(model_sum1, model_sum2)
model_sum8 = rbind(model_sum3, model_sum4)
model_sum9 = rbind(model_sum5, model_sum6)
model_sum10 = rbind(model_sum7, model_sum8)
model_sum11 = rbind(model_sum10, model_sum9)
model_sum11
```

```{r}
write.csv(model_sum11, '../outputs/model_summary/2020-05-27_tree-biomass-gcc-ndvi.csv', row.names = F)

```


# Manuscript Figures 

```{r fig.height=7, fig.width=6}

grid_biomass_gcc = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6,   labels = "AUTO", label_size = 12, align = "hv", ncol= 2) 
grid_biomass_gcc

```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_Biomass-tree-gcc.jpeg", plot = grid_biomass_gcc, width = 6, height = 7, units = c("in"), dpi=600 )
```

```{r fig.height=7, fig.width=6}

grid_biomass_ndvi = cowplot::plot_grid(plot_mod7, plot_mod8, plot_mod9, plot_mod10, plot_mod11, plot_mod12, labels = "AUTO", label_size = 12, align = "hv", ncol= 2) 
grid_biomass_ndvi

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_Biomass-tree-ndvi.jpeg", plot = grid_biomass_ndvi, width = 6, height = 7, units = c("in"), dpi=600 )
```

### Axis labels 3 columns
```{r fig.height=7, fig.width=6}

fig1 = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6, plot_mod7, plot_mod8, plot_mod9, plot_mod10, plot_mod11, plot_mod12, labels = "AUTO", label_size = 12, align = "hv", ncol= 3) + 
  theme(plot.margin = margin(0, 0, 0, 0))

fig1
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-21_Biomass-Tree-ndvi-gcc.jpeg", plot = fig1, width = 6, height = 7, units = c("in"), dpi=600 )
```
