---
title: "UAV-Scale-Analysis"
author: "Anna Talucci"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-05-20_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Analysis: 

# Part 1: GCC relates to NDVI

Assess spatial scale...


## 1. Model: NDVIas  function of GCC
```{r}
mod1 = glm(mean_ndvi_25cm ~ mean_gcc_25cm, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod1.res = simulateResiduals(fittedModel = mod1, n = 500)
mod1.res$scaledResiduals
mod1.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod1.res)
```

```{r}
testDispersion(mod1.res)
```

### Sumamry
```{r}
summary(mod1)
```

```{r}
with(summary(mod1), 1 - (deviance/null.deviance))
```

```{r}
data.frame(summary(lsmeans(mod1, ~ mean_gcc_25cm), type = "response"))
```

### Data for graph
```{r}
preddat_mod1 = data.frame(mean_gcc_25cm = field_gcc_ndvi$mean_gcc_25cm)

head(preddat_mod1)

pred_mod1 = predict(mod1, newdata = preddat_mod1, se.fit = TRUE)

UL_mod1 = with(pred_mod1, fit + 2*se.fit)
LL_mod1 = with(pred_mod1, fit - 2*se.fit)

field_gcc_ndvi1 = mutate(field_gcc_ndvi, pred_mod1 = pred_mod1$fit, 
               ucl_mod1 = UL_mod1, 
               lcl_mod1 = LL_mod1)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod1 = ggplot(data = field_gcc_ndvi1, aes(x = mean_gcc_25cm, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod1), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod1), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (25cm)") +
    xlab("Mean GCC (25cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(0.32, 0.37, 0.42, 0.47)) 

plot_mod1
```


## 2. Model: NDVIas  function of GCC
```{r}
mod2 = glm(mean_ndvi_50cm ~ mean_gcc_50cm, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

### Sumamry
```{r}
summary(mod2)
```

```{r}
with(summary(mod2), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod2, ~ mean_gcc_50cm), type = "response"))
```

### Data for graph
```{r}
preddat_mod2 = data.frame(mean_gcc_50cm = field_gcc_ndvi$mean_gcc_50cm)

head(preddat_mod2)

pred_mod2 = predict(mod2, newdata = preddat_mod2, se.fit = TRUE)

UL_mod2 = with(pred_mod2, fit + 2*se.fit)
LL_mod2 = with(pred_mod2, fit - 2*se.fit)

field_gcc_ndvi2 = mutate(field_gcc_ndvi, pred_mod2 = pred_mod2$fit, 
               ucl_mod2 = UL_mod2, 
               lcl_mod2 = LL_mod2)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod2 = ggplot(data = field_gcc_ndvi2, aes(x = mean_gcc_50cm, y = mean_ndvi_50cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod2), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod2, ymax = ucl_mod2, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod2), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod2), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (50cm)") +
    xlab("Mean GCC (50cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod2
```

## 3. Model: NDVIas  function of GCC
```{r}
mod3 = glm(mean_ndvi_1m ~ mean_gcc_1m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

### Sumamry
```{r}
summary(mod3)
```

```{r}
with(summary(mod3), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod3, ~ mean_gcc_1m), type = "response"))
```

### Data for graph
```{r}
preddat_mod3 = data.frame(mean_gcc_1m = field_gcc_ndvi$mean_gcc_1m)

head(preddat_mod3)

pred_mod3 = predict(mod3, newdata = preddat_mod3, se.fit = TRUE)

UL_mod3 = with(pred_mod3, fit + 2*se.fit)
LL_mod3 = with(pred_mod3, fit - 2*se.fit)

field_gcc_ndvi3 = mutate(field_gcc_ndvi, pred_mod3 = pred_mod3$fit, 
               ucl_mod3 = UL_mod3, 
               lcl_mod3 = LL_mod3)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod3 = ggplot(data = field_gcc_ndvi3, aes(x = mean_gcc_1m, y = mean_ndvi_1m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod3), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod3, ymax = ucl_mod3, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod3), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod3), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (1m)") +
    xlab("Mean GCC  (1m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod3
```

## 4. Model: NDVIas  function of GCC
```{r}
mod4 = glm(mean_ndvi_3m ~ mean_gcc_3m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

### Sumamry
```{r}
summary(mod4)
```

```{r}
with(summary(mod4), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod4, ~ mean_gcc_3m), type = "response"))
```

### Data for graph
```{r}
preddat_mod4 = data.frame(mean_gcc_3m = field_gcc_ndvi$mean_gcc_3m)

head(preddat_mod4)

pred_mod4 = predict(mod4, newdata = preddat_mod4, se.fit = TRUE)

UL_mod4 = with(pred_mod4, fit + 2*se.fit)
LL_mod4 = with(pred_mod4, fit - 2*se.fit)

field_gcc_ndvi4 = mutate(field_gcc_ndvi, pred_mod4 = pred_mod4$fit, 
               ucl_mod4 = UL_mod4, 
               lcl_mod4 = LL_mod4)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod4 = ggplot(data = field_gcc_ndvi4, aes(x = mean_gcc_3m, y = mean_ndvi_3m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod4), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod4, ymax = ucl_mod4, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod4), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod4), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (3m)") +
    xlab("Mean GCC (3m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.9, by = .05), labels = c("0.6", "", "0.7", "", "0.8", "", ""))

plot_mod4
```

## 5. Model: NDVIas  function of GCC
```{r}
mod5 = glm(mean_ndvi_5m ~ mean_gcc_5m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

### Sumamry
```{r}
summary(mod5)
```

```{r}
with(summary(mod5), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod5, ~ mean_gcc_5m), type = "response"))
```

### Data for graph
```{r}
preddat_mod5 = data.frame(mean_gcc_5m = field_gcc_ndvi$mean_gcc_5m)

head(preddat_mod5)

pred_mod5 = predict(mod5, newdata = preddat_mod5, se.fit = TRUE)

UL_mod5 = with(pred_mod5, fit + 2*se.fit)
LL_mod5 = with(pred_mod5, fit - 2*se.fit)

field_gcc_ndvi5 = mutate(field_gcc_ndvi, pred_mod5 = pred_mod5$fit, 
               ucl_mod5 = UL_mod5, 
               lcl_mod5 = LL_mod5)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod5 = ggplot(data = field_gcc_ndvi5, aes(x = mean_gcc_5m, y = mean_ndvi_5m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod5), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod5, ymax = ucl_mod5, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod5), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod5), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (5m)") +
    xlab("Mean GCC (5m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

plot_mod5
```

## 6. Model: NDVIas  function of GCC
```{r}
mod6 = glm(mean_ndvi_10m ~ mean_gcc_10m, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod6.res)
```

### Sumamry
```{r}
summary(mod6)
```

```{r}
with(summary(mod6), 1 - deviance/null.deviance)
```

```{r}
data.frame(summary(lsmeans(mod6, ~ mean_gcc_10m), type = "response"))
```

### Data for graph
```{r}
preddat_mod6 = data.frame(mean_gcc_10m = field_gcc_ndvi$mean_gcc_10m)

head(preddat_mod6)

pred_mod6 = predict(mod6, newdata = preddat_mod6, se.fit = TRUE)

UL_mod6 = with(pred_mod6, fit + 2*se.fit)
LL_mod6 = with(pred_mod6, fit - 2*se.fit)

field_gcc_ndvi6 = mutate(field_gcc_ndvi, pred_mod6 = pred_mod6$fit, 
               ucl_mod6 = UL_mod6, 
               lcl_mod6 = LL_mod6)
```

### Graph 

```{r fig.height=3, fig.width=3}
plot_mod6 = ggplot(data = field_gcc_ndvi6, aes(x = mean_gcc_10m, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod6), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod6, ymax = ucl_mod6, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod6), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod6), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI  (10m)") +
    xlab("Mean GCC (10m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

plot_mod6
```

# Manuscript Figures 

## Part 1: Vegetation Indices

```{r fig.height=7, fig.width=6}

grid_plot_vi = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_vi

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_VI-gcc-ndvi.jpeg", plot = grid_plot_vi, width = 6, height = 7, units = c("in"), dpi=600 )
```
