---
title: "UAV-EdgeEffect-Analysis"
author: "Anna Talucci"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
library(multcomp)
library(car)
library(grid)
library(gtable)
library(gridExtra)
```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-05-20_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Summary stats
```{r}
field_gcc %>% group_by(burn_unburn) %>% summarise(mean=mean(mean_gcc_10m), sd=sd(mean_gcc_10m), min=min(mean_gcc_10m), max=max(mean_gcc_10m))
```

```{r}
field_gcc_ndvi %>% group_by(burn_unburn) %>% summarise(mean=mean(mean_ndvi_10m), sd=sd(mean_ndvi_10m), min=min(mean_ndvi_10m), max=max(mean_ndvi_10m))
```

# Part 2:  Post-fire

## 1. Model: GCC burn/unburned
```{r}
fit1 = lm(mean_gcc_10m ~ burn_unburn, data = field_gcc)
```

#### Residuals
```{r}
# Get the fitted value for each observation
field_gcc$fit1 = fitted(fit1)
# Get the residuals of the model
field_gcc$res1 = residuals(fit1)
```

```{r}
qplot(x = fit1, y = res1, data = field_gcc,
main = "Residuals vs Fitted Values")
```

```{r}
qplot(x = burn_unburn, y = res1, data = field_gcc,
xlab = "Burn v unburn group",
ylab = "Residuals",
main = "Residuals vs burn/unburn")
```
```{r}
qplot(x = factor(1), y = res1, data = field_gcc, geom = "boxplot")
```

```{r}
qqnorm(field_gcc$res1, main = "Normal QQ Plot of Residuals")
qqline(field_gcc$res1) # add reference line to the qq plot
```

```{r}
plot(fit1, which = 1) # residual vs fitted values
```

```{r}
plot(fit1, which = 2) # qqnorm plot of residuals
```

#### Summary
```{r}
summary(fit1)
```
```{r}
# All the coefficients
coef(fit1)
```

```{r}
# All the confidence intervals for the coefficients
confint(fit1)
```
```{r}
data.frame(summary(lsmeans(fit1, pairwise ~ burn_unburn),type = "response"))
```

#### t-test
```{r}
( fit1_t = t.test(mean_gcc_10m ~ burn_unburn, data = field_gcc) )
```
##### Table
Difference in means
```{r}
0.3486187-0.3816558
```

```{r}
# Write out the results from the two-sample t-test with unequal variances
# A title for the test
titleres = as.character(expression(bold("Welch"~t-test*~"for"~a~difference*~"in"~means)))
# This is the t stat with df and p-value
ttestres1 = as.character(expression(t[-2.6]==23.2*","~italic(p)==0.02))
# The estimated difference in group means (I calculated from the test results)
diff1 = as.character(expression(Delta==-0.033))
# The 95% CI of the difference
ci1 = as.character(expression(95*"%"~CI*":"~-0.041~to~-0.005))
# Put these into a single column of a data.frame
d1 = data.frame(col = rbind(ttestres1, diff1, ci1) )
```

```{r}
t1 = tableGrob(d1, rows = NULL, cols = NULL,
theme = ttheme_default(core = list(bg_params = list(fill = "white"),
fg_params = list(parse = TRUE),
padding = unit(c(2.5, 2.5), "mm"))))
```

```{r}
t1 = gtable_add_grob(t1, grobs = rectGrob(gp = gpar(fill = NA, lwd = NA)),
t = 1, b = nrow(t1), r = ncol(t1), l = 1)
```

#### Boxplot
```{r}
g1 = ggplot(data=field_gcc, aes(x = burn_unburn, y = mean_gcc_10m, color=burn_unburn) ) + # define plot axes
  geom_boxplot(outlier.shape = NA) + # Add boxplots for each group
  geom_point(aes(color = burn_unburn, shape = burn_unburn), size = 3, position = position_jitter(w = 0.15, h = 0, seed=10)) +
stat_summary(fun = mean, geom= "point", size = 4) + # Add means to the plot
  scale_shape_manual(values = c(23, 24)) +
  labs(x=(NULL), y= "Mean GCC") +
  
  scale_color_manual(values = c("#E69F00", "#009E73")) +
  
  scale_x_discrete(labels= c("Burned", "Unburned")) +
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))


g1
```

## 2. Model:NDVI burn/unburned
```{r}
fit2 = lm(mean_ndvi_10m ~ burn_unburn, data = field_gcc_ndvi)
```

#### Residuals
```{r}
# Get the fitted value for each observation
field_gcc_ndvi$fit2 = fitted(fit2)
# Get the residuals of the model
field_gcc_ndvi$res2 = residuals(fit2)
```

```{r}
qplot(x = fit2, y = res2, data = field_gcc_ndvi,
main = "Residuals vs Fitted Values")
```

```{r}
qplot(x = burn_unburn, y = res2, data = field_gcc_ndvi,
xlab = "Burn v unburn group",
ylab = "Residuals",
main = "Residuals vs burn/unburn")
```
```{r}
qplot(x = factor(1), y = res2, data = field_gcc_ndvi, geom = "boxplot")
```

```{r}
qqnorm(field_gcc_ndvi$res2, main = "Normal QQ Plot of Residuals")
qqline(field_gcc_ndvi$res2) # add reference line to the qq plot
```

```{r}
plot(fit2, which = 1) # residual vs fitted values
```

```{r}
plot(fit2, which = 2) # qqnorm plot of residuals
```

#### Summary
```{r}
summary(fit2)
```
```{r}
# All the coefficients
coef(fit2)
```

```{r}
# All the confidence intervals for the coefficients
confint(fit2)
```
```{r}
data.frame(summary(lsmeans(fit2, pairwise ~ burn_unburn),type = "response"))
```

#### t-test
```{r}
( fit2_t = t.test(mean_ndvi_10m ~ burn_unburn, data = field_gcc_ndvi) )
```



##### Table
Difference in means
```{r}
0.6391836-0.728424
```

```{r}
# Write out the results from the two-sample t-test with unequal variances
# A title for the test
titleres = as.character(expression(bold("Welch"~t-test*~"for"~a~difference*~"in"~means)))
# This is the t stat with df and p-value
ttestres2 = as.character(expression(italic(p)<0.001))
# The estimated difference in group means (I calculated from the test results)
diff2 = as.character(expression(Delta==-0.089))
# The 95% CI of the difference
ci2 = as.character(expression(CI*":"~-0.121~to~-0.058))
# Put these into a single column of a data.frame
d2 = data.frame(col = rbind(ttestres2, diff2, ci2) )
 
```

```{r}
t2 = tableGrob(d2, rows = NULL, cols = NULL,
theme = ttheme_default(core = list(bg_params = list(fill = "white"),
fg_params = list(parse = TRUE),
padding = unit(c(2.5, 2.5), "mm"))))
```

```{r}
t2 = gtable_add_grob(t2, grobs = rectGrob(gp = gpar(fill = NA, lwd = NA)),
t = 1, b = nrow(t2), r = ncol(t2), l = 1)
```

#### Boxplot
```{r}
g2 = ggplot(data=field_gcc_ndvi, aes(x = burn_unburn, y = mean_ndvi_10m, color=burn_unburn) ) + # define plot axes
  geom_boxplot(outlier.shape = NA) + # Add boxplots for each group
  geom_point(aes(color = burn_unburn, shape = burn_unburn), size = 3, position = position_jitter(w = 0.15, h = 0, seed=10)) +
stat_summary(fun = mean, geom= "point", size = 4) + # Add means to the plot
  scale_shape_manual(values = c(23, 24)) +
  labs(x=(NULL), y= "Mean NDVI") +
  
  scale_color_manual(values = c("#E69F00", "#009E73")) +
  
  scale_x_discrete(labels= c("Burned", "Unburned")) +
  theme_bw() + 
  theme(legend.position = "none") +  
theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 12, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))


g2
```

  
## 7. Model: GCC burn/unburned
```{r}
mod7 = glm(mean_gcc_10m ~ burn_unburn, data = field_gcc, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod7.res = simulateResiduals(fittedModel = mod7, n = 500)
mod7.res$scaledResiduals
mod7.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod7.res)
```

```{r}
testDispersion(mod7.res)
```

### Summary
```{r}
summary(mod7)
```
#### Summary Data Frame

```{r}

mod7_df = data.frame(summary(lsmeans(mod7, revpairwise ~ burn_unburn, type = "response", infer = TRUE)))
mod7_df 
mod7_df1 = mod7_df %>% 
  mutate(model="mod7") %>% 
  mutate(response = "GCC") %>% 
  rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% 
  
  
  dplyr::select(model:response, explanatory:se, lcl:contrasts.SE, contrasts.z.ratio:contrasts.p.value)
mod7_df1
```

```{r}
( mod7_contrast = data.frame(summary(lsmeans(mod7, revpairwise ~ burn_unburn),type = "response", infer = TRUE)$contrasts))

mod7_contrast1 = mod7_contrast %>%  mutate(response = "GCC")  
 
```

### Data for graph

```{r}
(mod7_graph = data.frame(summary(lsmeans(mod7, pairwise ~ burn_unburn),type = "response")))
```


```{r}
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod7_graph$lsmeans.burn_unburn)[levels(mod7_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod7_graph1 = dplyr::select(mod7_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod7_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod7_graph1 = data.frame(mod7_graph1)
mod7_graph1

```

### Graph

```{r}
plot_mod7 = ggplot(data = mod7_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod7 
```

#### Box plot

```{r}
boxplot_mod7 = ggplot(field_gcc, aes(x=burn_unburn, y=mean_gcc_10m, color = burn_unburn, fill=burn_unburn) ) + # define plot axes
geom_boxplot(fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = .5) + 
stat_summary(fun.y = mean, geom= "point", shape = 18, size = 5) + 
labs(x=(NULL), y= "Mean GCC") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod7

```



## 8. Model: NDVI burn/unburned
```{r}
mod8 = glm(mean_ndvi_10m ~ burn_unburn, data = field_gcc_ndvi, family = gaussian)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod8.res = simulateResiduals(fittedModel = mod8, n = 500)
mod8.res$scaledResiduals
mod8.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod8.res)
```

```{r}
testDispersion(mod8.res)
```

### Summary
```{r}
summary(mod8)
```

#### Summary Dataframe
```{r}
mod8_df = data.frame(summary(lsmeans(mod8, revpairwise ~ burn_unburn, type = "response", infer = TRUE, adjust = "tukey")))
mod8_df
mod8_df1 = mod8_df %>% 
  mutate(model="mod8") %>% 
  mutate(response = "NDVI") %>% 
  rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% 
  dplyr::select(model:response, explanatory:se, lcl:contrasts.SE, contrasts.z.ratio:contrasts.p.value)
mod8_df1
```

```{r}
( mod8_contrast = data.frame(summary(lsmeans(mod8, revpairwise ~ burn_unburn),type = "response", infer = TRUE)$contrasts))
mod8_contrast1 = mod8_contrast %>%  mutate(response = "NDVI") 
```

### Data for graph

```{r}
(mod8_graph = data.frame(summary(lsmeans(mod8, pairwise ~ burn_unburn),type = "response")))
```
```{r}
mod8_df = data.frame(summary(lsmeans(mod8, revpairwise ~ burn_unburn, type = "response", infer = TRUE, adjust = "tukey")))
mod8_df = mod8_df %>% mutate(model="mod8") %>% mutate(response = "NDVI") %>% rename(explanatory = lsmeans.burn_unburn, estimate = lsmeans.lsmean, se = lsmeans.SE, lcl = lsmeans.asymp.LCL, ucl = lsmeans.asymp.UCL, contrast = contrasts.contrast) %>% dplyr::select(model:response, explanatory:se, lcl:contrasts.SE)
mod8_df
```

```{r}
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="burned"] = "Burned"
levels(mod8_graph$lsmeans.burn_unburn)[levels(mod8_graph$lsmeans.burn_unburn)=="unburned"] = "Unburned"

( mod8_graph1 = dplyr::select(mod8_graph, lsmeans.burn_unburn:lsmeans.asymp.UCL))



names(mod8_graph1)[1:6] = c("burn_unburn", "response", "se", "df", "lcl", "ucl")
mod8_graph1 = data.frame(mod8_graph1)
mod8_graph1

```

### Graph

```{r}
plot_mod8 = ggplot(data = mod8_graph1, aes(x = burn_unburn, y = response, color = burn_unburn) ) + 
   geom_errorbar(width = .2, lwd = .75, aes(ymin = lcl, ymax = ucl), position = position_dodge(width = .75)) + 
geom_point(size = 3, position = position_dodge(width = .75)) + 
  labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

plot_mod8 
```

```{r}
boxplot_mod8 = ggplot(field_gcc_ndvi, aes(x=burn_unburn, y=mean_ndvi_10m, color = burn_unburn, fill = burn_unburn) ) + # define plot axes
geom_boxplot(fill = "white") +
  geom_dotplot(binaxis = "y", stackdir = "center",
dotsize = .5) + # Dotplot by group
stat_summary(fun.y = mean, geom= "point", shape = 18, size = 5) + # Add means to the plot
labs(x=(NULL), y= "Mean NDVI") +
  scale_color_manual(values = c("#E69F00", "#009E73")) + 
  comp_theme

boxplot_mod8

```


## 11. Model: GCC distance from unburned edge 
```{r}
mod11 = glm(mean_gcc_10m ~ plot_dis, data = field_gcc, family = gaussian)
```

```{r}
fit3 = lm(mean_gcc_10m ~ plot_dis, data = field_gcc)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod11.res = simulateResiduals(fittedModel = mod11, n = 500)
mod11.res$scaledResiduals
mod11.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod11.res)
```

```{r}
testDispersion(mod11.res)
```

### Summary
```{r}
summary(mod11)
```

#### Summary Dataframe

```{r}
mod11_df = data.frame(summary(mod11)$coefficients[,], confint(mod11), deviance(mod11), summary(mod11)$null.deviance, extractAIC(mod11))
mod11_df
mod11_df2 = tibble::rownames_to_column(mod11_df, "coefficent")
mod11_df3 = mod11_df2 %>% 
  mutate(model = "mod11") %>% 
  mutate(response = "GCC" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod11., null_deviance= summary.mod11..null.deviance, AIC = extractAIC.mod11.) %>% dplyr::select(model:response, coefficent:AIC)
mod11_df3
```
#### lm summary
```{r}
fit3_df = data.frame(summary(fit3)$coefficients[,], confint(fit3), extractAIC(fit3))
fit3_df
fit3_df2 = tibble::rownames_to_column(fit3_df, "coefficent")
fit3_df3 = fit3_df2 %>% 
  mutate(model = "fit3") %>% 
  mutate(response = "GCC" ) %>%  
  mutate(rmse = RMSE(fit3)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit3.) %>% dplyr::select(model:response, coefficent:rmse)
fit3_df3
```

### Predicted data for for graph
```{r}
preddat_mod11 = data.frame(plot_dis = field_gcc$plot_dis)

head(preddat_mod11)

pred_mod11 = predict(mod11, newdata = preddat_mod11, se.fit = TRUE)

UL_mod11 = with(pred_mod11, fit + 2*se.fit)
LL_mod11 = with(pred_mod11, fit - 2*se.fit)

field_gcc11 = mutate(field_gcc, pred_mod11 = (pred_mod11$fit), 
               ucl_mod11 = (UL_mod11), 
               lcl_mod11 = (LL_mod11))
```


### Graph  

```{r}
plot_mod11 = ggplot(data = field_gcc11, aes(x = plot_dis, y = mean_gcc_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod11), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod11, ymax = ucl_mod11, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod11), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod11), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean GCC") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_y_continuous(breaks = c(0.34, 0.36, 0.38, 0.40, 0.42)) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod11
```
#### Graph lm

```{r}
p3 = ggplot(data = field_gcc, aes(x = plot_dis, y = mean_gcc_10m)) + 
    geom_point(size = 2) +  
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean GCC") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_y_continuous(breaks = c(0.34, 0.36, 0.38, 0.40, 0.42)) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))


p3
  
```

## 12.  Model: NDVI distance from edge
```{r}
mod12 = glm(mean_ndvi_10m ~ plot_dis, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit4 = lm(mean_ndvi_10m ~ plot_dis, data = field_gcc_ndvi)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod12.res = simulateResiduals(fittedModel = mod12, n = 500)
mod12.res$scaledResiduals
mod12.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod12.res)
```

```{r}
testDispersion(mod12.res)
```

### Summary
```{r}
summary(mod12)
```

#### Summary Dataframe

```{r}
mod12_df = data.frame(summary(mod12)$coefficients[,], confint(mod12), deviance(mod12), summary(mod12)$null.deviance, extractAIC(mod12))
mod12_df
mod12_df2 = tibble::rownames_to_column(mod12_df, "coefficent")
mod12_df3 = mod12_df2 %>% 
  mutate(model = "mod12") %>% 
  mutate(response = "NDVI" ) %>%  
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod12., null_deviance= summary.mod12..null.deviance, AIC = extractAIC.mod12.) %>% dplyr::select(model:response, coefficent:AIC)
mod12_df3
```
### lm summary
```{r}
fit4_df = data.frame(summary(fit4)$coefficients[,], confint(fit4), extractAIC(fit4))
fit4_df
fit4_df2 = tibble::rownames_to_column(fit4_df, "coefficent")
fit4_df3 = fit4_df2 %>% 
  mutate(model = "fit4") %>% 
  mutate(response = "GCC" ) %>%  
  mutate(rmse = RMSE(fit4)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit4.) %>% dplyr::select(model:response, coefficent:rmse)
fit4_df3
```

```{r}
preddat_mod12 = data.frame(plot_dis = field_gcc_ndvi$plot_dis)

head(preddat_mod12)

pred_mod12 = predict(mod12, newdata = preddat_mod12, se.fit = TRUE)

UL_mod12 = with(pred_mod12, fit + 2*se.fit)
LL_mod12 = with(pred_mod12, fit - 2*se.fit)

field_gcc_ndvi12 = mutate(field_gcc_ndvi, pred_mod12 = (pred_mod12$fit), 
               ucl_mod12 = (UL_mod12), 
               lcl_mod12 = (LL_mod12))
```

### Graph  

```{r}
plot_mod12 = ggplot(data = field_gcc_ndvi12, aes(x = plot_dis, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod12), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod12, ymax = ucl_mod12, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod12), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod12), linetype='longdash', size = 1) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean NDVI") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme + guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))

plot_mod12
```
#### Graph lm

```{r}
p4 = ggplot(data = field_gcc_ndvi, aes(x = plot_dis, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    geom_vline(xintercept=0, linetype="dashed", color = "#9C270E", size = 1) +
    ylab("Mean NDVI") +
    xlab("Distance from the unburned edge \n(m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(-50, 0, 50, 100, 150, 200))


p4
  
```

# Summary output Combine
## Burned-Unburned

```{r}
burn_unburn_sum = rbind(mod7_df1, mod8_df1)
burn_unburn_sum
```

```{r eval=FALSE, include=FALSE}
write.csv(burn_unburn_sum, '../outputs/model_summary/2020-05-27_burn-unburn-summary.csv', row.names = F)

```


```{r}
burn_unburn_contrast = rbind(mod7_contrast1, mod8_contrast1)
burn_unburn_contrast
```

```{r eval=FALSE, include=FALSE}
write.csv(burn_unburn_contrast, '../outputs/model_summary/2020-06-01_burn-unburn-contrast.csv', row.names = F)

```

```{r}
edge_sum = rbind(mod11_df3, mod12_df3)
edge_sum
```

```{r eval=FALSE, include=FALSE}
write.csv(edge_sum, '../outputs/model_summary/2020-05-27_distance-edge-summary.csv', row.names = F)

```


# Manuscript figures

## lm models burn/unburn
```{r fig.height=3, fig.width=6}
p1 = cowplot::plot_grid(g1, g2, labels = c("A", "B"), ncol = 2) +
  draw_label("p=0.02", x = .42, y = .15, size = 12, fontface = "plain") +
  draw_label("p<0.001", x = .91, y = .15, size = 12, fontface = "plain") 
p1
```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-13_burn-unburn_t-test.jpeg", plot = p1, width = 6, height = 3, units = c("in"), dpi=600 )
```

### Distance for unburned lm
```{r fig.height=3, fig.width=6}

lm_grid_edge1 = cowplot::plot_grid(p3, p4, labels = c("A", "B"), align = "hv", ncol= 2) +
  draw_label("*", x = .95, y = .87, size = 36, fontface = "bold") +
  draw_label("*", x = .45, y = .87, size = 36, fontface = "bold") 
lm_grid_edge1

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-13_distance_edge_pts_lm.jpeg", plot = lm_grid_edge1, width = 6, height = 3, units = c("in"), dpi=600 )
```