---
title: "UAV-Biomass-Nonlinear"
author: "Anna Talucci"
date: "8/10/2020"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(rcompanion)
library(qpcR)
library(caret)

```

# Functions

```{r}
numextract <- function(string){ 
  str_extract(string, "\\-*\\d+\\.*\\d*")
} 

```

# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-08-10_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```
# Pull out GCC and NDVI by buffer size

```{r}
gcc_long = gcc_all %>% 
  dplyr::select(ID:mean_gcc_10m) %>%
  pivot_longer(-ID, names_to = "buffer", values_to = "gcc") %>%
  mutate(buf_res = numextract(buffer))

gcc_long
```

```{r}
ndvi_long = ndvi_all %>% 
  dplyr::select(ID:mean_ndvi_10m) %>%
  pivot_longer(-ID, names_to = "buffer", values_to = "ndvi") %>%
  mutate(buf_res = numextract(buffer))

ndvi_long
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```
# Field data +  long data
```{r}
field_gcc_long = merge(field_data, gcc_long, by="ID")

field_gcc_long
```

```{r}
field_ndvi_long = merge(field_data, ndvi_long, by="ID")

field_ndvi_long
```

# Variables as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)
```

```{r eval=FALSE, include=FALSE}
str(field_gcc)
str(field_gcc_ndvi)
```


```{r}
field_gcc_long$burn_year = as.factor(field_gcc_long$burn_year)
field_ndvi_long$burn_year= as.factor(field_ndvi_long$burn_year)
field_gcc_long$buf_res = as.factor(field_gcc_long$buf_res)
field_ndvi_long$buf_res = as.factor(field_ndvi_long$buf_res)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
theme(panel.grid = element_blank(),
        panel.border = element_blank())
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 10, hjust = 0.5, vjust = -0.2),
        axis.title.y = element_text(size = 10, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 9, color = "black"),
        axis.text.y = element_text(size = 9, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}

blank_xy_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.1, r = 0.1, b = 0.6, l = 0.6), "cm")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))


```

 
```{r}

blank_x_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

 
```{r}

blank_y_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```
# Min max biomass


```{r}
min(field_gcc$woody_biomass_C_g_m)
max(field_gcc$woody_biomass_C_g_m)

```

```{r}
min(field_gcc$live_woody_biomass_C_g_m)
max(field_gcc$live_woody_biomass_C_g_m)

```

# Analysis: 

```{r}
head(field_gcc_long)
```
```{r}
fd_gcc_sub = field_gcc_long %>% 
  dplyr::select(ID:burn_unburn, live_woody_biomass_C_g_m, gcc:buf_res) 

head(fd_gcc_sub)
```

 filter outliers
```{r}
fd_gcc_sub %>% filter(live_woody_biomass_C_g_m > 1500)
```

```{r}
fd_gcc_sub %>% filter(burn_unburn == "unburned")
```

Data outliers removed 
```{r}
gcc_bio_out = fd_gcc_sub %>% filter(live_woody_biomass_C_g_m < 3000)
```

```{r}
gcc_bio_out1 = fd_gcc_sub %>% filter(burn_unburn == "unburned")
```

***
```{r}
#fit first degree polynomial equation:
fit  <- lm(live_woody_biomass_C_g_m ~ gcc + buf_res, data = gcc_bio_out1)
#second degree
fit2 <- lm(live_woody_biomass_C_g_m ~ poly(gcc,2,raw=TRUE) + buf_res, data = gcc_bio_out1)
#third degree
fit3 <- lm(live_woody_biomass_C_g_m ~ poly(gcc,3,raw=TRUE) + buf_res, data = gcc_bio_out1)
#fourth degree
fit4 <- lm(live_woody_biomass_C_g_m ~ poly(gcc,4,raw=TRUE) + buf_res, data = gcc_bio_out1)

```

```{r}
summary(fit)
summary(fit2)
summary(fit3)
summary(fit4)
```
```{r}
p <- ggplot(gcc_bio_out1, aes(x = gcc, y = live_woody_biomass_C_g_m, color = buf_res)) + 
  geom_point()

p
```
ggplot(mtcars, aes(x = hp, y = mpg, colour = factor(vs))) + geom_point() +
    stat_smooth(aes(group = 1), method = "lm", formula = y ~ x, se = FALSE)
```{r}
p + 
  stat_smooth(method = "lm", formula = y ~ x, size = 1, se = FALSE,
    colour = "black") + 
  stat_smooth(method = "lm", formula = y ~ x + I(x^2),
    size = 1, se = FALSE, colour = "blue") + 
  stat_smooth(method = "loess", formula = y ~
    x, size = 1, se = FALSE, colour = "red") + 
  stat_smooth(method = "gam", formula = y ~
    s(x), size = 1, se = FALSE, colour = "green") + 
  stat_smooth(method = "gam",
    formula = y ~ s(x, k = 3), size = 1, se = FALSE, colour = "violet")
```



```{r}
ggplot(gcc_bio_out, aes(x = gcc, y = live_woody_biomass_C_g_m, color = factor(buf_res))) + 
  geom_point() +
   stat_smooth(method = "lm", formula = y ~ x, size = 1, se = FALSE) 
 
```

```{r}
ggplot(gcc_bio_out, aes(x = gcc, y = live_woody_biomass_C_g_m, color = factor(buf_res))) + 
  geom_point() +
   
  stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1, se = FALSE) 
```




```{r}
ggplot(gcc_bio_out, aes(x = gcc, y = live_woody_biomass_C_g_m, color = factor(buf_res))) + 
  geom_point() + 
  stat_smooth(method = "loess", formula = y ~ x, size = 1, se = FALSE) 
```


```{r}
ggplot(gcc_bio_out, aes(x = gcc, y = live_woody_biomass_C_g_m, color = factor(buf_res))) + 
  geom_point() + 
  stat_smooth(method = "gam", formula = y ~ s(x), size = 1, se = FALSE) 
```


```{r}
ggplot(gcc_bio_out, aes(x = gcc, y = live_woody_biomass_C_g_m, color = factor(buf_res))) + 
  geom_point() + 
  stat_smooth(method = "gam", formula = y ~ s(x, k = 3), size = 1, se = FALSE)
```



***
```{r}
field_gcc_long1 = field_gcc_long %>% 
  dplyr::select(ID, burn_year, live_woody_biomass_C_g_m, gcc, buf_res)

head(field_gcc_long1)
```



```{r}
set.seed(123)
training.samples <- field_gcc_long1$live_woody_biomass_C_g_m %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- field_gcc_long1[training.samples, ]
test.data <- field_gcc_long1[-training.samples, ]
```

```{r}
ggplot(train.data, aes(gcc, live_woody_biomass_C_g_m, color = buf_res) ) +
  geom_point() +
  stat_smooth()
```

```{r}
# Build the model
model <- lm(live_woody_biomass_C_g_m ~ poly(gcc, 5, raw = TRUE), data = train.data)
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
data.frame(
  RMSE = RMSE(predictions, test.data$live_woody_biomass_C_g_m),
  R2 = R2(predictions, test.data$live_woody_biomass_C_g_m)
)
```
```{r}
# Build the model
model <- lm(live_woody_biomass_C_g_m ~ log(gcc):buf_res, data = field_gcc_long1)
# Make predictions
predictions <- model %>% predict(field_gcc_long1)
# Model performance
data.frame(
  RMSE = RMSE(predictions, field_gcc_long1$live_woody_biomass_C_g_m),
  R2 = R2(predictions, field_gcc_long1$live_woody_biomass_C_g_m)
)

summary(model)
```

# Biomass as it relates to GCC and NDVI

#Model GCC

```{r}
model1 = lm(live_woody_biomass_C_g_m ~ gcc:buf_res, data = gcc_bio_out)
```

```{r}
summary(model1)
```
