---
title: "UAV-Scale-Analysis"
author: "Anna Talucci"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview


# Pakcages
```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(lme4)
library(cowplot)
library(lme4)
library(lsmeans)
library(DHARMa)
library(qpcR)
```


# Field Data
```{r}
field_data = read.csv("../data/field_subset/field_data_all.csv")
```

```{r}
head(field_data)
```

## field Plot sizes

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(shrub_plot_area))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(min(tree_radius))
```

```{r}
field_data %>% group_by(site, transect) %>% 
  summarise(max(tree_radius))
```

# UAV Data

```{r}
gcc_all = read.csv("../data/extracted_data/gcc_all.csv", strip.white = TRUE)
ndvi_all = read.csv("../data/extracted_data/2020-05-20_ndvi_all_pix4D.csv", strip.white = TRUE)
```

```{r}
head(gcc_all)
head(ndvi_all)
```

# Combine Field and UAV data

```{r}
gcc_ndvi = merge(gcc_all, ndvi_all, by="ID")
gcc_ndvi
field_gcc = merge(field_data, gcc_all, by="ID") 
field_gcc
field_gcc_ndvi = merge(field_data, gcc_ndvi,  "ID")
field_gcc_ndvi
```

# burn_year as factor

```{r}
field_gcc$burn_year = as.factor(field_gcc$burn_year)
field_gcc_ndvi$burn_year = as.factor(field_gcc_ndvi$burn_year)

str(field_gcc)
str(field_gcc_ndvi)
```



# Define graph Theme and color Palette 

```{r}
comp_theme = theme_bw() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        axis.line = element_line(colour = "black"))
```
 
```{r}

reg_theme = theme_bw() + theme(legend.position = "none") +
  theme(plot.margin = unit(c(t = 0.3, r = 0.3, b = 0.3, l = 0.1), "cm")) +
  theme(axis.title.x = element_text(size = 11, hjust = 0.5, vjust = -0.1),
        axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"))

```

```{r}
cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

# Analysis: 

# Part 1: GCC relates to NDVI

Assess spatial scale...


## 1. Model: NDVIas  function of GCC
```{r}
mod1 = glm(mean_ndvi_25cm ~ mean_gcc_25cm, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit1 = lm(mean_ndvi_25cm ~ mean_gcc_25cm, data = field_gcc_ndvi)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod1.res = simulateResiduals(fittedModel = mod1, n = 500)
mod1.res$scaledResiduals
mod1.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod1.res)
```

```{r}
testDispersion(mod1.res)
```

### Summary
```{r}
summary(mod1)
```


```{r}
summary(fit1)
AIC(fit1)
RMSE(fit1)
```

```{r}
coef(mod1)

```


#### Summary Dataframe

```{r}
mod1_df = data.frame(summary(mod1)$coefficients[,], confint(mod1), deviance(mod1), summary(mod1)$null.deviance, extractAIC(mod1))
mod1_df
mod1_df2 = tibble::rownames_to_column(mod1_df, "coefficent")
mod1_df3 = mod1_df2 %>% 
  mutate(model = "mod1") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(mod1)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod1., null_deviance= summary.mod1..null.deviance, AIC = extractAIC.mod1.) %>% dplyr::select(model:response, coefficent:rmse)
mod1_df3
```
#### lm summary
```{r}
fit1_df = data.frame(summary(fit1)$coefficients[,], confint(fit1), extractAIC(fit1))
fit1_df
fit1_df2 = tibble::rownames_to_column(fit1_df, "coefficent")
fit1_df3 = fit1_df2 %>% 
  mutate(model = "fit1") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit1)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit1.) %>% dplyr::select(model:response, coefficent:rmse)
fit1_df3
```

### Data for graph
```{r}
preddat_mod1 = data.frame(mean_gcc_25cm = field_gcc_ndvi$mean_gcc_25cm)

head(preddat_mod1)

pred_mod1 = predict(mod1, newdata = preddat_mod1, se.fit = TRUE)

UL_mod1 = with(pred_mod1, fit + 2*se.fit)
LL_mod1 = with(pred_mod1, fit - 2*se.fit)

field_gcc_ndvi1 = mutate(field_gcc_ndvi, pred_mod1 = pred_mod1$fit, 
               ucl_mod1 = UL_mod1, 
               lcl_mod1 = LL_mod1)
```

### Graph 
```{r}
p1 = ggplot(data = field_gcc_ndvi, aes(x = mean_gcc_25cm, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI (25cm)") +
    xlab("Mean GCC (25cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(0.32, 0.37, 0.42, 0.47))
p1
```


```{r fig.height=3, fig.width=3}
plot_mod1 = ggplot(data = field_gcc_ndvi1, aes(x = mean_gcc_25cm, y = mean_ndvi_25cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod1), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod1, ymax = ucl_mod1, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod1), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod1), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (25cm)") +
    xlab("Mean GCC (25cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks = c(0.32, 0.37, 0.42, 0.47)) 

plot_mod1
```


## 2. Model: NDVIas  function of GCC
```{r}
mod2 = glm(mean_ndvi_50cm ~ mean_gcc_50cm, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit2 = lm(mean_ndvi_50cm ~ mean_gcc_50cm, data = field_gcc_ndvi)
```

### Residuals with DHARMa
```{r, include=FALSE}
mod2.res = simulateResiduals(fittedModel = mod2, n = 500)
mod2.res$scaledResiduals
mod2.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod2.res)
```

```{r}
testDispersion(mod2.res)
```

### Summary
```{r}
summary(mod2)
```

```{r}
with(summary(mod2), 1 - deviance/null.deviance)
```


```{r}
RMSE(mod2)
```

#### Summary Dataframe

```{r}
mod2_df = data.frame(summary(mod2)$coefficients[,], confint(mod2), deviance(mod2), summary(mod2)$null.deviance, extractAIC(mod2))
mod2_df
mod2_df2 = tibble::rownames_to_column(mod2_df, "coefficent")
mod2_df3 = mod2_df2 %>% 
  mutate(model = "mod2") %>% 
  mutate(response = "NDVI" ) %>% 
  mutate(rmse = RMSE(mod2)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod2., null_deviance= summary.mod2..null.deviance, AIC = extractAIC.mod2.) %>% dplyr::select(model:response, coefficent:rmse)
mod2_df3
```

#### lm summary
```{r}
fit2_df = data.frame(summary(fit2)$coefficients[,], confint(fit2), extractAIC(fit2))
fit2_df
fit2_df2 = tibble::rownames_to_column(fit2_df, "coefficent")
fit2_df3 = fit2_df2 %>% 
  mutate(model = "fit2") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit2)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit2.) %>% dplyr::select(model:response, coefficent:rmse)
fit2_df3
```


### Data for graph
```{r}
preddat_mod2 = data.frame(mean_gcc_50cm = field_gcc_ndvi$mean_gcc_50cm)

head(preddat_mod2)

pred_mod2 = predict(mod2, newdata = preddat_mod2, se.fit = TRUE)

UL_mod2 = with(pred_mod2, fit + 2*se.fit)
LL_mod2 = with(pred_mod2, fit - 2*se.fit)

field_gcc_ndvi2 = mutate(field_gcc_ndvi, pred_mod2 = pred_mod2$fit, 
               ucl_mod2 = UL_mod2, 
               lcl_mod2 = LL_mod2)
```

### Graph 
```{r}
p2 = ggplot(data = field_gcc_ndvi, aes(x = mean_gcc_50cm, y = mean_ndvi_50cm)) + 
    geom_point(size = 2) + 
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI (50cm)") +
    xlab("Mean GCC (50cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

p2

```


```{r fig.height=3, fig.width=3}
plot_mod2 = ggplot(data = field_gcc_ndvi2, aes(x = mean_gcc_50cm, y = mean_ndvi_50cm)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod2), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod2, ymax = ucl_mod2, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod2), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod2), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (50cm)") +
    xlab("Mean GCC (50cm)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod2
```

## 3. Model: NDVIas  function of GCC
```{r}
mod3 = glm(mean_ndvi_1m ~ mean_gcc_1m, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit3 = lm(mean_ndvi_1m ~ mean_gcc_1m, data = field_gcc_ndvi)
```
### Residuals with DHARMa
```{r, include=FALSE}
mod3.res = simulateResiduals(fittedModel = mod3, n = 500)
mod3.res$scaledResiduals
mod3.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod3.res)
```

```{r}
testDispersion(mod3.res)
```

### Summary
```{r}
summary(mod3)
```

```{r}
with(summary(mod3), 1 - deviance/null.deviance)
```


```{r}
RMSE(mod3)
```

#### Summary Dataframe
```{r}
mod3_df = data.frame(summary(mod3)$coefficients[,], confint(mod3), deviance(mod3), summary(mod3)$null.deviance, extractAIC(mod3))
mod3_df
mod3_df2 = tibble::rownames_to_column(mod3_df, "coefficent")
mod3_df3 = mod3_df2 %>% 
  mutate(model = "mod3") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(mod3)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod3., null_deviance= summary.mod3..null.deviance, AIC = extractAIC.mod3.) %>% dplyr::select(model:response, coefficent:rmse)
mod3_df3
```
#### lm summary
```{r}
fit3_df = data.frame(summary(fit3)$coefficients[,], confint(fit3), extractAIC(fit3))
fit3_df
fit3_df2 = tibble::rownames_to_column(fit3_df, "coefficent")
fit3_df3 = fit3_df2 %>% 
  mutate(model = "fit3") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit3)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit3.) %>% dplyr::select(model:response, coefficent:rmse)
fit3_df3
```

```{r}
data.frame(summary(lsmeans(mod3, ~ mean_gcc_1m), type = "response"))
```

### Data for graph
```{r}
preddat_mod3 = data.frame(mean_gcc_1m = field_gcc_ndvi$mean_gcc_1m)

head(preddat_mod3)

pred_mod3 = predict(mod3, newdata = preddat_mod3, se.fit = TRUE)

UL_mod3 = with(pred_mod3, fit + 2*se.fit)
LL_mod3 = with(pred_mod3, fit - 2*se.fit)

field_gcc_ndvi3 = mutate(field_gcc_ndvi, pred_mod3 = pred_mod3$fit, 
               ucl_mod3 = UL_mod3, 
               lcl_mod3 = LL_mod3)
```

### Graph 

```{r}
p3 = ggplot(data = field_gcc_ndvi, aes(x = mean_gcc_1m, y = mean_ndvi_1m)) + 
    geom_point(size = 2) +  
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI (1m)") +
    xlab("Mean GCC  (1m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 
p3

```


```{r fig.height=3, fig.width=3}
plot_mod3 = ggplot(data = field_gcc_ndvi3, aes(x = mean_gcc_1m, y = mean_ndvi_1m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod3), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod3, ymax = ucl_mod3, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod3), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod3), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (1m)") +
    xlab("Mean GCC  (1m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) 

plot_mod3
```

## 4. Model: NDVIas  function of GCC
```{r}
mod4 = glm(mean_ndvi_3m ~ mean_gcc_3m, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit4 = lm(mean_ndvi_3m ~ mean_gcc_3m, data = field_gcc_ndvi)
```
### Residuals with DHARMa
```{r, include=FALSE}
mod4.res = simulateResiduals(fittedModel = mod4, n = 500)
mod4.res$scaledResiduals
mod4.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod4.res)
```

```{r}
testDispersion(mod4.res)
```

### Summary
```{r}
summary(mod4)
```


#### Summary Dataframe

```{r}
mod4_df = data.frame(summary(mod4)$coefficients[,], confint(mod4), deviance(mod4), summary(mod4)$null.deviance, extractAIC(mod4))
mod4_df
mod4_df2 = tibble::rownames_to_column(mod4_df, "coefficent")
mod4_df3 = mod4_df2 %>% 
  mutate(model = "mod4") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(mod4)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod4., null_deviance= summary.mod4..null.deviance, AIC = extractAIC.mod4.) %>% dplyr::select(model:response, coefficent:rmse)
mod4_df3
```
#### lm summary
```{r}
fit4_df = data.frame(summary(fit4)$coefficients[,], confint(fit4), extractAIC(fit4))
fit4_df
fit4_df2 = tibble::rownames_to_column(fit4_df, "coefficent")
fit4_df3 = fit4_df2 %>% 
  mutate(model = "fit4") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit4)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit4.) %>% dplyr::select(model:response, coefficent:rmse)
fit4_df3
```

### Data for graph
```{r}
preddat_mod4 = data.frame(mean_gcc_3m = field_gcc_ndvi$mean_gcc_3m)

head(preddat_mod4)

pred_mod4 = predict(mod4, newdata = preddat_mod4, se.fit = TRUE)

UL_mod4 = with(pred_mod4, fit + 2*se.fit)
LL_mod4 = with(pred_mod4, fit - 2*se.fit)

field_gcc_ndvi4 = mutate(field_gcc_ndvi, pred_mod4 = pred_mod4$fit, 
               ucl_mod4 = UL_mod4, 
               lcl_mod4 = LL_mod4)
```

### Graph 

```{r}
p4 = ggplot(data = field_gcc_ndvi4, aes(x = mean_gcc_3m, y = mean_ndvi_3m)) + 
    geom_point(size = 2) +  
  
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI (3m)") +
    xlab("Mean GCC (3m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.9, by = .05), labels = c("0.6", "", "0.7", "", "0.8", "", ""))
p4
```

```{r fig.height=3, fig.width=3}
plot_mod4 = ggplot(data = field_gcc_ndvi4, aes(x = mean_gcc_3m, y = mean_ndvi_3m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod4), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod4, ymax = ucl_mod4, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod4), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod4), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (3m)") +
    xlab("Mean GCC (3m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.9, by = .05), labels = c("0.6", "", "0.7", "", "0.8", "", ""))

plot_mod4
```

## 5. Model: NDVIas  function of GCC
```{r}
mod5 = glm(mean_ndvi_5m ~ mean_gcc_5m, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit5 = lm(mean_ndvi_5m ~ mean_gcc_5m, data = field_gcc_ndvi)
```
### Residuals with DHARMa
```{r, include=FALSE}
mod5.res = simulateResiduals(fittedModel = mod5, n = 500)
mod5.res$scaledResiduals
mod5.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod5.res)
```

```{r}
testDispersion(mod5.res)
```

### Summary
```{r}
summary(mod5)
```


#### Summary Dataframe

```{r}
mod5_df = data.frame(summary(mod5)$coefficients[,], confint(mod5), deviance(mod5), summary(mod5)$null.deviance, extractAIC(mod5))
mod5_df
mod5_df2 = tibble::rownames_to_column(mod5_df, "coefficent")
mod5_df3 = mod5_df2 %>% 
  mutate(model = "mod5") %>% 
  mutate(response = "NDVI" ) %>% 
  mutate(rmse = RMSE(mod5)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod5., null_deviance= summary.mod5..null.deviance, AIC = extractAIC.mod5.) %>% dplyr::select(model:response, coefficent:rmse)
mod5_df3
```

#### lm summary
```{r}
fit5_df = data.frame(summary(fit5)$coefficients[,], confint(fit5), extractAIC(fit5))
fit5_df
fit5_df2 = tibble::rownames_to_column(fit5_df, "coefficent")
fit5_df3 = fit5_df2 %>% 
  mutate(model = "fit5") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit5)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit5.) %>% dplyr::select(model:response, coefficent:rmse)
fit5_df3
```

### Data for graph
```{r}
preddat_mod5 = data.frame(mean_gcc_5m = field_gcc_ndvi$mean_gcc_5m)

head(preddat_mod5)

pred_mod5 = predict(mod5, newdata = preddat_mod5, se.fit = TRUE)

UL_mod5 = with(pred_mod5, fit + 2*se.fit)
LL_mod5 = with(pred_mod5, fit - 2*se.fit)

field_gcc_ndvi5 = mutate(field_gcc_ndvi, pred_mod5 = pred_mod5$fit, 
               ucl_mod5 = UL_mod5, 
               lcl_mod5 = LL_mod5)
```

### Graph 

```{r}
p5 = ggplot(data = field_gcc_ndvi5, aes(x = mean_gcc_5m, y = mean_ndvi_5m)) + 
    geom_point(size = 2) +  
  stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI (5m)") +
    xlab("Mean GCC (5m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

p5
  
```

```{r fig.height=3, fig.width=3}
plot_mod5 = ggplot(data = field_gcc_ndvi5, aes(x = mean_gcc_5m, y = mean_ndvi_5m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod5), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod5, ymax = ucl_mod5, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod5), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod5), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI (5m)") +
    xlab("Mean GCC (5m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
    scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

plot_mod5
```

## 6. Model: NDVIas  function of GCC
```{r}
mod6 = glm(mean_ndvi_10m ~ mean_gcc_10m, data = field_gcc_ndvi, family = gaussian)
```

```{r}
fit6 = lm(mean_ndvi_10m ~ mean_gcc_10m, data = field_gcc_ndvi)
```
### Residuals with DHARMa
```{r, include=FALSE}
mod6.res = simulateResiduals(fittedModel = mod6, n = 500)
mod6.res$scaledResiduals
mod6.res$scaledResidualsNormal
```

In the plot below we are looking for the points in the QQ plot to fall along the RED linen. In the Residuals vs.predicted plot were are looking for the lines to be relatively horizontal. All looks good. 
```{r}
plotSimulatedResiduals(simulationOutput = mod6.res)
```

```{r}
testDispersion(mod6.res)
```

### Summary
```{r}
summary(mod6)
```

```{r}
with(summary(mod6), 1 - deviance/null.deviance)
```




#### Summary Dataframe


```{r}
mod6_df = data.frame(summary(mod6)$coefficients[,], confint(mod6), deviance(mod6), summary(mod6)$null.deviance, extractAIC(mod6))
mod6_df
mod6_df2 = tibble::rownames_to_column(mod6_df, "coefficent")
mod6_df3 = mod6_df2 %>% 
  mutate(model = "mod6") %>% 
  mutate(response = "NDVI" ) %>% 
  mutate(rmse = RMSE(mod6)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., deviance=deviance.mod6., null_deviance= summary.mod6..null.deviance, AIC = extractAIC.mod6.) %>% 
  dplyr::select(model:response, coefficent:rmse)

mod6_df3
```
#### lm summary
```{r}
fit6_df = data.frame(summary(fit6)$coefficients[,], confint(fit6), extractAIC(fit6))
fit6_df
fit6_df2 = tibble::rownames_to_column(fit6_df, "coefficent")
fit6_df3 = fit6_df2 %>% 
  mutate(model = "fit6") %>% 
  mutate(response = "NDVI" ) %>%  
  mutate(rmse = RMSE(fit6)) %>%
  rename(estimate = Estimate, se = Std..Error, t_value = t.value,  p_value = Pr...t.., lcl = X2.5.., ucl = X97.5.., AIC = extractAIC.fit6.) %>% dplyr::select(model:response, coefficent:rmse)
fit6_df3
```

### Data for graph
```{r}
preddat_mod6 = data.frame(mean_gcc_10m = field_gcc_ndvi$mean_gcc_10m)

head(preddat_mod6)

pred_mod6 = predict(mod6, newdata = preddat_mod6, se.fit = TRUE)

UL_mod6 = with(pred_mod6, fit + 2*se.fit)
LL_mod6 = with(pred_mod6, fit - 2*se.fit)

field_gcc_ndvi6 = mutate(field_gcc_ndvi, pred_mod6 = pred_mod6$fit, 
               ucl_mod6 = UL_mod6, 
               lcl_mod6 = LL_mod6)
```

### Graph 

```{r}
p6 = ggplot(data = field_gcc_ndvi6, aes(x = mean_gcc_10m, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
   stat_smooth(method = "lm", col = "black", alpha = .25) +
    
    ylab("Mean NDVI  (10m)") +
    xlab("Mean GCC (10m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

p6
 
```

```{r fig.height=3, fig.width=3}
plot_mod6 = ggplot(data = field_gcc_ndvi6, aes(x = mean_gcc_10m, y = mean_ndvi_10m)) + 
    geom_point(size = 2) +  
    geom_line(aes(y = pred_mod6), linetype = 1, size = 2) + 
    geom_ribbon( aes(ymin = lcl_mod6, ymax = ucl_mod6, color = NULL, show.legend = FALSE), alpha = .15) +
    geom_line(aes(y= lcl_mod6), linetype = 'longdash', size = 1) + 
    geom_line(aes(y=ucl_mod6), linetype='longdash', size = 1) +
    
    ylab("Mean NDVI  (10m)") +
    xlab("Mean GCC (10m)")  +
    reg_theme +  guides(color=guide_legend(override.aes=list(fill=NA))) +
    scale_x_continuous(breaks=c(0.35, 0.38, 0.41)) +
  scale_y_continuous(breaks = seq(0.6, 0.8, by = .05), labels = c("0.6", "", "0.7", "", "0.8"))

plot_mod6
```


# Combine Summary output 

```{r}
model_sum1 = rbind(mod1_df3, mod2_df3)
model_sum2 = rbind(mod3_df3, mod4_df3)
model_sum3 = rbind(mod5_df3, mod6_df3)
model_sum4 = rbind(model_sum1, model_sum2)
model_sum5 = rbind(model_sum4, model_sum3)
model_sum5
```

Calculate delta AIC
https://stats.stackexchange.com/questions/232465/how-to-compare-models-on-the-basis-of-aic

```{r}
model_sum5_data = model_sum5 %>%
  mutate(min_AIC = -105.13361) %>%
  mutate(dAIC = round((AIC-min_AIC), 5))

model_sum5_data
```

Model  |  Delta_AIC   |
-------|--------------|
1      |    50.72     |
2      |    45.10     |
3      |    32.48     |
4      |     8.45     |
5      |     5.31     |
6      |     0.00     |


```{r}
write.csv(model_sum5_data, '../outputs/model_summary/2020-06-02_spatial-res-gcc-ndvi.csv', row.names = F)

```


```{r}
model_fit1 = rbind(fit1_df3, fit2_df3)
model_fit2 = rbind(fit3_df3, fit4_df3)
model_fit3 = rbind(fit5_df3, fit6_df3)
model_fit4 = rbind(model_fit1, model_fit2)
model_fit5 = rbind(model_fit4, model_fit3)
model_fit5
```

Calculate delta AIC
https://stats.stackexchange.com/questions/232465/how-to-compare-models-on-the-basis-of-aic

```{r}
model_fit5_data = model_fit5 %>%
  mutate(min_AIC = -197.9457) %>%
  mutate(dAIC = round((AIC-min_AIC), 4))

model_fit5_data
```
```{r}
write.csv(model_fit5_data, '../outputs/model_summary/2020-07-13_spatial-res-gcc-ndvi-lm.csv', row.names = F)

```
Model  |  Delta_AIC   |
-------|--------------|
1      |    50.72     |
2      |    45.10     |
3      |    32.48     |
4      |     8.45     |
5      |     5.31     |
6      |     0.00     |


# Manuscript Figures 

## Part 1: Vegetation Indices

```{r fig.height=7, fig.width=6}

grid_plot_vi = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_vi

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-05-20_VI-gcc-ndvi.jpeg", plot = grid_plot_vi, width = 6, height = 7, units = c("in"), dpi=600 )
```

```{r fig.height=7, fig.width=6}

grid_plot_lm = cowplot::plot_grid(p1, p2, p3, p4, p5, p6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) 
grid_plot_lm

```
expression(beta)
labs(x=expression(C~mass~(g~C~m^-2))) +

geom_text(x=0.4, y=0.6, label=(expression(Delta~AIC))) +

Model  |  Delta_AIC   |
-------|--------------|
1      |    50.72     |
2      |    45.10     |
3      |    32.48     |
4      |     8.45     |
5      |     5.31     |
6      |     0.00     |

expression(paste(delta^{15}, "N-NO"[3]^-{}, " (vs air)")))
```{r fig.height=7, fig.width=6}

grid_plot1 = cowplot::plot_grid(plot_mod1, plot_mod2, plot_mod3, plot_mod4, plot_mod5, plot_mod6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2) +
  draw_label(label = (expression(paste(Delta~AIC, "=50.7"))), x = .4, y = .77, size = 12, fontface = "plain") + #model 1 
  draw_label(label = (expression(paste(Delta~AIC, "=45.1"))), x = .9, y = .77, size = 12, fontface = "plain") + # model2
draw_label(label = (expression(paste(Delta~AIC, "=32.5"))), x = .4, y = .45, size = 12, fontface = "plain") + #model 3 
  draw_label(label = (expression(paste(Delta~AIC, "=8.5"))), x = .9, y = .45, size = 12, fontface = "plain") + # model4

draw_label(label = (expression(paste(Delta~AIC, "=5.3"))), x = .4, y = .1, size = 12, fontface = "plain") + #model 5 
  draw_label(label = (expression(paste(Delta~AIC, "=0.0"))), x = .9, y = .1, size = 12, fontface = "plain")  # model6



grid_plot1

```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-06-02_VI-gcc-ndvi-dAIC.jpeg", plot = grid_plot1, width = 6, height = 7, units = c("in"), dpi=600 )
```

### lm models

Model  |  Delta_AIC   |
-------|--------------|
1      |    50.72     |
2      |    45.10     |
3      |    32.48     |
4      |     8.45     |
5      |     5.31     |
6      |     0.00     |

```{r fig.height=7, fig.width=6}

grid_lm = cowplot::plot_grid(p1, p2, p3, p4, p5, p6,   labels = c("A", "B", "C", "D", "E", "F"), align = "hv", ncol= 2)  +
  draw_label(label = (expression(paste(Delta~AIC, "=50.7"))), x = .4, y = .77, size = 12, fontface = "plain") + #model 1 
  draw_label(label = (expression(paste(Delta~AIC, "=45.1"))), x = .9, y = .77, size = 12, fontface = "plain") + # model2
draw_label(label = (expression(paste(Delta~AIC, "=32.5"))), x = .4, y = .45, size = 12, fontface = "plain") + #model 3 
  draw_label(label = (expression(paste(Delta~AIC, "=8.5"))), x = .9, y = .45, size = 12, fontface = "plain") + # model4

draw_label(label = (expression(paste(Delta~AIC, "=5.3"))), x = .4, y = .1, size = 12, fontface = "plain") + #model 5 
  draw_label(label = (expression(paste(Delta~AIC, "=0.0"))), x = .9, y = .1, size = 12, fontface = "plain")  # model6

grid_lm
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/2020-07-12_lm-gcc-ndvi-dAIC.jpeg", plot = grid_lm, width = 6, height = 7, units = c("in"), dpi=600 )
```